### 2023-09-05 paper-source/main.tex
Added lots to project. Had a breakdown with lots of sources being muddled up. Restarted, and working up. Paper source added to project.

% mnras_template.tex 
%
% LaTeX template for creating an MNRAS paper
%
% v3.0 released 14 May 2015
% (version numbers match those of mnras.cls)
%
% Copyright (C) Royal Astronomical Society 2015
% Authors:
% Keith T. Smith (Royal Astronomical Society)

% Change log
%
% v3.0 May 2015
%    Renamed to match the new package name
%    Version number matches mnras.cls
%    A few minor tweaks to wording
% v1.0 September 2013
%    Beta testing only - never publicly released
%    First version: a simple (ish) template for creating an MNRAS paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Basic setup. Most papers should leave these options alone.
\documentclass[fleqn,usenatbib]{mnras}

% MNRAS is set in Times font. If you don't have this installed (most LaTeX
% installations will be fine) or prefer the old Computer Modern fonts, comment
% out the following line
\usepackage{newtxtext,newtxmath}
% Depending on your LaTeX fonts installation, you might get better results with one of these:
%\usepackage{mathptmx}
%\usepackage{txfonts}

% Use vector fonts, so it zooms properly in on-screen viewing software
% Don't change these lines unless you know what you are doing
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}

%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
% \usepackage{enumitem}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Mergers in COSMOS]{Mergers in the COSMOS Field}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[D. O'Ryan et al.]{
David O'Ryan$^{1}$\thanks{E-mail: d.oryan@lancaster.ac.uk}
\\
% List of institutions
$^{1}$Lancaster University \\
}

% These dates will be filled out by the publisher
\date{Accepted XXX. Received YYY; in original form ZZZ}

% Enter the current year, for the copyright statements etc.
\pubyear{2023}

% Don't change these lines
\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle

% Abstract of the paper
\begin{abstract}
   Abstract will go here.
\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
keyword1 -- keyword2 -- keyword3
\end{keywords}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%

\section{Introduction}\label{introduction}
 Galaxy interaction and merging is of fundamental importance to our current theories of galaxy formation and evolution. Specifically, in the theory of $\Lambda$CDM cosmology, where structure is expected to form hierarchically \cite{normal cosmology papers}. These interactions lead to disturbed morphologies \citep{normal disturbed morphology papers}, intense starbursts \citep{normal starburst papers} and, potentially, the rapid quenching of those systems \citep{normal quenching papers}. These process are found to occur not just in our simulations of galaxy interaction \citep{new simulation papers} but across a wide range of observations of interacting systems as well \citep{new observation papers}. There is also evidence to suggest that interaction plays a role in the activation of active galactic nuclei (AGN) \citep{normal papers on AGN activation}. Therefore, with interaction having such an affect on the galaxies we see - over a long time period - understanding galaxy interaction is fundamental to understanding galaxy evolution.

 To completely understand galaxy interaction, and put reliable statistical constraints on its effect on galaxies, we require large samples of interacting galaxies to compare to non-interacting control galaxies. These large samples are surprisingly difficult to come by; with the first interacting galaxy catalogue (the \citet{1966ApJS...14....1A} catalogue) containing only 318 systems. More recent studies have created their own samples, and used them to draw conclusions on the effects of interacting and merging galaxies on galaxy formation. \textbf{Give examples here of such studies}.

 However, we elect to use the newly created interacting galaxy catalogue created by \citet{2023ApJ...948...40O} (hereafter, OR23) which found and published a sample of 21,926 interacting galaxies. This sample was created using the new ESA Datalabs\footnote{ESA Datalabs: link} platform and the new machine learning algorithm \texttt{Zoobot} \citep{2022MNRAS.509.3966W, 2023JOSS....8.5312W} classifying all sources in the Hubble Source Catalogue from the Hubble Space Telescope (HST) archives as to whether they were interacting or not. A rigorous process was then conducted to select likely interacting and merging candidates. They presented this catalogue with initial explorations of the catalogue (such as its limitations) but mainly focused on the methods used to create it.

 In this work, we utilise the new OR23 catalogue and match it with the Cosmic Evolutionary Survey (COSMOS) catalogues and explore the parameters of these systems in a statistically meaningful way. We elect to use COSMOS as it has much flexibility in the parameters we can extract, having many editions of its catalogues using a variety of software to give estimates of stellar masses, star formation rates, luminosity's, and redshift information. For our aims, we use a combination of the COSMOS2015 \citep{2016ApJS..224...24L} and COSMOS2020 \citep{2022ApJS..258...11W} catalogues. The COSMOS2015 catalogue contains excellent estimates of stellar mass and photometric redshift, while the COSMOS2020 catalogue contains information to calculate the star formation rates of each galaxy from estimate luminosity's as well as X-ray flux information to define an AGN.

 Interestingly, there has also been little work done to investigate mergers and interacting galaxies that exist in the COSMOS field, with the most recent work \citet{2022ApJ...940....4S} investigating on 2351 systems throughout the field, focusing on the relationship of projected separation of the galaxy pairs with star formation; finding a significant enhancement in each interactor the smaller the projected separation between them was. Using OR23, we find a sample of 3096 interacting systems that are also in the COSMOS field. We will use these to investigate not only the star formation rate difference, but also the rate of occurance of AGN and the evolution of the nonparametric CAS, Gini and M$_{20}$ parameters.

 Upon matching the OR23 catalogue to COSMOS, we also break the matched systems down into different stages in the interaction, attempting to investigate the changes in star formation rates, AGN activity and morphology as an interaction continues. We create a control sample, and aim to quantify the increase in star formation experienced by an interacting galaxy and also aim to see what this increase is at its height. We also compare the difference in occurrence in AGN between the interacting and control sample, and also speculate on the potential power of these AGN in the comparison. Finally, we measure the change in the regular morphology parameters from \citet{2004AJ....128..163L} throughout the different stages.

 This paper is laid out as follows in Section \ref{data} we fully explain the OR23 and COSMOS catalogues, and describe the process of catalogue matching. Section \ref{staging} describes the methods by which we split the interacting systems in their different stages, calculate the star formation rates of each system as well as describe how we classify a galaxy as an AGN. In Section \ref{results} we full describe and discuss our results, and their implications, before we make concluding remarks in Section \ref{conclusion}.

Where necessary, we use a Flat $\Lambda$CDM cosmology with $H_0$ = $70$\,km/s/Mpc and $\Omega_M = 0.3$. Hereafter in this paper, when referring to an interacting galaxy we are referring to a galaxy which has undergone one or multiple flybys by a secondary galaxy and caused tidal disturbance. A merging galaxy is the final state of these flybys, where two or more systems have or are about to coalesce to form a highly morphologically irregular system.

\section{Data \& Catalogue Matching} \label{data}
\noindent In this work, we utilise the interacting galaxy catalogue created in \citet{2023ApJ...948...40O}. While the creation of this catalogue is fully detailed there, we will briefly describe it here. This catalogue of 21,926 interacting galaxies was created using a Convolutional Neural Network - \textit{Zoobot} - to search all final product data in the \textit{Hubble} Legacy Archive. This was done using single-band \textit{Hubble} images, specificially the \textit{F814W} filter. This choice was motivated by it having the highest number of final product FITS files associated with it. Using the \textit{Hubble} Source Catalogue to extract 92 million sources, these were classified into non-interacting and interacting galaxies. Due to existing issues with using CNNs (see \citet{papers on problems with CNN}) an extremely conservative prediction score from \textit{Zoobot} was required to define an interacting galaxy. This resulted in a very pure, but highly incomplete catalogue of interacting galaxies. Still, this is the largest catalogue of interacting galaxies directly found to date.

However, in the OR23 catalogue, only the coordinates and the \textit{Hubble} Source catalogue are provided. For ancillary data, this catalogue must be matched to different data repositories. This is not a trivial task, as a large proportion of the OR23 catalogue is known to not exist in any existing astrophysical data repository. However, in this work, we opt to match the OR23 catalogue to the Cosmic Evolution Survey (COSMOS) 2020 catalogue \citep{2022ApJS..258...11W}. This contains estimates of stellar masses, photometric redshifts, star formation rates and many line fluxes estimated from LaPhare \citep{LaPhare paper} and EAZY \citep{EAZY paper}. It also contains the observed fluxes for multiple lines from UVISTA and Subaru HyperSuprime-Cam (HSC). For all further measurements of absolute magnitude, we opt to use the HSC infrared band, centered on 7740.58\AA. This is selected as it is the most relevant in detecting radiation from star forming regions over our redshift range.

The two catalogues were matched by searching a 10" radius about each interacting galaxy in OR23. The galaxy closest to the OR23 coordinates in projected separation was defined as the primary galaxy. To find the secondary galaxy, another search radius of 30" was defined about the found primary galaxy coordinates in the COSMOS catalogue. A range of $\pm0.001$ about the primary redshift was taken. Note, this was based on the estimated photometric redshift from EAZY. Once this cut had been applied, the galaxy closest to the primary galaxy in projected separation was taken to be the secondary galaxy. With these criteria, a matched sample of 3,568 primary galaxies were found. For each primary, a secondary was also successfully recovered giving us a total of 7,136 interacting galaxies.

However, duplication existed in this matched catalogue. This was when a primary galaxy in OR23 had been assigned to multiple COSMOS sources or vice versa. This was also true of secondaries, where the secondary galaxy source could be assigned to different primaries. Therefore, a de-duplication was conducted on the COSMOS Identification numbers. The same ID for the primary or secondary could not appear multiple times, as well as no primary or secondary galaxy IDs could match. Upon this de-duplication, we were left with a sample of 3,437 systems or 6,874 interacting galaxies.

\section{Finding Secondaries \& Staging Interacting Galaxies}\label{staging}
In this section, we describe our methodology of finding the secondaries about each galaxy and detail how we classified each interaction into separate stages. The \citet{2023ApJ...948...40O} catalogue only made predictions on interacting systems, not individual galaxies. This was due to the high number of duplication found in the source ids in the HSC. Therefore, very often, any neighbouring secondary galaxy that would have appeared in the catalogue has been merged under a single SourceID related to the primary galaxy. We use the photometric redshifts available in the COSMOS2020 catalogue to search around each primary galaxy for their related secondary. Each interacting pair is then split into four different stages of interaction. This was done by four of the authors of this work. Here, we detail how we maintain statistical robustness and quantify our biases even with multiple classifiers. We also detail the number of galaxies in each stage bin.

\subsection{Secondary Identification}
\noindent As stated previously, the \citet{2023ApJ...948...40O} catalogue only identified interacting galaxy systems, not individual interacting galaxies. Therefore, we must find the secondary in each interaction using the COSMOS2020 catalogue. We achieve this by applying three steps to each system. First, we identify all sources within a 10" radius of our identified primary interacting galaxy. We then create a slice in redshift to find galaxies which are actually nearby in 3D. This is done using a similar parameter as that defined by \citet{Baldry et al. (2006)} when calculating the environment about each galaxy. We define the slice in redshift by $\pm\Delta$zc $= \pm1000$km/s.

Upon applying these two criteria, we are often only left with very few potential candidates to be the secondary interacting galaxy. At this stage, we then order all of our candidates by the measured 3D distance from our primary galaxy using the on-sky separation and their respective redshifts. The closest candidate is then used as the secondary galaxy. To test this method is robust, we conduct two final checks on our candidate interacting systems. First, for all systems we can, we look up the spectroscopic information of each. We find no serious change in the redshift between the photometric and spectroscopic redshifts. We also finally conduct a visual inspection of each candidate interacting galaxy system. We confirm that the potential secondary does exhibit morphological disturbance or is clearly involved in the interaction with the primary.

In a few cases (N), we find that our secondary identification has failed. This is purely due to the secondary already merging with the primary galaxy, and therefore, not being identified as a second source or object in the COSMOS2020 catalogue. Later on, these will be classified as our stage 4 galaxies. We keep these galaxies in our sample, as they are clearly merging, merged or post-merger candidates, however do not attempt to find a secondary for them. Thus, our sample of 3,784 primary interacting galaxies is increased, with their secondaries, to N galaxies.

\subsection{Classifying Stage of Interaction}
The primary purpose of this project is to compare different stages of interaction and investigate changes in their underlying photometric parameterisations. This will give us insights into the interplay between interaction and these underlying processes. Therefore, in this section we describe how we break our interacting galaxies into different stages.

Our sample overlapping with COSMOS20202 is broken down into four different stages. We visually classify each system accounting for the pair separation and distortion. The four different stages are as follows:

% \vspace{-2mm}

\begin{itemize}
    \item Stage 1: Well-separated with no morphological disturbance.
    \item Stage 2: Close pairs showing strong signs of interaction.
    \item Stage 3: Well separated pairs with evidence of disturbance.
    \item Stage 4: Overlapping with morphological distortion.
\end{itemize}

% \vspace{-2mm}

\noindent Each stage is designed to capture a different part of interaction, where we expect different physical processes to be dominant.

In the first stage of interaction, the two galaxies remain separated with no morphological disturbance. We expect this to be because the two galaxies are approaching each other and about to begin their first pericentre pass. Therefore, we would not expect any of the usual effects of interaction to have started. This stage acts, essentially, as a control on our sample.

In stage 2, we observe morphology distortion as the two galaxies have crossed their first pericentre passage.

In stage 3, we expect to have captured those galaxies which have undergone their first passage of each other and be approaching their apocentre. There are then three future outcomes of this. First, the secondary galaxy is only just approaching its apocentre, it has just passed it's apocentre, or the galaxy is about to escape from the system. In any case, we observe severe morphological disturbance at this point, and would expect to begin seeing the effects of interaction on the galaxy. The severe torques exerted on the gas should lead to some initial effects of a starburst, and there could also be some ignition of nuclear activity.

Stage 4 expects to capture those galaxies which are actually undergoing coalescence or be at the point where they are about to. This is, from the literature, the point we would expect all the effects of interaction to be taking place.

The categorisation was conducted by the co-authors of this paper (names). Initially, 300 samples from the COSMOS sample are classified together, to reduce biases from the group and then split between the group evenly. This leads to 4,385 classifications being made by each co-author. To further quantify the bias and error involved in using different classifiers, a further 20 galaxies were classified as a group followed by each member of the group classifying individually the same 80 galaxies. The results of this is shown in Figure \ref{fig:std-dev-clsf}. It is important to note here, that the two stages with highest disagreement between classifiers is stages 1 and 4. \textcolor{red}{Explain why this could be?}

\section{Results \& Discussion}\label{results}
 - Show breakdown of stages. \\
 - What are their mass distributions? \\
 - Mass Ratios \\
 - Investigate SF with Mass \\
 - Investigate SF with Mass Ratio/Merger Type \\
 - Investigate SF with projected Separation \\
 - Control for Environment \\
 - Where do the interacting galaxies lie? \\
 - What does this all mean?

\section{Conclusions}\label{conclusion}
 - Restate the Results \\
 - What's the next steps of this project?
    - Hint at what I would do in a Fellowship.

\section*{Acknowledgements}
The Acknowledgements section is not numbered. Here you can thank helpful
colleagues, acknowledge funding agencies, telescopes and facilities used etc.
Try to keep it short.

This work utilised data from the Cosmic Evolution Survey (COSMOS) which has a digital object identifier of 10.26131/IRSA178.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%

% The best way to enter references is to use BibTeX:
\bibliographystyle{mnras}
\bibliography{references} % if your bibtex file is called example.bib

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%

\appendix

\section{Needed?}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Don't change these lines
\bsp	% typesetting comment
\label{lastpage}
\end{document}

% End of mnras_template.tex

### 2023-09-05 scripts/calc-environ-rel-serial.py

@@ -1,0 +1,139 @@
+import pandas as pd
+import numpy as np
+
+from astropy.io import fits
+from astropy.table import Table
+from astropy.cosmology import FlatLambdaCDM
+from astropy.coordinates import SkyCoord
+import astropy.units as u
+
+import sys
+import logging
+import os
+import glob
+from tqdm import tqdm
+
+def calc_sep(ra1, dec1, ra2, dec2, z_1, z_2, cosmo):
+    
+    d1 = cosmo.comoving_distance(z_1).to(u.kpc)
+    d2 = cosmo.comoving_distance(z_1).to(u.kpc)
+    
+    c1 = SkyCoord(ra = ra1 * u.deg, dec = dec1 * u.deg, frame = 'fk5')
+    c2 = SkyCoord(ra = ra2 * u.deg, dec = dec2 * u.deg, frame = 'fk5')
+    
+    ang_sep = c1.separation(c2).to(u.arcmin)
+    conversion = cosmo.kpc_proper_per_arcmin(z_1)
+    
+    proj_sep = ang_sep * conversion
+    
+    return float(proj_sep.to(u.Mpc) / u.Mpc)
+
+def get_n_neighbours(gal_id, ra, dec):
+    
+    end_index = 0
+    ang = 0.1
+    while end_index < 5:
+        record = data[(data['ALPHA_J2000'] < (ra + ang)) & (data['ALPHA_J2000'] > (ra - ang)) & (data['DELTA_J2000'] < (dec + ang)) & (data['DELTA_J2000'] > (dec - ang))]
+
+        table = Table(record)
+
+        prim_galaxy_record = record[record['ID'] == gal_id]
+        prim_z = prim_galaxy_record['ez_z_phot'][0]
+
+        df = table.to_pandas()[['ID','ALPHA_J2000', 'DELTA_J2000', 'ez_z_phot', 'lp_type']]
+        df = df.query('lp_type == 0').drop(columns = 'lp_type').dropna()
+        df = df.query('ID != @gal_id')
+
+        if len(df) < 0.5:
+            return 'null'
+
+        df_z_diff = (
+            df
+            .assign(z_diff = df.ez_z_phot.apply(lambda x: abs(x - prim_z)))
+        )
+
+        df_z_cut = df_z_diff.query('z_diff < 0.005')
+        if len(df_z_cut) < 1:
+            return {'IDs': [], 'separations': [], 'N_1' : None, 'N_2' : None, 'N_3' : None, 'N_4': None, 'N_5' : None}
+
[…]

### 2023-09-05 scripts/calc-environ-relation-dict.py

@@ -1,0 +1,127 @@
+## Imports
+import pandas as pd
+import numpy as np
+
+from astropy.io import fits
+from astropy.table import Table
+from astropy.cosmology import FlatLambdaCDM
+from astropy.coordinates import SkyCoord
+import astropy.units as u
+
+import logging
+import os
+import glob
+from tqdm import tqdm
+tqdm.pandas()
+
+## Functions
+def calc_sep(ra1, dec1, ra2, dec2, conversion):
+    
+    c1 = SkyCoord(ra = ra1 * u.deg, dec = dec1 * u.deg, frame = 'fk5')
+    c2 = SkyCoord(ra = ra2 * u.deg, dec = dec2 * u.deg, frame = 'fk5')
+    
+    ang_sep = c1.separation(c2).to(u.arcmin)
+        
+    proj_sep = ang_sep * conversion
+    
+    return float(proj_sep.to(u.Mpc) / u.Mpc)
+
+## Main Function
+def main():
+    data_folder = '/mmfs1/storage/users/oryan/cosmos-data'
+    results = f'/mmfs1/storage/users/oryan/cosmos/results'
+
+    logging.info('Importing COSMOS data...')
+    with fits.open(f'{data_folder}/COSMOS2020_CLASSIC_R1_v2.1_p3.fits.gz') as hdul:
+        data_rec = hdul[1].data
+    logging.info('Completed.')
+
+    logging.info('Reducing Data Table...')
+    data_rec = data_rec[data_rec['lp_type'] == 0]
+    data_rec = Table(data_rec)
+    data = data_rec['ID', 'ALPHA_J2000', 'DELTA_J2000', 'ez_z_phot']
+    del data_rec
+    logging.info('Completed.')
+
+    logging.info('Setting up loop...')
+    ids = list(data['ID'])
+    ang = 0.1
+    cosmo = FlatLambdaCDM(H0=70, Om0=0.3, Tcmb0=2.725)
+    results_dict = {}
+    counter = 0
+
+    logging.info('Beginning loop...')
+    for i in tqdm(ids):
+        tmp_dict = {'IDs': [], 'N_1': np.nan, 'N_2': np.nan, 'N_3': np.nan, 'N_4': np.nan, 'N_5': np.nan}
+        entry = data[data['ID'] == i]
+        if np.isnan(entry['ALPHA_J2000']) or np.isnan(entry['DELTA_J2000']) or np.isnan(entry['ez_z_phot']):
[…]

### 2023-09-05 scripts/calc-environ-relation.py

@@ -1,0 +1,155 @@
+import pandas as pd
+import numpy as np
+
+from astropy.io import fits
+from astropy.table import Table
+from astropy.cosmology import FlatLambdaCDM
+from astropy.coordinates import SkyCoord
+import astropy.units as u
+
+import multiprocessing
+
+import os
+import logging
+import time
+import datetime
+import glob
+from tqdm import tqdm
+
+def calc_sep(ra1, dec1, ra2, dec2, z_1, z_2, cosmo):
+        
+    c1 = SkyCoord(ra = ra1 * u.deg, dec = dec1 * u.deg, frame = 'fk5')
+    c2 = SkyCoord(ra = ra2 * u.deg, dec = dec2 * u.deg, frame = 'fk5')
+    
+    ang_sep = c1.separation(c2).to(u.arcmin)
+    conversion = cosmo.kpc_proper_per_arcmin(z_1)
+        
+    proj_sep = ang_sep * conversion
+    
+    return float(proj_sep.to(u.Mpc) / u.Mpc)
+
+def get_n_neighbours(gal_id, ra, dec):
+
+    nearest = {'IDs': [], 'separations': [], 'N_1' : np.nan, 'N_2' : np.nan, 'N_3' : np.nan, 'N_4': np.nan, 'N_5' : np.nan}
+
+    # if gal_id % 500 == 0:
+    #     logging.info(gal_id)
+
+    # record = data[(data['ALPHA_J2000'] < (ra + ang)) & (data['ALPHA_J2000'] > (ra - ang)) & (data['DELTA_J2000'] < (dec + ang)) & (data['DELTA_J2000'] > (dec - ang))]
+
+    table = Table(data)
+
+    prim_galaxy_record = data[data['ID'] == gal_id]
+    prim_z = prim_galaxy_record['ez_z_phot'][0]
+
+    df = table.to_pandas()[['ID','ALPHA_J2000', 'DELTA_J2000', 'ez_z_phot', 'lp_type']]
+    df = df.query('lp_type == 0').drop(columns = 'lp_type').dropna()
+    df = df.query('ID != @gal_id')
+
+    if len(df) < 0.5:
+        return nearest
+
+    df_z_diff = (
+        df
+        .assign(z_diff = df.ez_z_phot.apply(lambda x: abs(x - prim_z)))
+    )
+
+    df_z_cut = df_z_diff.query('z_diff < 0.005')
+    if len(df_z_cut) < 1:
[…]

### 2023-11-17 paper-source/main.tex
Major update to code and paper. Code, reclassified stages. Paper, methods section completed and prepping to write up results.

@@
 \usepackage{amssymb}	% Extra maths symbols
+\usepackage{hyperref}
 % \usepackage{enumitem}
@@
 \section{Introduction}\label{introduction}
- Galaxy interaction and merging is of fundamental importance to our current theories of galaxy formation and evolution.
-Specifically, in the theory of $\Lambda$CDM cosmology, where structure is expected to form hierarchically \cite{normal cosmology papers}.
-These interactions lead to disturbed morphologies \citep{normal disturbed morphology papers}, intense starbursts \citep{normal starburst papers} and, potentially, the rapid quenching of those systems \citep{normal quenching papers}.
-These process are found to occur not just in our simulations of galaxy interaction \citep{new simulation papers} but across a wide range of observations of interacting systems as well \citep{new observation papers}.
-There is also evidence to suggest that interaction plays a role in the activation of active galactic nuclei (AGN) \citep{normal papers on AGN activation}.
-Therefore, with interaction having such an affect on the galaxies we see - over a long time period - understanding galaxy interaction is fundamental to understanding galaxy evolution.
+\noindent Galaxy interaction and merging is of fundamental importance to our current theories of galaxy formation and evolution.
+Our current cosmological theory, $\Lambda$CDM dictates that structure is expected to form and assemble hierarchically \citep{1978MNRAS.183..341W, 2013MNRAS.436.1765M}.
+Thus, understanding the underlying processes that occur in galaxy interaction and merging are paramount to understanding cosmological theories.
+It is well known that many underlying processes are triggered or enhanced due to galaxy interaction.
+The clearest result of interaction is the disruption of galactic morphology, the acceleration of disks to spheroidal systems and the formation of tidal features \citep{1972ApJ...178..623T, 1977ApJ...212..616T, 2005MNRAS.357..753G, 2009MNRAS.397..802H}, increases in star formation rates when compared to the general galaxy population \citep{1991ApJ...370L..65B, 2006ApJ...652...56B, 2014MNRAS.437.2137S, 2015ApJ...807L..16K} and, potentially, their rapid quenching \citep{2013MNRAS.430.1901H, 2023RAA....23i5026D}.
+There is also evidence to suggest that interaction plays a role in the activation of active galactic nuclei (AGN) \citep{2011MNRAS.418.2043E, 2015ApJ...806..219C, 2023MNRAS.523.4164H}.
+Therefore, with interaction having such an affect on the galaxies we see - over a long time period - understanding galaxy interaction is fundamental to understanding galaxy evolution
 
- To completely understand galaxy interaction, and put reliable statistical constraints on its effect on galaxies, we require large samples of interacting galaxies to compare to non-interacting control galaxies.
-These large samples are surprisingly difficult to come by; with the first interacting galaxy catalogue (the \citet{1966ApJS...14....1A} catalogue) containing only 318 systems.
-More recent studies have created their own samples, and used them to draw conclusions on the effects of interacting and merging galaxies on galaxy formation.
-\textbf{Give examples here of such studies}.
+To better our understanding of galaxy interaction, it is often prudent to break them down into different stages of interaction.
+This relates to the dynamical time of the interaction, and the snapshot in the interaction we are observing.
+Previous works focused on simulations find that a sudden increase in star formation occurs early in the dynamical timescale of the interaction \citep{2008MNRAS.384..386C, 2019MNRAS.490.2139R}, however, confirming this definitive link observationally remains elusive \citep{2023arXiv230916531R}.
+The same studies could also be done for nuclear activation as well as quenching of interacting systems \citep{Papers on nuclear activation}.
+While we cannot yet directly measure when in the dynamical timescale star formation is enhanced from observations, we can approximate it by splitting different interactions into different stages.
+These stages relate directly to the dynamical timescale of the interaction.
+Often, they are split into four: gravitationally bounded pairs, approaching pericentre of the interaction, approaching apocentre of the interaction, and approaching coalescence.
 
- However, we elect to use the newly created interacting galaxy catalogue created by \citet{2023ApJ...948...40O} (hereafter, OR23) which found and published a sample of 21,926 interacting galaxies.
-This sample was created using the new ESA Datalabs\footnote{ESA Datalabs: link} platform and the new machine learning algorithm \texttt{Zoobot} \citep{2022MNRAS.509.3966W, 2023JOSS....8.5312W} classifying all sources in the Hubble Source Catalogue from the Hubble Space Telescope (HST) archives as to whether they were interacting or not.
-A rigorous process was then conducted to select likely interacting and merging candidates.
-They presented this catalogue with initial explorations of the catalogue (such as its limitations) but mainly focused on the methods used to create it.
+To fully study the relationship between interaction stage and the underlying physical processes occurring we require large, statistically robust interacting galaxy samples.
+However, they are surprisingly difficult to create; with the first interacting galaxy catalogue (the \citet{1966ApJS...14....1A} catalogue) containing only 318 systems.
+More recent samples have been created either by machine learning classification \citep{2019A&A...626A..49P, 2023A&A...669A.141S}, visual classification by citizen scientists \citep{2010MNRAS.401.1043D} or by photometric parameterisation \citep{2004AJ....128..163L, 2023MNRAS.522....1N}.
+However, each sample has always been plagued by contamination and a loss of statistical significance when broken down into stages.
+It is notoriously difficult, from morphology alone, to select interacting or merging galaxies.
+Without redshift information it is difficult to discern if they are close together in 3D space or only by projection effects.
 
- In this work, we utilise the new OR23 catalogue and match it with the Cosmic Evolutionary Survey (COSMOS) catalogues and explore the parameters of these systems in a statistically meaningful way.
-We elect to use COSMOS as it has much flexibility in the parameters we can extract, having many editions of its catalogues using a variety of software to give estimates of stellar masses, star formation rates, luminosity's, and redshift information.
-For our aims, we use a combination of the COSMOS2015 \citep{2016ApJS..224...24L} and COSMOS2020 \citep{2022ApJS..258...11W} catalogues.
-The COSMOS2015 catalogue contains excellent estimates of stellar mass and photometric redshift, while the COSMOS2020 catalogue contains information to calculate the star formation rates of each galaxy from estimate luminosity's as well as X-ray flux information to define an AGN.
+We elect to use the newly created interacting galaxy catalogue created by \citet{2023ApJ...948...40O} (hereafter, OR23) which found a sample of 21,926 interacting galaxy systems.
+This is the largest visually classified interacting galaxy catalogue to date.
+This sample was created using the new ESA Datalabs\footnote{ESA Datalabs: link} platform and the convolutional neural network machine
+\texttt{Zoobot} \citep{2022MNRAS.509.3966W, 2023JOSS....8.5312W}.
+This classified all sources in the Hubble Source Catalogue \citep{2016AJ....151..134W} from the Hubble Space Telescope (HST) archives into interacting or non-interacting.
+Once this was done, a rigorous process of de-duplication, contamination removal and visual inspection was conducted.
 
- Interestingly, there has also been little work done to investigate mergers and interacting galaxies that exist in the COSMOS field, with the most recent work \citet{2022ApJ...940....4S} investigating on 2351 systems throughout the field, focusing on the relationship of projected separation of the galaxy pairs with star formation; finding a significant enhancement in each interactor the smaller the projected separation between them was.
-Using OR23, we find a sample of 3096 interacting systems that are also in the COSMOS field.
-We will use these to investigate not only the star formation rate difference, but also the rate of occurance of AGN and the evolution of the nonparametric CAS, Gini and M$_{20}$ parameters.
+In this work, we cross match this catalogue with the Cosmic Evolutionary Survey (COSMOS) survey\footnote{DOI: \href{https://www.ipac.caltech.edu/doi/irsa/10.26131/IRSA178}{10.26131/IRSA178}}.
+This provides us with ancillary data for a subset of the OR23 catalogue.
+This ancillary data contains many galactic parameters of interest and we explore how they evolve with different stages of interaction.
+We define four distinct stages that occur over the course of the full dynamical timescale of interaction, from the two galaxies approaching each other to full coalescence.
+We primarily focus on the evolution of the stellar masses, star formation rates, surrounding environment and AGN classification from various COSMOS catalogues across the full dynamical timescale of interaction.
+With the photometric redshifts available from COSMOS, we also confirm a set of interacting galaxies and close pairs to investage further parameters of interest.
+These include the trend of projected separation of the galactic pairs on star formation rate as well as the change with mass ratio.
 
- Upon matching the OR23 catalogue to COSMOS, we also break the matched systems down into different stages in the interaction, attempting to investigate the changes in star formation rates, AGN activity and morphology as an interaction continues.
-We create a control sample, and aim to quantify the increase in star formation experienced by an interacting galaxy and also aim to see what this increase is at its height.
-We also compare the difference in occurrence in AGN between the interacting and control sample, and also speculate on the potential power of these AGN in the comparison.
-Finally, we measure the change in the regular morphology parameters from \citet{2004AJ....128..163L} throughout the different stages.
+%, comparing to the work of \citet{2022ApJ...940....4S} a different study using COSMOS to investigate these latter relations.
 
- This paper is laid out as follows in Section \ref{data} we fully explain the OR23 and COSMOS catalogues, and describe the process of catalogue matching.
-Section \ref{staging} describes the methods by which we split the interacting systems in their different stages, calculate the star formation rates of each system as well as describe how we classify a galaxy as an AGN.
-In Section \ref{results} we full describe and discuss our results, and their implications, before we make concluding remarks in Section \ref{conclusion}.
+This paper is laid out as follows in Section \ref{data} we explain the OR23 and COSMOS catalogues, and describe the process of catalogue matching especially focused on accurate de-duplication and cross-matching selection from the different catalogues.
+Section \ref{staging} describes the methods by which we split the interacting systems into their different stages, and how we identify the secondary galaxies to each identified interacting galaxy.
+We also discuss our processes of calculating projected separations.
+In Section \ref{results} we describe and discuss our results, and their implications, and compare to previous works focused on investigating different stages of interaction.
+Finally, Section \ref{conclusion} we make concluding remarks and discuss future work to better our constraints.
 
@@
 
-\section{Data \& Catalogue Matching} \label{data}
-\noindent In this work, we utilise the interacting galaxy catalogue created in \citet{2023ApJ...948...40O}.
-While the creation of this catalogue is fully detailed there, we will briefly describe it here.
-This catalogue of 21,926 interacting galaxies was created using a Convolutional Neural Network - \textit{Zoobot} - to search all final product data in the \textit{Hubble} Legacy Archive.
-This was done using single-band \textit{Hubble} images, specificially the \textit{F814W} filter.
-This choice was motivated by it having the highest number of final product FITS files associated with it.
-Using the \textit{Hubble} Source Catalogue to extract 92 million sources, these were classified into non-interacting and interacting galaxies.
-Due to existing issues with using CNNs (see \citet{papers on problems with CNN}) an extremely conservative prediction score from \textit{Zoobot} was required to define an interacting galaxy.
-This resulted in a very pure, but highly incomplete catalogue of interacting galaxies.
-Still, this is the largest catalogue of interacting galaxies directly found to date.
+\section{DATA: Catalogue Matching \& Secondary Identification} \label{data}
+\subsection{The O'Ryan+23 Catalogue}
+\noindent We utilise the interacting galaxy catalogue created in OR23.
+While the full process of its creation is detailed there, we briefly describe it here.
+This sample of interacting galaxies was created using a convolutional neural network - \texttt{Zoobot} - to search all final product data in the \textit{Hubble} Legacy Archive.
+A regular convolutional neural network classifies images by extracting features from them, and using this to output a solution.
+\texttt{Zoobot} differs by extracting features from an image, and then reduces them to a generalised representation (essentially, a small feature vector).
+The power of this is that it makes \texttt{Zoobot} incredibly generalisable.
+This is further reinforced by training it on citizen scientist responses to the Galaxy Zoo: DECaLS \citep{2022MNRAS.509.3966W} project to every task in that project.
+Thus, it can answer a host of questions as well as be very easily finetuned to new datasets and classification tasks.
+In OR23, it was easily finetuned on \textit{Hubble} data by using classifications from all previous Galaxy Zoo projects \citep{2008MNRAS.389.1179L}.
+
+Cutouts of each source were created as single-band \textit{F814W} images at 150 $\times$ 150 pixels across.
+This choice was motivated by it having the highest number of final product FITS files associated with it, while the image size was kept small due to the high number of cutouts required to be stored.
+Source coordinates were found in the \textit{Hubble} Source Catalogue \citep{2016AJ....151..134W}.
+This corresponded to just over 92 million cutouts to create and sources to classify.
+Due to issue of classifying interacting galaxies by morphology alone an extremely conservative prediction score from \textit{Zoobot} was required.
+This resulted in a very pure, but highly incomplete catalogue of 21,926 interacting galaxy systems.
+This is the largest catalogue of interacting galaxies directly found to date.
 
@@
 This is not a trivial task, as a large proportion of the OR23 catalogue is known to not exist in any existing astrophysical data repository.
-However, in this work, we opt to match the OR23 catalogue to the Cosmic Evolution Survey (COSMOS) 2020 catalogue \citep{2022ApJS..258...11W}.
-This contains estimates of stellar masses, photometric redshifts, star formation rates and many line fluxes estimated from LaPhare \citep{LaPhare paper} and EAZY \citep{EAZY paper}.
-It also contains the observed fluxes for multiple lines from UVISTA and Subaru HyperSuprime-Cam (HSC).
-For all further measurements of absolute magnitude, we opt to use the HSC infrared band, centered on 7740.58\AA.
-This is selected as it is the most relevant in detecting radiation from star forming regions over our redshift range.
+In this work, we opt to match the OR23 catalogue to the COSMOS catalogues.
 
-The two catalogues were matched by searching a 10" radius about each interacting galaxy in OR23.
-The galaxy closest to the OR23 coordinates in projected separation was defined as the primary galaxy.
-To find the secondary galaxy, another search radius of 30" was defined about the found primary galaxy coordinates in the COSMOS catalogue.
-A range of $\pm0.001$ about the primary redshift was taken.
-Note, this was based on the estimated photometric redshift from EAZY.
-Once this cut had been applied, the galaxy closest to the primary galaxy in projected separation was taken to be the secondary galaxy.
-With these criteria, a matched sample of 3,568 primary galaxies were found.
-For each primary, a secondary was also successfully recovered giving us a total of 7,136 interacting galaxies.
+\subsection{The COSMOS2020 Catalogue}
+We opt to match the OR23 catalogue with the catalogues of the COSMOS survey.
+Specifically, we elect to use the COSMOS2020 catalogue \citep{2022ApJS..258...11W}.
+This catalogue has a wealth of ancillary information for just over 1.7 million sources in a 2 square degree area of the sky.
+Each source found in this area has been analysed with well used astronomical software, for our purposes primarily LePhare \citep{1999MNRAS.310..540A, 2006A&A...457..841I} and EAzY \citep{2008ApJ...686.1503B}.
+These provide two different measurements of the parameters we wish to investigate and match with stage.
+The first is the stellar masses of each our cross matched galaxies and the estimated star formation rates.
+We opt to simply use one of these two measurements in our analysis.
+For the stellar mass we use the LePhare measurement and for the star formation rates we use the EAzY measurements.
+Using either the vice versa of this, both EAzY or both LePhare measurements led to the degeneracy's within the underlying model Spectral Energy Distribution (SED) templates being revealed.
+Therefore, using these two opposing parameters gave realistic approximations of these photometrically approximated values.
 
-However, duplication existed in this matched catalogue.
-This was when a primary galaxy in OR23 had been assigned to multiple COSMOS sources or vice versa.
-This was also true of secondaries, where the secondary galaxy source could be assigned to different primaries.
-Therefore, a de-duplication was conducted on the COSMOS Identification numbers.
-The same ID for the primary or secondary could not appear multiple times, as well as no primary or secondary galaxy IDs could match.
-Upon this de-duplication, we were left with a sample of 3,437 systems or 6,874 interacting galaxies.
+As stated previously, the OR23 catalogue only contained the source ID, right ascension and declination of each interacting galaxy.
+Therefore, we had to cross match these with the COSMOS2020 catalogue right ascension and declination measurements.
+To do this, we searched the COSMOS2020 catalogue for any sources within 10" of the OR23 sources.
+If more than one COSMOS2020 source was within this radius, we took the closest source to the OR23 coordinates as the correct source.
+Upon matching based on coordinates, we conducted a de-duplication of the resultant catalogue based on COSMOS2020 ID, and reassigned COSMOS2020 sources to each duplication.
+If no further COSMOS2020 sources were within 10" of the OR23 source, then this was considered not to be cross matched.
+We find that, after this cross matching and de-duplication, 3,786 of the OR23 sources exist in the COSMOS2020 catalogue.
 
-\section{Finding Secondaries \& Staging Interacting Galaxies}\label{staging}
-In this section, we describe our methodology of finding the secondaries about each galaxy and detail how we classified each interaction into separate stages.
-The \citet{2023ApJ...948...40O} catalogue only made predictions on interacting systems, not individual galaxies.
-This was due to the high number of duplication found in the source ids in the HSC.
-Therefore, very often, any neighbouring secondary galaxy that would have appeared in the catalogue has been merged under a single SourceID related to the primary galaxy.
-We use the photometric redshifts available in the COSMOS2020 catalogue to search around each primary galaxy for their related secondary.
-Each interacting pair is then split into four different stages of interaction.
-This was done by four of the authors of this work.
-Here, we detail how we maintain statistical robustness and quantify our biases even with multiple classifiers.
-We also detail the number of galaxies in each stage bin.
+We make two further cuts, based on the ancillary data available in the COSMOS2020 catalogue.
+First, there are many unphysical photometric measurements for the stellar mass or star formation rates.
+Therefore, we cut out these results as spurious.
+We only keep systems within a mass range of $6.5 \leq \log_{10} \text{M}_{*}(\text{M}_{\odot}) \leq 12.5$ and a star formation rate range of $-5 < \log_{10} \text{SFR} (M_{\odot}yr^{-1}) \leq 3.5$.
+Secondly, we institute a redshift cut of $z \leq 1.2$.
+This is to match the catalogue that will be later used to investigate the incidence of our sample of interacting galaxies with environment (detailed in Section \ref{data:environ}).
+Applying these cuts reduces our sample size to 3,689 interacting galaxies.
 
 \subsection{Secondary Identification}
-\noindent As stated previously, the \citet{2023ApJ...948...40O} catalogue only identified interacting galaxy systems, not individual interacting galaxies.
+\noindent As stated previously, the OR23 catalogue only identified interacting galaxy systems, not individual interacting galaxies.
 Therefore, we must find the secondary in each interaction using the COSMOS2020 catalogue.
-We achieve this by applying three steps to each system.
-First, we identify all sources within a 10" radius of our identified primary interacting galaxy.
-We then create a slice in redshift to find galaxies which are actually nearby in 3D.
-This is done using a similar parameter as that defined by \citet{Baldry et al.
-(2006)} when calculating the environment about each galaxy.
-We define the slice in redshift by $\pm\Delta$zc $= \pm1000$km/s.
+The size of the cutouts in this catalogue were also small, and therefore, the secondary did not often appear in the cutout in that project.
+To find the secondaries, we apply three steps.
+First, a cutout surrounding the primary of each system was created.
+These cutouts were from the COSMOS cutout service, selecting HST-ACS tiles as the source of the cutouts in the $F814W$ filter.
+Each cutout had a 30" radius (corresponding to 1001 $\times$ 1001 pixels) centred and was centred on the primary galaxy.
+The original OR23 cutout was also displayed next to the enlarged cutout.
+We then searched the COSMOS2020 catalogue for all sources within the cutout.
+Their positions and redshifts were recorded and used to annotate the cutout.
 
-Upon applying these two criteria, we are often only left with very few potential candidates to be the secondary interacting galaxy.
-At this stage, we then order all of our candidates by the measured 3D distance from our primary galaxy using the on-sky separation and their respective redshifts.
-The closest candidate is then used as the secondary galaxy.
-To test this method is robust, we conduct two final checks on our candidate interacting systems.
-First, for all systems we can, we look up the spectroscopic information of each.
-We find no serious change in the redshift between the photometric and spectroscopic redshifts.
-We also finally conduct a visual inspection of each candidate interacting galaxy system.
-We confirm that the potential secondary does exhibit morphological disturbance or is clearly involved in the interaction with the primary.
+We then visually assessed each annotated cutout, giving one of the four following classifications to each: system disturbed but secondary could not be identified; secondary could be identified; cannot confirm galaxy is interacting; null redshift; incorrect primary assigned.
+Our definition of a secondary galaxy was such that the secondary had to be within the cutout we were visually assessing and within $z=\pm0.1$ of the primary redshift.
+We use this cutoff as this is often used when calculating environment parameters \citep[e.g][]{Baldry 2006} or defining interacting galaxies by close pairs \citep[e.g][]{Shah et al.
+paper from 2022 / 2023} based on the uncertainties present in using photometric redshift estimates from SED fitting.
+We define a null redshift as one outwith our redshift limits or NaN.
+A minority of the cutouts we visually assessed were found to have the incorrect primary at the centre.
+This was a result of our cross matching based on radius with the COSMOS catalogue.
 
-In a few cases (N), we find that our secondary identification has failed.
-This is purely due to the secondary already merging with the primary galaxy, and therefore, not being identified as a second source or object in the COSMOS2020 catalogue.
-Later on, these will be classified as our stage 4 galaxies.
-We keep these galaxies in our sample, as they are clearly merging, merged or post-merger candidates, however do not attempt to find a secondary for them.
-Thus, our sample of 3,784 primary interacting galaxies is increased, with their secondaries, to N galaxies.
+Using these definitions, we find that of the 3,689 original systems cross-matched with COSMOS2020 2,209 could not have their secondary identified, 834 had a clear secondary, 446 could not be reliably classified as an interacting galaxy, 248 had a null redshift and 149 were the incorrect primary.
+Figure \ref{fig:secondary_selection} shows an example of each of our classifications.
+Each secondary we identify was added to our sample, increasing our sample size to 3,829.
 
-\subsection{Classifying Stage of Interaction}
-The primary purpose of this project is to compare different stages of interaction and investigate changes in their underlying photometric parameterisations.
-This will give us insights into the interplay between interaction and these underlying processes.
-Therefore, in this section we describe how we break our interacting galaxies into different stages.
+\begin{figure*}
+    \centering
+    \includegraphics[width=\textwidth]{figures/cutouts_ex.pdf}
+    \caption{An example of each visual classification made on the cross matched sample.
+From left to right these are the secondary could not be identified, the primary had a clear secondary, the primary could not be reliably classified as an interacting galaxy, the redshift was null and the incorrect primary was identified in OR+23.
+Based on these classifications, we either add the secondary galaxies to the sample or we remove the contamination from it.
+These images are 30" across using the COSMOS cutout service, selecting HST/ACS tiles as the basis for the observations in the $F814W$ filter.}
+    \label{fig:secondary_selection}
+\end{figure*}
 
-Our sample overlapping with COSMOS20202 is broken down into four different stages.
-We visually classify each system accounting for the pair separation and distortion.
-The four different stages are as follows:
+% Define our classifications above.
+While initially surprising that the majority of our systems could not have a secondary identified, we found that it was mostly due to limitations in the COSMOS catalogue or the way in which we had conducted our secondary identification.
+To define a secondary galaxy, the object had to have a ID associated with it in the COSMOS2020 catalogue.
+However, when two systems were very close together and small enough, often they would be identified under a single COSMOS ID despite being two separate systems.
+The same also occurred when two systems were merging or interacting.
+The tidal features connecting the systems would lead to only one of them being identified in the catalogue, or when two cores appeared in one merging system.
+Figure \ref{fig:secondary_selection} specifically an example of two systems being close enough together that they have been identified under a single COSMOS2020 entry.
+Figure \ref{fig:secondaries_found} shows this disparity with the different types of interaction we observe.
 
-% \vspace{-2mm}
+\begin{figure}
+    \centering
+    \includegraphics[width=0.45\textwidth]{figures/visualisation_classification.pdf}
+    \caption{Where a secondary could be identified at different stages in the interaction.
+The reasoning for such disparity in secondaries identified is due to the relative distance each the secondary would be from the primary at each stage.
+For a close pair, we often found the secondary galaxy, but a minority of these were so close together that the entire system was given a single COSMOS ID.
+The same was true for those interacting systems approaching pericentre or merging.
+When the secondary was near apocentre, often it would be outwith the cutout we were using for visual classification.}
+    \label{fig:secondaries_found}
+\end{figure}
+
+Those galaxies which were found to be contamination (i.e., could not be reliably classified as interacting or having a null redshift) were removed from our sample.
+Galaxies that could not be reliably classified as interacting were those which showed little tidal distortion and had no systems nearby with a redshift approximately that of the primary.
+Often, these were systems that were overlapping but at different redshifts, systems with irregular morphologies of spiral arms or clumpy galaxies.
+There was also many systems that were at high redshift ($z \geq 1$) where the resolution of the cutouts meant that features could not be discerned visually.
+
+Finally, we found that there were 149 systems which had been assigned to an incorrect primary.
+These were systems where the interacting galaxies were clearly in the cutout but some tidal debris or some nearby system had been assigned as the primary instead.
+This was a result of our catalogue matching based solely on separation between the OR23 coordinates and the COSMOS2020 source coordinates.
+We reassign these systems to the correct COSMOS IDs and then take them through the secondary identification process.
+
+By the end of this pipeline, we find a sample size of 3,829 interacting galaxies.
+We conduct a de-duplication based on the COSMOS2020 ID, which reduces the sample back down to 3,547 interacting galaxies.
+This shows that many of the secondaries we had identified for the different systems were already found in the OR23 catalogue.
+The remaining systems are each visually confirmed interacting and disturbed galaxies based on their morphology and photometric redshift as measured in the COSMOS2020 catalogue.
+
+\subsection{Finding Additional Systems}
+\noindent As a result of using visual classification to find the secondary galaxy in each interaction, we were able to also confirm other interacting systems which had not been found in the OR23 catalogue.
+Primarily, these extra interacting galaxies were more systems that were involved in the interactions already recorded in OR23.
+The pipeline described previously was only used to find a secondary for each interacting galaxy, however in many cases more galaxies were involved.
+Other interacting galaxies that were added here were low redshift systems which would have appeared very large in the OR23 cutout.
+Details and tidal features were then lost in the original classification process.
+By looking at the larger COSMOS2020 cutouts used here, we were able to confirm these were interacting galaxies and add them to the catalogue.
+The final set of extra systems we added were often those that were close pairs, but physically in 3D space.
+While they had little tidal disruption - what the interacting galaxies were classified on in OR23 - with the photometric redshifts to hand, we could correctly identify them here.
+
+In total, we found an extra 841 interacting systems that we could add to our sample.
+Upon conducting a de-duplication of these with the sample already found, this was reduced to 634 interacting systems.
+This gives us a total sample size of 4,181 which we use through the rest of this work.
+
+\section{METHOD: Environment, AGN and Interaction Stage}
+In this section, we describe how we separate our sample of 4,181 interacting galaxies into separate stages.
+Each stage is defined to capture a different part of the interaction, and a different part of the dynamical history of the interaction.
+We want to compare different stages in the interaction to different physical underlying processes, such as star formation rate.
+Such parameters can be found in the COSMOS2020 catalogue.
+However, two fundamental properties we also want to compare with is that of AGN fraction evolution with time and that of environment, and the impacts this might have.
+
+The parameters required to calculate the AGN fraction are not found in the COSMOS2020, and we therefore must cross match with other catalogues to find the required parameters.
+We also describe the catalogue we use here to define the density parameter around each of our sources, and define how the environment is calculated there.
+
+\subsection{Classifying Stage of Interaction}\label{sec:staging}
+The primary goal of this work is to find if a relation exists between a host of galactic parameters, underlying physical processes and the stage of the interaction.
+We, therefore, need to define different stages for them.
+We have hinted at this in the previous section with Figure \ref{fig:secondaries_found}.
+We break our sample down into four stages:
 
 \begin{itemize}
-    \item Stage 1: Well-separated with no morphological disturbance.
-    \item Stage 2: Close pairs showing strong signs of interaction.
-    \item Stage 3: Well separated pairs with evidence of disturbance.
-    \item Stage 4: Overlapping with morphological distortion.
+    \item Stage 1: Systems which are well-separated with no morphological disturbance.
+    \item Stage 2: Close pairs showing either morphological distortion or physical connection by tidal features.
+    \item Stage 3: Well separated pairs with morphological disturbance or isolated galaxies with clear tidal features.
+    \item Stage 4: Highly disturbed systems with two or more cores within.
 \end{itemize}
 
-% \vspace{-2mm}
+\noindent Examples of each stage can be found in Figure \ref{fig:stages}. Each stage is designed to capture a different part of the interaction history of a system in the total dynamical time.
 
-\noindent Each stage is designed to capture a different part of interaction, where we expect different physical processes to be dominant.
+\begin{figure}
+    \centering
+    \includegraphics[width=0.45\textwidth]{figures/examples-stages.pdf}
+    \caption{Examples of the four stages we split our interacting galaxy sample into.
+Stage 1: A close pair with confirmed redshift matching.
+Stage 2: Two distinct systems interacting with tidal features forming.
+Stage 3: A tidally disturbed system with no secondary present, likely at apocentre.
+Stage 4: A galaxy with multiple cores while highly disturbed.
+At the final stage before coalescence.}
+    \label{fig:stages}
+\end{figure}
 
-In the first stage of interaction, the two galaxies remain separated with no morphological disturbance.
-We expect this to be because the two galaxies are approaching each other and about to begin their first pericentre pass.
-Therefore, we would not expect any of the usual effects of interaction to have started.
-This stage acts, essentially, as a control on our sample.
+Stage 1 of the interaction captures the first approach of the two systems.
+This is the time when the two galaxies potentials are beginning to have an effect on one another.
+They have no morphological disturbance yet and, in our sample, are most often those galaxies with distinct disks.
+Hence, this stage has the highest number of if identified secondaries with every system having a secondary that can be visually classified.
+In this sample, we would expect no effects from the interaction to have began yet.
 
-In stage 2, we observe morphology distortion as the two galaxies have crossed their first pericentre passage.
+Stage 2 of the interaction is defined as the point where the two galaxies in the interaction are approaching or just passing the pericentre of the tidal encounter.
+For those galaxies before pericentre, we would expect the beginning of morphological disturbance or some irregularity in the two systems.
+Once the galaxies have passed pericentre, we would define it by much higher morphological disturbance, distortion and tidal debris.
+This requirement for morphological disturbance is how we differentiate stage 2 from stage 1 interacting galaxies.
+Throughout this stage of the interaction, in our sample, we see significant overlap or connection of the two systems in the form of tidal features and morphological distortion.
 
-In stage 3, we expect to have captured those galaxies which have undergone their first passage of each other and be approaching their apocentre.
-There are then three future outcomes of this.
-First, the secondary galaxy is only just approaching its apocentre, it has just passed it's apocentre, or the galaxy is about to escape from the system.
-In any case, we observe severe morphological disturbance at this point, and would expect to begin seeing the effects of interaction on the galaxy.
-The severe torques exerted on the gas should lead to some initial effects of a starburst, and there could also be some ignition of nuclear activity.
+Stage 3 interacting galaxies are described as those interacting systems where the systems have approached apocentre from each other.
+In many of cases of this stage, if the galaxies have sufficient velocity, the galaxies will escape each other and not coalesce.
+Hence, galaxies at this stage often could not have a secondary galaxy identified in our visual assessment.
+We purely describe a galaxy as stage 3 based on significant tidal and morphological disturbance.
+This stage has the highest potential for contamination by irregular galaxies or galaxies whose morphology has been disturbed by processes other than tidal interaction.
+We discuss the potential impacts of this contamination, and the limitations of using visual morphology as a proxy for stage in Section \ref{sec:limitations}.
 
-Stage 4 expects to capture those galaxies which are actually undergoing coalescence or be at the point where they are about to.
-This is, from the literature, the point we would expect all the effects of interaction to be taking place.
+Finally, stage 4 represents the final step of a galaxy interaction.
+If the two galaxies do not have sufficient velocity to escape one another, then they go on to coalesce and ultimately merge.
+We define this stage such that the sample is of galaxies just before this coalescence and the two cores remain distinct.
+However, it is important to note that this stage may be contaminated by some post-merger remnants.
+In this context, we define a stage 4 galaxy as one with significant morphological disturbance but with multiple cores present in the disks.
+At this stage, the interaction is at it's most violent with complete disruption of both galactic disks.
+We also expect star formation rate to increase significantly in this stage.
+This is important to note, as high star forming at specific redshifts in the $F814W$ filter may appear like a second core within a galactic disk.
+At this point, we would be observing a post-merger remnant rather than the point just before coalescence.
+Therefore, to mitigate potential contamination in from the post-merger stage we only classify stage 4 galaxies as those with highly disrupted disks and second cores close to the primary core (and not far out in the disk).
 
-The categorisation was conducted by the co-authors of this paper (names).
-Initially, 300 samples from the COSMOS sample are classified together, to reduce biases from the group and then split between the group evenly.
-This leads to 4,385 classifications being made by each co-author.
-To further quantify the bias and error involved in using different classifiers, a further 20 galaxies were classified as a group followed by each member of the group classifying individually the same 80 galaxies.
-The results of this is shown in Figure \ref{fig:std-dev-clsf}.
-It is important to note here, that the two stages with highest disagreement between classifiers is stages 1 and 4.
-\textcolor{red}{Explain why this could be?}
+Our four stage approach is not a new one, and many other works have utilised it to differentiate different parts of the dynamical history of a galaxy interaction \citep{}.
+It is, however, important to note its limitations.
+First, this is a simplified view of the dynamical timescale of an interaction.
+We have assumed that an interaction begins, the pair have enough velocity to escape or they coalesce and that is representative of the full dynamical timescale.
+We have not considered systems where there are multiple flybys before coalescence or systems where there are multiple members at different stages of the interaction.
+This is a particular concern when looking at stages 2 and 3.
+For instance, the effects could be enhanced or diminished over multiple flybys, and we have no way to capture this.
+
+However, with these simplifications in our assumptions, we will investigate the parameters which are proxies for the underlying physical processes and interpret them.
+We will investigate the whether we see have a bias in our systems based on environment, whether we find increased AGN activity and if we observe enhancement in star formation with stage.
+The star formation rate is already present in the COSMOS2020 catalogue from both EAzY and LePhare.
+For the environment parameter and whether AGN are detected, we cross match to two further catalogues.
+We describe these catalogues here, our process of cross matching and the new sample sizes we have in each subsample.
+
+\subsection{Matching to Environment Catalogue}\label{data:environ}
+\noindent There is no measure of the environmental density in the COSMOS2020 catalogue.
+Such a measure is often calculated in numerous ways, such as the N-nearest neighbour \citep{2006MNRAS.373..469B}, different Bayesian metrics \citep{2008ApJ...674L..13C} or estimating it from Voronoi Tesselation \citep{2021inas.book...57V}.
+However, in this work, we utilise the existing environmental density catalogue produced by \citet{2017ApJ...837...16D}.
+This catalogue was created specifically for the COSMOS survey, and has a measured density for all sources with mass $\log(\frac{M}{M_\odot}) \geq 9.6$ and out to a redshift of 1.2.
+In this catalogue, they calculate not only the density, but also the density parameter $\delta$ and assign each source to a field, filament or cluster classification.
+For a full description of how they calculate the environment and density field see \citet{2015ApJ...805..121D} and \citet{2017ApJ...837...16D}, but we will briefly describe it here.
+
+To build the density field throughout the COSMOS field, they first construct a set of overlapping redshift slices.
+Within each slice, a subset of the galaxies are selected such that the median of the probability distribution function (PDF) of their photometric redshift is within it.
+Then, from this subset, they calculate the weighted surface density within the redshift slice.
+The weighting is based upon the PDF of the photmetric redshift present within the redshift slice.
+These weights significantly reduce the effects of projection effects.
+They then apply a weighted adaptive kernel smoothing using a 2D Gaussian kernel whose width changes based on the found local density of galaxies.
+Once this density field is created, the density around the sample galaxies can simply be interpolated across the density field based on the angular position and the redshift slice the sample galaxy is in (based on its photometric redshift PDF).
+
+The result of this process, and the cuts defined previously, is a catalogue of $\approx$45,000 galaxies with their densities accurately measured.
+As advised with the catalogue, we remove any sources which are flagged as uncertain.
+This is recorded in the catalogue.
+This leaves us with $\approx$39,000 sources with which to cross match the OR23 sample.
+We apply the same cuts to our sample as applied in \citet{2017ApJ...837...16D}, and only consider those systems with a mass $\log(\frac{M}{M_\odot}) \geq 9.6$.
+To cross match with our sample, we simply utilise the COSMOS2015\_ID which is recorded in the COSMOS2020 catalogue which corresponds to the ID in the \citet{2017ApJ...837...16D} catalogue.
+We find that every source in our COSMOS2020 sample has a COSMOS2015 ID associated with it, and therefore we fully match the reduced catalogue.
+
+Upon applying the mass cut to our sample, we find that we are matching 2,800 sources to the \citet{2017ApJ...837...16D} catalogue.
+Upon matching based upon the COSMOS2015 ID, we find that 628 sources in our sample do not exist in the environment catalogue.
+This reduces our sample to 2,172 galaxies with confirmed and reliable environment density measurements.
+
+\subsection{Classifying AGN}
+\noindent We will also investigate the affect of interaction stage upon the AGN activity within the galaxies involved.
+Unfortunately, the outputs of EAzY and LePhare do not provide us with photometric estimates of the line fluxes needed to define an AGN on a Baldwin, Philips and Terlevich (BPT) diagram \citep{}.
+Therefore, we cannot directly identify if a galaxy is only star forming, has nuclear activity or is a composite.
+So, we turn to cross-matching our sample to three different catalogues which contain the required information.
+We use the Chandra COSMOS Legacy Survey Multiwavelength Catalogue \citep{2016ApJ...817...34M} and the COSMOS VLA 3GHz survey \citep{2017A&A...602A...6S, 2017A&A...602A...3D}.
+In these catalogues an AGN, star forming or composite classification is given within the catalogue.
+
+Again, our cross match process is very much the same as previously described.
+We use the previously identified COSMOS2020 source coordinates and conduct a radial search of 10".
+If more than one source is within this radius, we match on the closest source.
+The two catalogues derived from the COSMOS survey do not contain IDs which overlap with the COSMOS2020 catalogue, therefore we must do it based on coordinates.
+We conduct our matching in serial, starting from the \citet{2017A&A...602A...6S} catalogue and then to the Chandra survey.
+At every step, if we find a match in the relevant catalogue, we remove it from subsequent searches in other catalogues and take the first classification as the correct one.
+
+Applying our matching criteria, we find 1,059 classifications in the VLA 3GHz survey and 155 in the Chandra survey.
+These were split into 812 star forming galaxies and 402 AGN.
+We also investigate cross matching with the MPA-JHU catalogue \citep{2003MNRAS.341...33K, 2004MNRAS.351.1151B, 2007ApJS..173..267S}, however, found that all matches were already represented by the VLA and Chandra surveys.
+Therefore, we only utilise these two catalogues in our sample.
+
+While the ratio of AGN to star forming galaxies in our sample seems large compared to other works, it is important to note that this is a result of limited matching between the catalogues.
+Of the 4,182 galaxies in our sample, only 1,214 appeared at all in either the VLA or Chandra catalogues.
+Any galaxy which did not appear in these catalogues, we discard as unclassified.
+Therefore, we require these catalogues to specifically show us if a galaxy is star forming or not before we classify it as such.
+This is why our number of star forming galaxies is lower than expected.
+We discuss this limitation in section \ref{sec:limitations} and the effect it may have on our results of AGN fraction evolution with stage.
 
 \section{Results \& Discussion}\label{results}
- - Show breakdown of stages. \\
- - What are their mass distributions? \\
- - Mass Ratios \\
- - Investigate SF with Mass \\
- - Investigate SF with Mass Ratio/Merger Type \\
- - Investigate SF with projected Separation \\
- - Control for Environment \\
- - Where do the interacting galaxies lie? \\
- - What does this all mean?
+\noindent With our samples selected, and numbers throughout known, we can begin to investigate teh change in multiple parameters with stage of the interaction.
+As stated previously, the four stages of interaction are designed to capture the main different parts of galaxy interaction.
+First, we show the results of breaking down our sample into stages with relation to the star formation and mass of our sample.
+We investigate the differences between these distributions and interpret what underlying physical processes could be occurring to show these differences.
+We show that the results we have found could not be due to other effects, like different environments affecting our selection etc.
+We then this up by discussing the changing AGN sample that we see, discuss selection effects and discuss the potential underlying processes responsible for our results.
+
+Finally, to put this in more context with the literature, we break our sample down further into correctly identified pairs and mergers.
+We use this subsample to explore the relationship between the galactic parameters previously discussed, and the mass ratio and projected separations of the systems.
+We show that this agrees with previous works, and how this lends legitimacy to our results with different stages of interaction.
+
+\subsection{Star Formation Rate with Stage}
+
+\subsection{Controlling for Galactic Environment}
+
+\subsection{Nuclear Activity with Stage}
+
+\subsection{Star Formation and Mass Ratio}
+
+\subsection{Star Formation and Projected Separation}
+
+\subsection{Comparison to Other Works}
+
+\section{Limitations of Approach}\label{sec:limitations}
+\subsection{Redshift Effects on Visual Classification}
+\noindent An important limitation of our visual approach is related to the effect of tidal features out to higher redshifts.
+As the redshift increases, surface brightness dimming of the systems may lead to a lack of visual confirmation in the tidal features of different objects.
+Thus, if we were heavily affected by this in our redshift range ($0.0 \leq z \leq 1.2$), we would see distinct signs of it in our selection function of our mergers.
+For instance, if all of our stage 4 classifications were actually high redshift stage 3 galaxies, we would observe this in our selection function.
+Therefore, Figure \ref{fig:redshift_selection} shows our selection functions across our redshift range for each defined stage in our interaction.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.45\textwidth]{figures/stage-selection.pdf}
+    \caption{Redshift vs Mass distribution for each stage of interaction we have defined.
+This is important as we use tidal distortion and the existence as tidal features as a fundamental for our classification methodology.
+As shown here, the distribution of systems across redshift and mass is consistent for all stages in our sample.
+Therefore, we are likely not affected by this in our analysis.}
+    \label{fig:redshift_selection}
+\end{figure}
+
+As shown, the distribution of masses across redshift that we find in our sample is reasonably consistent with each other.
+This means we are likely not affected by surface brightness dimming across our sample and our redshift range.
+
+\subsection{Selection Effects in AGN Sample}
+
+\subsection{Limitations of Visual Classification}
 

### 2023-11-23 paper-source/main.tex
Major additions to paper source. Got new SF classifications. Beginning update of KS tests.

@@
 \usepackage{hyperref}
-% \usepackage{enumitem}
+\usepackage{enumerate}
 
@@
 \begin{itemize}
-    \item Stage 1: Systems which are well-separated with no morphological disturbance.
+    \item Stage 1: Systems which are well-separated with little to no morphological disturbance.
     \item Stage 2: Close pairs showing either morphological distortion or physical connection by tidal features.
@@
 We use the Chandra COSMOS Legacy Survey Multiwavelength Catalogue \citep{2016ApJ...817...34M} and the COSMOS VLA 3GHz survey \citep{2017A&A...602A...6S, 2017A&A...602A...3D}.
-In these catalogues an AGN, star forming or composite classification is given within the catalogue.
+Each source has an AGN, star forming or composite classification is within the catalogue.
+
+% Need a small paragraph here about these two catalogues and their differences.
 
@@
 
-\section{Results \& Discussion}\label{results}
-\noindent With our samples selected, and numbers throughout known, we can begin to investigate teh change in multiple parameters with stage of the interaction.
+\section{STAR FORMATION EVOLUTION WITH INTERACTION STAGE}\label{results}
+\subsection{Controlling for Interaction Stage}
+\noindent With our samples selected we investigate the change in multiple parameters with stage of the interaction.
 As stated previously, the four stages of interaction are designed to capture the main different parts of galaxy interaction.
 First, we show the results of breaking down our sample into stages with relation to the star formation and mass of our sample.
-We investigate the differences between these distributions and interpret what underlying physical processes could be occurring to show these differences.
-We show that the results we have found could not be due to other effects, like different environments affecting our selection etc.
-We then this up by discussing the changing AGN sample that we see, discuss selection effects and discuss the potential underlying processes responsible for our results.
+We utilise the estimates of these parameters that exist in the COSMOS2020 catalogue itself.
+We have the option to use either the measured estimates from LePhare or EAzY.
+We opt to use the stellar mass measured from LePhare and the star formation rate measured with EAzY for our final results.
+We choose this as using any other combination reveals the degeneracys of the SED template fitting conducted in either of the underlying softwares.
+Figure \ref{fig:difference-measures} shows how the two measures differ from each other.
+As shown, EAzY measures larger stellar masses compared to LePhare while the scatter in SFR is very large.
 
-Finally, to put this in more context with the literature, we break our sample down further into correctly identified pairs and mergers.
-We use this subsample to explore the relationship between the galactic parameters previously discussed, and the mass ratio and projected separations of the systems.
-We show that this agrees with previous works, and how this lends legitimacy to our results with different stages of interaction.
+\begin{figure}
+    \centering
+    \includegraphics[width=0.45\textwidth]{figures/mass-sfr-scatter.pdf}
+    \caption{Comparison of the measures of stellar mass and SFR using either LePhare or EAzY photometric codes to calculate them.
+\textit{Left}: The scatter in the stellar masses between softwares.
+As shown, EAzY often seems to find larger stellar masses when compared to LePhare.
+\textit{Right}: Scatter in SFRs when measured with LePhare or EAzY.
+There is a large difference between the measures of LePhare and EAzY here, and therefore we opt to only use EAzY measures of the SFR through this work.}
+    \label{fig:difference-measures}
+\end{figure}
 
-\subsection{Star Formation Rate with Stage}
+As the measure of the masses between the softwares is similar, we can interchange which mass we use in these measurements.
+However, with the very large scatter of the SFRs between the softwares, we opt to only use the EAzY measurement.
+% Where do these differences come from?
+What potential impact could this have on our results?
 
-\subsection{Controlling for Galactic Environment}
+With the measures of stellar mass and SFR selected, we break down our sample into their different stages.
+Figure \ref{fig:sfr-mass} shows the breakdown of these parameters with stage.
+On a population scale, there is clear evolution in the star formation rate from stage 1 through to stage 4.
+In stage 1, where the galaxies are distinct from one another with no clear morphological disturbance, we clearly see two populations of galaxies.
+These are the blue, star-forming and red sequences.
+The contours of number density in Figure \ref{fig:sfr-mass} bring out this population.
+In stage 2, when the galaxies are at pericentre, this red sequence remains but is highly diminished while the star forming sequence remains constant.
+Stage 3 shows a similar effect, where the red sequence reduces again before finally in stage 4 the red sequence completely disappears.
 
-\subsection{Nuclear Activity with Stage}
+\begin{figure}
+    \centering
+    \includegraphics[width = 0.45\textwidth]{figures/sfr-mass-stages.pdf}
+    \caption{The LePhare stellar mass against the EAzY SFR across the different stages of the interaction.
+The blue contours are 8 levels of density of the underlying populations in each frame.
+\textit{Top left}: The stellar mass and star formation rate of Stage 1 of our sample.
+Here, the interacting galxies are simply close pairs with little to no morphological disturbance.
+There are clearly two populations here: a main, star forming sequence forming the main population and a smaller red sequence.
+\textit{Top right}: Stage 2 of the interaction, where the two interactors are close to pericentre.
+The star forming sequence remains, but the red sequence is reduced significantly.
+\textit{Bottom left}: Stage 3 of the interaction, where the interactors are close to apocentre or escaped.
+Here, we see the almost complete disappearance of the red sequence.
+\textit{Bottom Right}: Stage 4 of the interaction, where the two systems are close to coalescence or have merged.
+The red sequence of galaxies has completely disappeared.}
+    \label{fig:sfr-mass}
+\end{figure}
 
+However, this result could also be due to many other factors rather due to interaction stage.
+For instance, if the mass distribution of our sources evolves as well, it could just be that we are selecting higher mass systems in stage 4 when compared to stage 1.
+This would have the result of systems in stage 4 having, on average, higher SFRs than those in stage 1 and appearing like we had evolution in the star forming population with stage.
+Another effect that could cause this relation to appear would be our selection was highly dependent on galactic environment.
+It is well known that environment and star formation are closely linked, and that classifying interacting galaxies by morphology classifiers can weight up the cluster environment over galaxies in the field.
+In Section \ref{sec:env-cont}, we control for the environment in our sample and show that this is not an issue.
+Here, we investigate the question of the evolution of the mass distribution that could give us this result.
+
+We can quantify the similarity of the mass distributions, and then the SFR distributions, using well known statistical tests.
+We opt to use two different tests: the KS-test and the Shapiro-Wilkes test.
+The KS-test is excellent at comparing different weighted distributions to each other, while the Shapiro-Wilkes test compares these distributions to other well known functions (in our case, the normal function).
+Thus, by weighting the mass distributions and using a KS-test, we will be able to quantify how alike the mass distributions are and then compare this to the weighted distribution of the SFRs.
+The weighting scheme we utilise normalises the distributions such that each bin in the distribution had the same number of sources within it.
+Therefore, any bins with few than the average number of sources will be weighted up while those bins with more will be weighted down.
+These weights applied to the mass distribution are then applied to the SFR distribution so the counts in each bin are, essentially, the same.
+
+\begin{figure}
+    \centering
+    \includegraphics[width = 0.45\textwidth]{figures/stellar-mass-dist.pdf}
+    \caption{The stellar mass distribution across the four stages. Each bin is weighted to have equivalent counts within them.}
+    \label{fig:weighted-mass}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.45\textwidth]{figures/sfr-dist.pdf}
+    \caption{SFR distribution weighted by mass across each stage.}
+    \label{fig:weighted-sfr}
+\end{figure}
+
+Figure \ref{fig:weighted-mass} shows the weighted mass distributions through the four different stages.
+These appear highly similar, and we conduct Kolmogorov-Smirnov \citep[KS-test;][]{an1933sulla} and Anderson-Darling \citep[AD-test;][]{AD_paper} tests to compare each distribution.
+In each test, we calculate the value of the KS test and a p-value which is the probability that each distribution is drawn from the same parent distribution.
+For each mass distribution, we find that p-value of the KS test is approximately one.
+Thus, it is not unreasonable to assume that the galaxies between each of our samples are drawn from the same parent sample and are very similar.
+Figure \ref{fig:weighted-sfr} shows the SFR distributions while being weighted and controlled for mass.
+When comparing stages 1 and 2, 1 and 3, 1 and 4, 2 and 4 and 3 and 4, the p-values are $\ll$0.05.
+Thus, we can reject the null hypothesis for these distributions and assume they are from different parent samples and are not identical.
+However, for comparing stages 2 and 3, the p-value of the KS test is $\approx$0.90.
+Thus, while these distributions are likely to be not identical, they are very similar in the parent sample they have been drawn from.
+\textbf{Thus, for the same mass distribution through each stage of interaction, the star formation distribution radically changes from stage 1 to stage 2 and from stage 3 to stage 4, while remaining reasonably similar from stage 2 to stage 3.}
+
+Putting this result into the context of the dynamical timescale of an interaction, it shows there are three separate stages star formation evolution in these systems.
+The first is the change from isolated SFRs to interacting SFRs.
+Here, the SFR between galaxies which are close pairs and those that are at pericentre are radically different.
+This difference persists through to stage 3 - where the galaxies are at pericentre in the interaction.
+The SFR distribution remains approximately the same between these two, meaning the forces that drive and affect star formation remain equivalent between these two stages.
+Finally, the SFR radically changes again when we approach the merging or post-merger stage of the interaction.
+We can also say that this change is likely an enhancement in the SFR of the galaxies through the interaction due this change being driven by the disappearance of the red sequence through each stage.
+
+We also control for redshift in our examination of this result.
+While the red sequence is significantly reduced across stage, it is important that we put this into the context of the star forming main sequence of galaxies.
+We expect that, due to an interaction, the population of starbursting and quiescent galaxies will change with stage.
+Therefore, we define a star forming main sequence through across redshift.
+This allows us to classify each source based on its SFR independently of redshift.
+To define the star forming main sequence (SFMS), we follow the example of \citet{2019MNRAS.484.4360A}.
+There, they define the star forming main sequence as a function of galactic stellar mass and redshift as
+
+\begin{equation}
+    \log \text{SFR}_{\text{MS}}(z)[M_\odot yr^{-1}] = -7.6 + 0.76\log\frac{M_*}{M_\odot} + 2.95\log(1+z).
+\end{equation}
+
+\noindent This finds the expected, main sequence, SFR of a galaxy at a given stellar mass, $M_*$, and redshift, z.
+
+The ratio of the measured galaxy SFR and the expected main sequence SFR is then taken. We then use this fraction to classify each galaxy into distinct bins. These are:
+
+\begin{enumerate}[(i)]
+    \item Starburst galaxies. Here, the galaxy SFR is highly elevated compared to the SFMS. We follow \citet{2019MNRAS.484.4360A} and define a cutoff of $\log$SFR/SFR$_{\text{MS}} >$ 0.4.
+    \item Main sequence galaxy. The galaxy is within 0.4 dex of the SFMS and approximately has the expected SFR. Defined as $-0.4 < \log$SFR/SFR$_{\text{MS}} < 0.4$.
+    \item Sub-main sequence galaxy. A galaxy whose SFR is below the majority of the SFMS, but likely not quiescent. Defined as $-1.3 < \log$SFR/SFR $_{\text{MS}} < $ -0.4.
+    \item Quiescent (High) galaxy. A galaxy with an SFR in the top $\approx$50\% of the quiscent galaxy population. Defined as $-2.3 < \log$SFR/SFR $_{\text{MS}} <$ -1.3.
+    \item Quiescent (Low) galaxy. A galaxy with low SFR and very likely completely quenched. Defined as $\log$SFR/SFR $_{\text{MS}} <$ -2.3.
+\end{enumerate}
+
+\noindent We split our sample into its different stages and apply these criteria.
+Figure \ref{fig:sfr-clsf} shows the ratio between the expected SFMS SFR and the found SFR in COSMOS.
+This clearly shows a large increase in galaxies classified as starburst from stages 1 to 4 and a large reduction in the number of quenched systems.
+Figure \ref{fig:sfr-clsf-bar} shows the change in fraction of the different galaxy classifications through stage.
+These Figures reflect the results found in Figure \ref{fig:sfr-mass}.
+Initially, in stage 1, we find that the majority of our galaxies lie on the SFMS or just below it.
+There also exists a small population of galaxies which are classified as a starburst with a population of quiescent galaxies that is roughly double the fraction.
+As we move through the interaction stage, we see that the quiescent galaxy fraction gradually decreases to the point of almost non-existence in stage 4 galaxies.
+The complete inverse is true in our starburst fraction.
+We find that this almost quadruples in the fraction of our sample over the course of the different stages of interaction.
+The fraction of galaxies on the SFMS remains dominant throughout, however, we do find the fraction of sub-MS galaxies significantly reduced.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.45\textwidth]{figures/sfr-clsf-dist.pdf}
+    \caption{Stellar mass against the ratio of measured SFR to the expected SFR if the galaxy was on the SFMS.
+Black points are the individual sources, while the blue contours are as in Figure \ref{fig:sfr-mass}.
+The red dotted lines show the cutoffs for different galaxy classifications based on their SFR, with each cut off being defined by the text in blue.
+We find that through interaction stage, the quiescent galaxy population significantly reduces while the starburst population rapidly increases.
+As these cutoffs are also dependent on redshift, we find that this evolution in SFR with interaction stage is independent of redshift.}
+    \label{fig:sfr-clsf}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.45\textwidth]{figures/sfr-clsf-bar.pdf}
+    \caption{The change in fraction of different galaxy classifications from the fraction of SFR to the expected SFR on the SFMS.
+While galaxies on the SFMS remain dominant through each sample across interaction stage, there is significant change in the starburst and quiescent populations.
+The starburst galaxy population moves from being roughly half the size of the quiescent population in stage 1 to completely dominating it in stage 4.
+This is occurring while the quiescent population is significantly reduced to almost non-existence in stage 4.}
+    \label{fig:sfr-clsf-bar}
+\end{figure}
+
+% So, what does this all mean?
+Thus, we find that throughout the different stages of interaction the star formation within the systems is being driven upwards.
+This is not an unexpected result.
+It has long been known that the SFRs of merging and post-merging galaxies is increased with respect to control samples of galaxies within the field \citep{papers saying this}.
+However, what we have found here is that this process of increasing SFR and galaxies being driven to starburst begins from the pericentre of the first interaction.
+Simulations have long showed that there is a peak in SFR initially in an interaction, followed by a slow reduction to a final enhanced level in the post-merger stage \citep{papers saying this}.
+However, due to the initial starburst, it is often shown that the gas within the galaxy is either quickly used up and the galaxy quenches or it is heated to the point that star formation becomes very inefficient.
+Thus, what we would expect to see here is that stages 2 and 4 would have the highest fractions of galaxies undergoing a starburst and the smallest quiescent fractions.
+
+Our work here is found to be correct by both simulations and previous works on when the starburst occurs in an interacting galaxy.
+We observe significant change in the starburst and quiescent fractions from stage 1 to 2 and stage 3 to 4.
+Thus, the initial part of the interaction appears to have a significant impact on the SFR (and, therefore, the gas content) of the galaxies involved.
+This enhanced star formation then persists through the interaction, even when the other galaxy approaches the apocentre of the interaction.
+This is seen by the relatively little change in the SFR classifications from stage 2 to 3.
+While the fraction of MS galaxies does increase slightly, the fraction of starburst galaxies remains essentially constant.
+There is also no major change in the quiescent fraction either.
+However, it is interesting to note that the sub-MS fraction does decrease.
+Thus, the transition to stage 2 to stage 3 of an interaction may bring with it slight enhancement in the SFR, but not on the scale of the other transitions in interaction stage.
+We then see clear evidence for a second starburst is being driven by the merging of the systems that goes beyond even the enhanced from the initial pericentre passage.
+
+So, what does the SFR evolution look like from our results?
+As the interactors approach each other, they are representative of a control sample where there is a population of quiescent, MS and starburst galaxies.
+However, upon transitioning from stage 1 to 2, the disturbance due to interaction provokes increased fragmentation of a galaxies gas and leads to an increase in star formation.
+This is true even of the galaxies which have very little gas remaining, as the quiescent fraction reduces significantly in our sample.
+This enhancement persists from stage 2 to stage 3, where we see no major change in the classification fractions.
+Then, upon merging and transitioning to stage 4, we find that even the most gas-empty galaxies begin forming stars quickly.
+
+Now, it is important to note the parameter space that we are searching in these examples.
+We are probing major interactions between galaxies, where the resultant tidal features that form would be classifiable in an image.
+It is well know that the mass ratio of an interaction takes an important role in the enhancement of star formation \citep{papers about major interaction}, and we are probing the most extreme examples.
+Hence, even those mergers which are considered dry - with very little gas - would be capable of driving major rejuvenation in the star formation of these systems.
+To conclude, \textbf{we find clear, statistically robust evolution of a galaxys' SFR with interaction stage.
+The SFR changes dramatically from stage 1 to 2 and stage 3 to 4 - at the pericentre and coalescence of the interaction.
+Existing simulations of galaxy interactions support this interpretation of when star formation changes.}
+
+\subsection{Controlling for Galactic Environment} \label{sec:env-cont}
+\noindent While we have found clear evidence of evolution in the SFR of interacting galaxies with stage, it is important we remove a potential source of contamination.
+It is well known that the environment has a direct impact on the observed SFR of galaxies.
+A galaxy in a cluster environment has, on average, a higher SFR than those in the field \citep{Papers on environment with SFR}.
+Thus, if any of our stage classifications are biased towards one environment or another, it could have severe consequences for our results.
+Therefore, we utilise the existing COSMOS envrionment catalogue described in \citet{2017ApJ...837...16D} to ensure there are no environmental biases in our staging.
+
+Upon applying the matching described in Section \ref{data:environ}, we break our samples into different environment measures with stage.
+Figure \ref{fig:dens-stage} shows the distribution of our matched samples with their density values.
+It is important to note that \citet{2017ApJ...837...16D} has a higher mass cutoff than we have implemented in our underlying sample.
+Therefore, this is showing the density of all systems $\log$M$_*$/ M$_\odot \geq$ 9.6.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.45\textwidth]{figures/density-stage.pdf}
+    \caption{The density about each of our sources matched with the \citet{2017ApJ...837...16D} catalogue.
+As shown, there is no existing bias in the distribution of galactic environments throughout our stages.
+This is confirmed by performing KS- and AD-tests.
+Therefore, we can conclude that the shown evolution in SFR with interaction stage is not due to environmental effects.}
+    \label{fig:dens-stage}
+\end{figure}
+
+\section{Nuclear Activity with Interaction Stage}
+\subsection{Controlling for Stage}
+
+\section{Characteristics of Matched Pairs}
 \subsection{Star Formation and Mass Ratio}
@@
 \subsection{Star Formation and Projected Separation}
-
-\subsection{Comparison to Other Works}
 
@@
 \subsection{Limitations of Visual Classification}
+
+\subsection{Selection Effects of SFR Sample}
 

### 2023-11-24 paper-source/main.tex
Updated mass and SFR weightings. Updated paper with beginning AGN section.

@@
 
-\subsection{Classifying AGN}
+\subsection{Classifying AGN}\label{sec:agn-clsf}
 \noindent We will also investigate the affect of interaction stage upon the AGN activity within the galaxies involved.
@@
     \includegraphics[width = 0.45\textwidth]{figures/stellar-mass-dist.pdf}
-    \caption{The stellar mass distribution across the four stages. Each bin is weighted to have equivalent counts within them.}
+    \caption{The stellar mass distribution across the four stages. Each bin is weighted based on the counts in the smallest sub-sample in stage. This is stage 4 of interaction.}
     \label{fig:weighted-mass}
@@
     \includegraphics[width=0.45\textwidth]{figures/sfr-dist.pdf}
-    \caption{SFR distribution weighted by mass across each stage.}
+    \caption{SFR distribution weighted by mass across each stage. This weighting is based on our sample of stage 4.}
     \label{fig:weighted-sfr}
@@
 Thus, if any of our stage classifications are biased towards one environment or another, it could have severe consequences for our results.
-Therefore, we utilise the existing COSMOS envrionment catalogue described in \citet{2017ApJ...837...16D} to ensure there are no environmental biases in our staging.
+Therefore, we utilise the existing COSMOS environment catalogue described in \citet{2017ApJ...837...16D} to ensure there are no environmental biases in our staging.
 
@@
 
+We conduct weighted KS and AD tests on the environment distributions, and confirm they are likely drawn from the same parent sample.
+The resultant p-values are $\approx$1 when comparing between the distributions.
+Thus, there are no biases in our stage selection with environment, and it fair to assume that the evolution in the SFR with stage is due to interaction, not environment.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.45\textwidth]{figures/sfr-mass-density.pdf}
+    \caption{The distribution of environment classifications through our sample.
+This is only for sources with a $\log$M$_*$ / M$_\odot \geq$ 9.6.
+However, from this subsample, we see that there is no trend with environment and that the distribution is random throughout each stage.
+Therefore, the effects of increasing SFR with interaction stage is not due to environmental effects.}
+    \label{fig:dens-sfr-mass}
+\end{figure}
+
+Figure \ref{fig:dens-sfr-mass} shows the environment classification in our reduced stellar mass-SFR distribution.
+This shows that there is no ordered structure, or bias, in our sample with environment and further reinforces that the galactic environment is not responsible for our proposed SFR evolution with stage.
+The majority of our sample lie either within filaments or in the field.
+The environment which would have the most effect upon the SFRs of our sample is a cluster environment.
+However, the fraction of our sample within a cluster is never greater than 10\%.
+It is important to note, however, that the galaxies most likely to lie in a cluster in our sample would be lower mass galaxies.
+However, these systems are not found in the red sequence where we see the most change in SFR due to interaction.
+Therefore, the lack of information here does not have a large impact on this measurement.
+
 \section{Nuclear Activity with Interaction Stage}
 \subsection{Controlling for Stage}
+\noindent We now cross match our sample with the two AGN catalogues and methods described in Section \ref{sec:agn-clsf}.
+This gives a sample of 1,284 AGN and star forming galaxies (SFGs) to cross match with the stage.
+Figure \ref{fig:agn-stage} shows distribution of stellar mass to SFR with stage, with the confirmed AGN and SFG marked.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.45\textwidth]{figures/agn-stage-dist.pdf}
+    \caption{The distribution of AGN through stage with SFR and stellar mass.}
+    \label{fig:agn-stage}
+\end{figure}
 

### 2023-11-29 paper-source/main.tex
Major update to finding weighted AGN fraction. Also added to paper and lots of projected separation stuff. Paper nearly there, just gotta write a discussion and conclusion.

@@
 Previous works focused on simulations find that a sudden increase in star formation occurs early in the dynamical timescale of the interaction \citep{2008MNRAS.384..386C, 2019MNRAS.490.2139R}, however, confirming this definitive link observationally remains elusive \citep{2023arXiv230916531R}.
-The same studies could also be done for nuclear activation as well as quenching of interacting systems \citep{Papers on nuclear activation}.
+The same studies could also be done for nuclear activation as well as quenching of interacting systems \citep{2011MNRAS.418.2043E, 2018PASJ...70S..37G, 2023ApJ...942..107S}.
 While we cannot yet directly measure when in the dynamical timescale star formation is enhanced from observations, we can approximate it by splitting different interactions into different stages.
@@
 This paper is laid out as follows in Section \ref{data} we explain the OR23 and COSMOS catalogues, and describe the process of catalogue matching especially focused on accurate de-duplication and cross-matching selection from the different catalogues.
-Section \ref{staging} describes the methods by which we split the interacting systems into their different stages, and how we identify the secondary galaxies to each identified interacting galaxy.
+Section \ref{method} describes the methods by which we split the interacting systems into their different stages, and how we identify the secondary galaxies to each identified interacting galaxy.
 We also discuss our processes of calculating projected separations.
@@
 
-\subsection{Secondary Identification}
+\subsection{Secondary Identification}\label{sec:sec-ident}
 \noindent As stated previously, the OR23 catalogue only identified interacting galaxy systems, not individual interacting galaxies.
@@
 Our definition of a secondary galaxy was such that the secondary had to be within the cutout we were visually assessing and within $z=\pm0.1$ of the primary redshift.
-We use this cutoff as this is often used when calculating environment parameters \citep[e.g][]{Baldry 2006} or defining interacting galaxies by close pairs \citep[e.g][]{Shah et al.
-paper from 2022 / 2023} based on the uncertainties present in using photometric redshift estimates from SED fitting.
+We use this cutoff as this is often used when calculating environment parameters \citep[e.g][]{2006MNRAS.373..469B} or defining interacting galaxies by close pairs \citep[e.g][]{2022ApJ...940....4S} based on the uncertainties present in using photometric redshift estimates from SED fitting.
 We define a null redshift as one outwith our redshift limits or NaN.
@@
 
+Each of the galaxies that have a confirmed secondary will be used in measuring effects of projected separation with star formation and AGN fraction.
+Therefore, we must define a control sample by which to compare to.
+We find these control galaxies from the COSMOS2020 catalogue.
+All galaxies within 0.01 dex of our sub-samples' stellar mass are selected from the catalogue, and within a $\pm$0.01 redshift slice.
+We then order the control galaxies to be whichever system is furthest from our target.
+Each control galaxy is then visually confirmed to be non-interacting and in isolation.
+We also confirm that it does not already exist in the catalogue, and ensure there is no duplication in the control sample.
+Figure \ref{fig:matched-distributions} shows the mass distribution of our paired sub-sample of galaxies and their control, showing a closely similar mass distribution.
+With the previously defined cuts, we find a control galaxy for all but one of our galaxies with a confirmed secondary.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.45\textwidth]{figures/mass-matching-pairs.pdf}
+    \caption{The mass distribution of the paired interacting galaxy sample and the control sample.
+Both primary and secondary galaxies are within this distribution.
+From our sample of 4,135 interacting galaxies morphologically identified, 960 are confirmed galaxy pairs.
+This means that the secondary in the interacting galaxy system has been identified from morphology and photometric redshifts.}
+    \label{fig:matched-distributions}
+\end{figure}
+
 \subsection{Finding Additional Systems}
@@
 
-\section{METHOD: Environment, AGN and Interaction Stage}
+\subsection{Redshift Effects on Visual Classification}
+\noindent There are two limits when using visual morphology to find interacting galaxies.
+The first is the limitation of being able to characterise tidal features with increasing redshift.
+As the redshift increases, surface brightness dimming of the systems may lead to a lack of visual confirmation in the tidal features of different objects.
+Thus, if we are heavily affected by this in our redshift range ($0.0 \leq z \leq 1.2$), we would see distinct signs of it in our selection function of our mergers.
+For instance, if all of our stage 4 classifications were actually high redshift stage 3 galaxies, we would observe this in our selection function.
+Therefore, Figure \ref{fig:redshift_selection} shows our selection functions across our redshift range for each defined stage in our interaction.
+As shown, the distribution of masses across redshift that we find in our sample is reasonably consistent with each other.
+This means we are likely not affected by surface brightness dimming across our sample and our redshift range.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.45\textwidth]{figures/stage-selection.pdf}
+    \caption{Redshift vs Mass distribution for each stage of interaction we have defined.
+This is important as we use tidal distortion and the existence as tidal features as a fundamental for our classification methodology.
+As shown here, the distribution of systems across redshift and mass is consistent for all stages in our sample.
+Therefore, we are likely not affected by this in our analysis.}
+    \label{fig:redshift_selection}
+\end{figure}
+
+The second issue that could affect our sample is that of contamination by close pairs by projection effects rather than by galaxies which are physically close together.
+For the majority of these systems, we are limited to only having their calculated photometric redshift from the COSMSO2020 catalogue and not their well-constrained spectroscopic redshift.
+As we are conducting visual classification, this issue is rather limited.
+The criteria on all of our sources besides stage 1 is that they must be morphologically disturbed.
+Each source is confirmed to have some kind of tidal feature f=present in the image, even if a secondary is not present in the image.
+There are, always, of course other galaxies in each image and there is no guarantee that the calcualted photometric redshift is correct.
+WE often find galaxies which are clearly interacting or paired, but with the photometric wildly different.
+In these cases, we defer to the redshift and only record one of the galaxies in our sample.
+This approach, however, means we must be careful to investigate the effects of environment on our galaxies as disturbance by, say, ram pressure stripping can appear like tidal features.
+
+\section{METHOD: Environment, AGN and Interaction Stage} \label{method}
 In this section, we describe how we separate our sample of 4,181 interacting galaxies into separate stages.
@@
 
+\begin{figure*}
+    \centering
+    \includegraphics[width=0.95\textwidth]{figures/projected-seps.pdf}
+    \caption{The projected separations of the confirmed galaxy pairs in our sample.
+This confers with other works the definition of our different stages.
+Stage 1 can be at any projected separation, however, we have visually confirmed that these sources are not morphologically disturbed.
+Stage 2 is dominated by systems with small projected separation as, by definition, they must be morphologically linked or overlapping.
+Those systems at larger separation are very large systems whose morphology categorise them as stage 2.
+Finally, stage 3 galaxies are those which are visually confirmed to be fully morphologically separated and tidally disturbed.
+The bulk of these lie in a range of 25 - 100kpc in projected separation from each other.
+There is some overlap between stage 2 and stage 3 in projected separation, as their visual classification is also dependent on the system size.}
+    \label{fig:proj-seps}
+\end{figure*}
+
 Stage 1 of the interaction captures the first approach of the two systems.
@@
 We purely describe a galaxy as stage 3 based on significant tidal and morphological disturbance.
-This stage has the highest potential for contamination by irregular galaxies or galaxies whose morphology has been disturbed by processes other than tidal interaction.
-We discuss the potential impacts of this contamination, and the limitations of using visual morphology as a proxy for stage in Section \ref{sec:limitations}.
 
@@
 
-Our four stage approach is not a new one, and many other works have utilised it to differentiate different parts of the dynamical history of a galaxy interaction \citep{}.
+Our four stage approach is not a new one, and many other works have utilised it to differentiate different parts of the dynamical history of a galaxy interaction \citep{2022ApJ...937...97C, 2023ApJ...952..122G}.
 It is, however, important to note its limitations.
@@
 
-However, with these simplifications in our assumptions, we will investigate the parameters which are proxies for the underlying physical processes and interpret them.
-We will investigate the whether we see have a bias in our systems based on environment, whether we find increased AGN activity and if we observe enhancement in star formation with stage.
+We relate our classification of stage to projected separations between systems, more often used in the literature, by using our confirmed galaxy pair subsample.
+Figure \ref{fig:proj-seps} shows the stage classification with projected separation between the two pairs.
+The projected separation is measured by taking the average of the best fit photometric redshifts between the two galaxies, and converting their angular separation to a physical one.
+The most dinstinct separation in stages in between stage 2 and stage 3.
+Here, we see that stage 2 is dominated by systems with a projected separation $<$35kpc while stage 3 is dominated $25 \leq s_{proj} \leq 100$ kpc.
+This is to be expected from our definitions of stage.
+Stage 2 is visually classified as systems which are highly morphologically disturbed, while either being morphologically linked to each other or overlapping.
+Those galaxy pairs with large projected separations are pairs which are very large in angular size, while still overlapping or morphologically linked.
+If this criteria is not met, then the system becomes a stage 3 interaction where the two galaxies in the pair are completely dinstinct.
+There is some overlap between the projected separations of stage 2 and stage 3 as this is somewhat dependent on the angular size of the two systems involved in the interaction.
+
+We will investigate the parameters which are proxies for the underlying physical processes of our sample and interpret them.
+We will investigate whether we see have a bias in our systems based on environment, whether we find increased AGN activity and if we observe enhancement in star formation with stage.
 The star formation rate is already present in the COSMOS2020 catalogue from both EAzY and LePhare.
@@
 \noindent We will also investigate the affect of interaction stage upon the AGN activity within the galaxies involved.
-Unfortunately, the outputs of EAzY and LePhare do not provide us with photometric estimates of the line fluxes needed to define an AGN on a Baldwin, Philips and Terlevich (BPT) diagram \citep{}.
+Unfortunately, the outputs of EAzY and LePhare do not provide us with photometric estimates of the line fluxes needed to define an AGN on a Baldwin, Philips and Terlevich (BPT) diagram.
 Therefore, we cannot directly identify if a galaxy is only star forming, has nuclear activity or is a composite.
@@
 Therefore, we require these catalogues to specifically show us if a galaxy is star forming or not before we classify it as such.
-This is why our number of star forming galaxies is lower than expected.
-We discuss this limitation in section \ref{sec:limitations} and the effect it may have on our results of AGN fraction evolution with stage.
 
@@
 Figure \ref{fig:weighted-mass} shows the weighted mass distributions through the four different stages.
-These appear highly similar, and we conduct Kolmogorov-Smirnov \citep[KS-test;][]{an1933sulla} and Anderson-Darling \citep[AD-test;][]{AD_paper} tests to compare each distribution.
+These appear highly similar, and we conduct Kolmogorov-Smirnov \citep[KS-test;][]{an1933sulla} and Anderson-Darling \citep[AD-test;][]{stephens_74} tests to compare each distribution.
 In each test, we calculate the value of the KS test and a p-value which is the probability that each distribution is drawn from the same parent distribution.
@@
 Thus, we find that throughout the different stages of interaction the star formation within the systems is being driven upwards.
-This is not an unexpected result.
-It has long been known that the SFRs of merging and post-merging galaxies is increased with respect to control samples of galaxies within the field \citep{papers saying this}.
-However, what we have found here is that this process of increasing SFR and galaxies being driven to starburst begins from the pericentre of the first interaction.
-Simulations have long showed that there is a peak in SFR initially in an interaction, followed by a slow reduction to a final enhanced level in the post-merger stage \citep{papers saying this}.
+We have found here is that this process of increasing SFR and galaxies being driven to starburst begins from the pericentre of the first interaction.
+Simulations have long showed that there is a peak in SFR initially in an interaction, followed by a slow reduction to a final enhanced level in the post-merger stage.
 However, due to the initial starburst, it is often shown that the gas within the galaxy is either quickly used up and the galaxy quenches or it is heated to the point that star formation becomes very inefficient.
@@
 We are probing major interactions between galaxies, where the resultant tidal features that form would be classifiable in an image.
-It is well know that the mass ratio of an interaction takes an important role in the enhancement of star formation \citep{papers about major interaction}, and we are probing the most extreme examples.
 Hence, even those mergers which are considered dry - with very little gas - would be capable of driving major rejuvenation in the star formation of these systems.
@@
 
+\subsection{Projected Separation and Star Formation Enhancement}
+\noindent To further confirm this result, we directly investigate the relation between the star formation enhancement (SFE) and the projected separation using our confirmed sub-sample of galaxy pairs.
+This sample is significantly smaller than our non-pair sample: containing 480 pairs or 960 galaxies.
+Upon sub-dividing this into different stages we find 310 stage 1 galaxies, 146 stage 2 galaxies and 498 stage 3 galaxies.
+Only 3 stage 4 galaxies were in our confirmed galaxy pair sub-sample, and therefore we do not attempt to make inferences about this population.
+
+To measure the SFE of our galaxy pairs, we directly compare the to the control sample that was also created with this sub-sample and defined in Section \ref{sec:sec-ident}.
+We separate our galaxy pair sample into different bins based on the projected separation between them.
+We find that the bulk of our sample has a projected separation between the two galaxies of $\leq$50kpc.
+Therefore, we sample from this region of the parameter space with high precision and smaller bin widths before we increase the bin widths at larger projected separations.
+We define a cutoff that each bin must contain at least 10 counts to be included in this plot and, therefore, by changing the bin widths with projected separation we are able to maintain some level of statistical robustness.
+We define our bins as [0.5, 10, 20, 50, 100, 125, 150] kpc.
+
+We create distributions based on these bins of projected separation: one of interacting galaxies and the other of our control galaxies.
+We then take the average of each bin separately, before dividing each distribution by the other.
+By taking the average of each bin, we are finding the total excess of the SFR caused by interaction alone and then comparing it to what we would expect from non-interacting galaxies in the same bin.
+Note, that the control galaxy relation to the projected separation is meaningless as they are not paired.
+The control galaxies are simply mass and redshift matched to each interacting galaxy and used as a reference for what SFR we would expect of it had it not been interacting.
+Finally, we divide the the averaged interacting SFR distribution by the averaged control SFR distribution.
+This provides us with a measure of the excess star formation due to interaction, and the SFE when compared to the regular population.
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=0.95\textwidth]{figures/sfr-enhancement-projected-sep.pdf}
+    \caption{The projected separation against the star formation enhancement in average star formation at different bins of projected separation.
+Each bin must contain at least 10 counts to be considered.
+As the bulk of our galaxy pair sample is at low projected separation, we heavily sample from this region of the parameter space.
+The bins are: [0.5, 10, 20, 50, 100, 125] kpc.
+As we move to higher projected separation, the bins increase in width to maintain statistical significance in our sample.
+\textit{Left}: The star formation enhancement found in the entire galaxy pair sample.
+As expected, we see a gradually decreasing enhancement.
+\textit{Right}: As left but broken up into different stages of the interaction.
+Black markers are stage 1, red stage 2 and blue stage 3.
+We only investigate stages 1,2 and 3 as only three galaxy pairs were identified in stage 4.
+Here, we find a generally decreasing star formation enhancement with projected separation but very different individual behaviour dependent on the stage classification.}
+    \label{fig:sfr-enhancement-sep}
+\end{figure*}
+
+Figure \ref{fig:sfr-enhancement-sep} shows star formation enhancement between our interacting and control binned SFRs and the projected separations between each galaxy pair.
+On the left of the plot, we have the distribution for the full galaxy pair sample, without taking account of stage.
+The error bars are calculated based on the counts within the bin and errors on the underlying SFRs of the galaxies within.
+The dashed black line represents no enhancement in SFR, as the average SFR in the interacting galaxy sample would be equal to the average SFR in the control sample.
+We find at very small projected separation a SFR enhancement of 1.87 which gradually decreases with projected separation down to approximately 1 at 117.5kpc.
+On the right, we break the galaxy pair sample into different stages and plot out the resultant enhancement in star formation.
+This shows very different behaviour in enhancement dependent on the stage of the interaction.
+
+In stage 1, we find that the star formation is very weakly enhanced, at a level of approximately 1.25.
+As we increase the projected separation bins, the enhancement then changes around an enhancement of 1, even dropping below 1 at 40kpc.
+Taking into account the errors on our measurements, the true value of the enhancement could be around 1 for the entire projected separation distribution.
+This is not unexpected.
+Stage 1 represents when the two galaxies are close pairs, but with no morphological disturbance.
+Therefore, we would not expect significant, if any, enhancement in the SFR based on the projected separation.
+This is the stage with the lowest enhancement across projected separation, remaining close to 1.
+
+In stage 2, we see consistent enhancement with projected separation.
+It is also much larger than stage 1, with it being approximately 1.75 up to 1.90.
+In fact, the measured enhancement increases across the 50kpc of projected separation.
+However, accounting for the errors on these measurements and the declining counts in each bin, it is likely that the enhancement does drop as the projected separation increases.
+We see a very large enhancement in the overlapping stage 3 galaxies which overlap with the stage 2 measurements.
+The enhancement in stage 3 galaxies then rapidly declines as we move to higher projected separations.
+After 150kpc, our galaxy pair sample does not have the counts to make robust estimates of the SFE.
+
+Finding that the SFE declines with projected separation is not an unexpected.
+Previous works also find this and even match our results \citep{2000ApJ...530..660B, 2008AJ....135.1877E, 2013MNRAS.433L..59P}.
+Where our result differs is by taking into account the stages of the interaction.
+\textbf{While using only projected separation is a proxy for stage, we find the actual SFE is also dependent on the time of in the dynamical timescale the interaction is}.
+For instance, all of our stage 2 systems have high SFE of greater than 1.5 no matter the projected separation between them.
+This shows that the morphological connection and overlap of the two systems is driving the enhancement.
+Then, moving to stage 3 with low projected separation, we see the SFE grows even larger to 2.5.
+The galaxy pair will be just at the point of breaking overlap and morphological connection here, only just moving away from pericentre here.
+Simulations have predicted that once the two systems are just passed pericentre and moving away from each other, the two galaxies will undergo an intense delayed starburst \citep{2015MNRAS.448.1107M}.
+We see this effect in the sudden increase in SFE as the two galaxies disconnect from each other and begin to move away from one another.
+
+These distributions of SFE paint a picture of the disturbance and change in the SFRs of these systems throughout the interaction, we will summarise here.
+First, in stage 1, the two systems move towards one another (or away with little disturbance) with no SFE and matching the control.
+Upon entering into stage 2, the galaxies SFR dramatically increases due to the morphological disturbance of the two disks and potential overlapping and linking of the two systems.
+Then, once the two systems are past pericentre and enter into stage 3 to flyby one another, the gravitational torques on the two systems take hold and star formation is, again, dramatically increased.
+This increase relaxes as the systems move towards apocentre and higher projected separations.
+
+However, it is important to note that this result has been found with a sample of 960 interacting galaxies in their pairs.
+No stage 4 galaxies have been represented and in numerous projected separation bins the counts are small enough to have conclusion altering error bars.
+\textbf{Therefore, it is imperative that future works, with larger sample sizes not only look at the projected separation of the systems but the morphology as well.}
+
 \subsection{Controlling for Galactic Environment} \label{sec:env-cont}
@@
 It is well known that the environment has a direct impact on the observed SFR of galaxies.
-A galaxy in a cluster environment has, on average, a higher SFR than those in the field \citep{Papers on environment with SFR}.
+A galaxy in a cluster environment has, on average, a higher SFR than those in the field \citep{2006MNRAS.373..469B}.
 Thus, if any of our stage classifications are biased towards one environment or another, it could have severe consequences for our results.
@@
 \section{Nuclear Activity with Interaction Stage}
-\subsection{Controlling for Stage}
 \noindent We now cross match our sample with the two AGN catalogues and methods described in Section \ref{sec:agn-clsf}.
-This gives a sample of 1,284 AGN and star forming galaxies (SFGs) to cross match with the stage.
-Figure \ref{fig:agn-stage} shows distribution of stellar mass to SFR with stage, with the confirmed AGN and SFG marked.
+This provides us a sample of 1,361 AGN and star forming galaxies (SFGs).
+The breakdown of number of classifications per stage is shown in Table \ref{tab:agn-sfg-breakdown}.
+Figure \ref{fig:agn-stage} shows distribution of stellar mass to SFR with stage, with the confirmed AGN and SFGs marked.
+We find no major changes in AGN with stellar mass or SFR with stage in our sample.
+Galaxies containing AGN appearing throughout the SFMS and red sequence across each stage.
+There is no obvious bias in stellar mass or SFR for hosting an AGN.
+We do, however, see a concentration of AGN in stage 1 on the red sequence at higher masses.
+This shifts as we increase interaction stage, with the bulk of the AGN beginning to appear at lower masses in stages 3 and 4.
+Finally, in stage 4 we see AGN and SFGs distributed almost evenly across the star forming main sequence with little bias in distribution with mass.
+This hints at evolution with stage.
+
+Applying KS- or AD- tests these, however, reveals values close to 1 and therefore it is very likely that these distributions have been drawn from the same parent sample.
+However, due to the low counts of AGN and SFGs in our sample, using KS- and AD-tests to verify this is not optimal.
+Therefore, we instead investigate the global AGN fractions in our sample across different stages.
+We apply a weighting, as in our SFR and stellar mass distribution examples, to account for the various counts across the different stages.
+We then take a second weighting of the measured AGN fraction from the total size of the different samples we have.
+Thus, we have assumed that we have equivalent counts in each mass bin of our sample as well as approximated having the same sample size in each stage bin.
 
@@
     \includegraphics[width=0.45\textwidth]{figures/agn-stage-dist.pdf}
-    \caption{The distribution of AGN through stage with SFR and stellar mass.}
+    \caption{The distribution of AGN through stage with SFR and stellar mass. We do not find any major changes and evolution with AGN and SFG position through interaction stage. }
     \label{fig:agn-stage}
@@
 
-\section{Characteristics of Matched Pairs}
-\subsection{Star Formation and Mass Ratio}
-
-\subsection{Star Formation and Projected Separation}
-
-\section{Limitations of Approach}\label{sec:limitations}
-\subsection{Redshift Effects on Visual Classification}
-\noindent An important limitation of our visual approach is related to the effect of tidal features out to higher redshifts.
-As the redshift increases, surface brightness dimming of the systems may lead to a lack of visual confirmation in the tidal features of different objects.
-Thus, if we were heavily affected by this in our redshift range ($0.0 \leq z \leq 1.2$), we would see distinct signs of it in our selection function of our mergers.
-For instance, if all of our stage 4 classifications were actually high redshift stage 3 galaxies, we would observe this in our selection function.
-Therefore, Figure \ref{fig:redshift_selection} shows our selection functions across our redshift range for each defined stage in our interaction.
+\begin{table}
+    \centering
+    \begin{tabular}{|c|c|c|c|c|}
+         & Stage 1 & Stage 2 & Stage 3 & Stage 4 \\
+         \hline
+        SFG & 135 & 212 & 337 & 199 \\
+        AGN & 103 & 117 & 163 & 95
+    \end{tabular}
+    \caption{Breakdown in number of classified AGN and SFGs per stage.
+With our counts so low in this sample, it is difficult to make concrete conclusions about the evolution of AGN during interaction.}
+    \label{tab:agn-sfg-breakdown}
+\end{table}
 
@@
     \centering
-    \includegraphics[width=0.45\textwidth]{figures/stage-selection.pdf}
-    \caption{Redshift vs Mass distribution for each stage of interaction we have defined.
-This is important as we use tidal distortion and the existence as tidal features as a fundamental for our classification methodology.
-As shown here, the distribution of systems across redshift and mass is consistent for all stages in our sample.
-Therefore, we are likely not affected by this in our analysis.}
-    \label{fig:redshift_selection}
+    \includegraphics[width=0.45\textwidth]{figures/agn-frac-time.pdf}
+    \caption{The change in AGN fraction with stage.
+We define the AGN fraction as the ratio of number of confirmed AGN divided by the number confirmed AGN and SFGs in the sample.
+Errors on each point are found by bootstrapping.
+We do not include any sources of which we have no information.
+We find a sudden drop in AGN fraction from stage 1 to stage 2, followed by a rapid increase from stage 3 to 4.}
+    \label{fig:agn-frac-time}
 \end{figure}
 
-As shown, the distribution of masses across redshift that we find in our sample is reasonably consistent with each other.
-This means we are likely not affected by surface brightness dimming across our sample and our redshift range.
+Figure \ref{fig:agn-frac-time} shows the changing AGN fraction with interaction stage.
+We find that the AGN fraction generally increases with interaction stage.
+There is a large increase from stage 1 to 2, followed by the fraction mostly remaining unchanged until stage 3.
+Then, in stage 4 we measure another large jump in the AGN fraction.
+However, before we discuss this result further, we must point out that the large error bars on our measurements and the low number counts of confirmed AGN and SFG make this difficult to interpret.
+We measure the errors on our sample from bootstrapping the underlying low-count population of AGN and SFGs and comparing to the change in fraction measured.
+Thus, while our inital values show a general increase, because of the large error bars, there could be no increase at all with stage to even a slight decline.
 
-\subsection{Selection Effects in AGN Sample}
+However, finding that AGN fraction increases with stage is inline with other works \citep{2011MNRAS.418.2043E, 2023ApJ...942..107S} which often find an increase in AGN fraction with projected separation.
+Stage can also be considered as a proxy for the projected separation of the two systems, where stage 4 will be systems with the smallest projected separation and stage 3 being the largest separation.
+This matches what we find here, with stage 4 systems having the highest fraction of AGN compared to stage 1 systems.
+What is different in our results, however, is the change in AGN fraction from stage 2 to 3.
+While we see a large increase in AGN fraction from stage 1 to 2, this enhancement holds from stage 2 to 3.
+Again, this is not an unusual result and works such as \citet{2011MNRAS.418.2043E} show that the enhancement of nuclear ignition can actually be delayed in galaxy interaction.
+Thus, we only see the final ignition in the later part of the dynamical time than the initial flyby.
 
-\subsection{Limitations of Visual Classification}
+% Section here on actually looking at the projected separation of the two systems.
+It is also difficult to use interaction stage as a proxy for the projected separation in this context.
+As shown previously, stages 2 and 3 have some overlap in the range of projected separations we have classified them into.
+Therefore, we also investigate any overlap between our confirmed pairs and the AGN fractions we see here.
+We find 104 AGN and 180 SFGs overlap with our confirmed pairs.
+This sample is far too small to breakdown further into different stages.
+Therefore, Figure \ref{fig:sfg-agn-proj} shows the change in density of AGN classifications and SFGs with increasing projected separation.
+As expected, we find that with increasing projected separation the number of confirmed AGN and SFGs decreases.
+However, in the AGN distribution, we find two contributing components in it.
+The first is a peak in the projected separation distribution is from 0kpc-25kpc.
+The only contribution here is from stage 2 galaxies, which are close to pericentre.
+The second peak, from a projected separation of 30kpc - 60kpc is dominated by stage 3 galaxies, although some stage 1 AGN are in this peak as well.
+Finally, the third peak from 85 - 125kpc is representative of a mixture of stage 1 and stage 3 galaxies.
+None of our stage 4 galaxies which had their secondaries identified overlapped with our AGN and SFG identified sample.
 
-\subsection{Selection Effects of SFR Sample}
+\begin{figure}
+    \centering
+    \includegraphics[width=0.45\textwidth]{figures/sfg-agn-dist.pdf}
+    \caption{The distribution of both AGN and SFGs which have been cross matched with our confirmed galaxy pairs.
+While we find, as expected, the number of AGN and SFGs decreases with projected separation we find interesting structure within the AGN sample.
+Here, there appears to be a double peak in the number of counts of AGN.
+The first peak, between a projected separation of 0 and 25kpc is primarily from stage 2 galaxies while the second peak of 40 to 65kpc is of stage 3 galaxies in our sample.
+As shown in Figure \ref{fig:agn-frac-time}, we expect the fraction of AGN to be similar in these two stages while they are at very different times in the dynamical timescale of the interaction.
+The third peak, from 75 to 125kpc is only from stage 1 and stage 3 galaxies.}
+    \label{fig:sfg-agn-proj}
+\end{figure}
+
+Thus, the observed enhancement in AGN across a range of different projected separations if primarily due to different parts of the dynamical time of an interaction.
+The peak in nuclear activity, as expected, is within stage 2 galaxies which are close to pericentre in their interaction.
+However, as we move to higher projected separations and towards stage 3 of the interaction, the number of AGN begins to decrease.
+This implies, following other works, that enhancement occurs early in the interaction, when the systems are at pericentre from each other and with the smaller the pericentre, the more likely it is of nuclear ignition.
+The nuclear ignition from stage 2 can then be switched off again as we move to higher projected separation and stage 3.
+Finally, as the interaction begins to move into coalescence, we find another large increase in the AGN fraction which indicates that AGN activity becomes enhanced.
+Therefore, \textbf{when finding the AGN fraction of interacting systems it is important to consider the stage, and relate this to the projected separation of the system.}
+
+\section{Discussion}
+\subsection{Interaction Stage and Projected Separation}
+
+\subsection{Interaction Stage and AGN}
+
+\subsection{Comparison to Simulations}
 

### 2023-11-30 paper-source/main.tex
Finished draft of paper. Big simulation image missing, error updates needed and want to talk about AGN flickering and needing more information from simulations.

@@
 % Keep the title short and informative.
-\title[Mergers in COSMOS]{Mergers in the COSMOS Field}
+\title[Interactions in COSMOS]{When do the effects of interaction happen? Interacting and disturbed galaxies in the COSMOS field}
 
@@
 \noindent Galaxy interaction and merging is of fundamental importance to our current theories of galaxy formation and evolution.
-Our current cosmological theory, $\Lambda$CDM dictates that structure is expected to form and assemble hierarchically \citep{1978MNRAS.183..341W, 2013MNRAS.436.1765M}.
+Our current cosmological theory, $\Lambda$CDM dictates that structure is expected to form and assemble hierarchically \citep{1978MNRAS.183..341W, 2001MNRAS.328..726S, 2013MNRAS.436.1765M}.
 Thus, understanding the underlying processes that occur in galaxy interaction and merging are paramount to understanding cosmological theories.
@@
 The clearest result of interaction is the disruption of galactic morphology, the acceleration of disks to spheroidal systems and the formation of tidal features \citep{1972ApJ...178..623T, 1977ApJ...212..616T, 2005MNRAS.357..753G, 2009MNRAS.397..802H}, increases in star formation rates when compared to the general galaxy population \citep{1991ApJ...370L..65B, 2006ApJ...652...56B, 2014MNRAS.437.2137S, 2015ApJ...807L..16K} and, potentially, their rapid quenching \citep{2013MNRAS.430.1901H, 2023RAA....23i5026D}.
-There is also evidence to suggest that interaction plays a role in the activation of active galactic nuclei (AGN) \citep{2011MNRAS.418.2043E, 2015ApJ...806..219C, 2023MNRAS.523.4164H}.
-Therefore, with interaction having such an affect on the galaxies we see - over a long time period - understanding galaxy interaction is fundamental to understanding galaxy evolution
+There is also evidence to suggest that interaction plays a role in the ignition of active galactic nuclei (AGN) \citep{2011MNRAS.418.2043E, 2015ApJ...806..219C, 2023MNRAS.523.4164H}.
+Therefore, with interaction having such an affect on the galaxies we see - over a long time period - understanding galaxy interaction is fundamental to understanding galaxy evolution.
 
-To better our understanding of galaxy interaction, it is often prudent to break them down into different stages of interaction.
-This relates to the dynamical time of the interaction, and the snapshot in the interaction we are observing.
-Previous works focused on simulations find that a sudden increase in star formation occurs early in the dynamical timescale of the interaction \citep{2008MNRAS.384..386C, 2019MNRAS.490.2139R}, however, confirming this definitive link observationally remains elusive \citep{2023arXiv230916531R}.
+To fully map out the effect of galaxy interaction, we must understand its impact on galaxies through the entire merger history and dynamical timescale of the interaction.
+As each observation only provide snapshots of different parts of the dynamical timescale across different merger histories, it is imperative we have large samples to capture the full history.
+The most obvious place to start with mapping the full dynamical histories is with simulations.
+Previous works find sudden increases in star formation occurs early in the dynamical timescale of the interaction \citep{2008MNRAS.384..386C, 2019MNRAS.490.2139R}, however, confirming this definitive link observationally remains elusive \citep{2023ApJ...958...96R}.
 The same studies could also be done for nuclear activation as well as quenching of interacting systems \citep{2011MNRAS.418.2043E, 2018PASJ...70S..37G, 2023ApJ...942..107S}.
-While we cannot yet directly measure when in the dynamical timescale star formation is enhanced from observations, we can approximate it by splitting different interactions into different stages.
-These stages relate directly to the dynamical timescale of the interaction.
-Often, they are split into four: gravitationally bounded pairs, approaching pericentre of the interaction, approaching apocentre of the interaction, and approaching coalescence.
 
-To fully study the relationship between interaction stage and the underlying physical processes occurring we require large, statistically robust interacting galaxy samples.
-However, they are surprisingly difficult to create; with the first interacting galaxy catalogue (the \citet{1966ApJS...14....1A} catalogue) containing only 318 systems.
-More recent samples have been created either by machine learning classification \citep{2019A&A...626A..49P, 2023A&A...669A.141S}, visual classification by citizen scientists \citep{2010MNRAS.401.1043D} or by photometric parameterisation \citep{2004AJ....128..163L, 2023MNRAS.522....1N}.
+Achieving such study in the dynamical history of an interaction with observations is more difficult.
+While we cannot directly measure the full dynamical timescale for individual systems, we can create large samples of interacting galaxies which are representative over the dynamical history.
+The first interacting galaxy sample (the \citet{1966ApJS...14....1A} catalogue) contained only 318 systems, while more recent samples have been created either by machine learning classification \citep{2019A&A...626A..49P, 2023A&A...669A.141S}, visual classification by citizen scientists \citep{2010MNRAS.401.1043D} or by photometric parameterisation \citep{2004AJ....128..163L, 2023MNRAS.522....1N}.
+With larger samples, we can approximate different parts of the dynamical time them into their constituent stages.
 However, each sample has always been plagued by contamination and a loss of statistical significance when broken down into stages.
 It is notoriously difficult, from morphology alone, to select interacting or merging galaxies.
-Without redshift information it is difficult to discern if they are close together in 3D space or only by projection effects.
+
+Often, the stage of an interaction is approximated by measuring different parameters with the projected separation between two systems.
+Early works showed that there was significant star formation enhancement (SFE) in galaxy pairs with small separations \citep{2003MNRAS.346.1189L ,2008AJ....135.1877E, 2022ApJ...940....4S}.
+A connection was also found between the projected separation in galaxy pairs and the AGN fraction where, once again, the AGN fraction appears to increase with decreasing projected separation \citep{2009MNRAS.399.2172R, 2011MNRAS.418.2043E, 2017MNRAS.465.2671G, 2021ApJ...909..124S}.
+However, using projected separation as a proxy for the stage in dynamical time of an interacting history overlooks which part of the dynamical history the interaction is at.
+For instance if a galaxy pair is found to have small projected separation, without visually confirming the morphology, it is difficult to ascertain if the galaxies are just approaching each other or just passed each other.
+The differences between these being paramount to understanding the effects of interaction on the galaxies involved.
+
+In this work, we split a large sample of interacting galaxies into four specific stages based from their morphology.
+Each stage is designed to capture different parts of the dynamical time of an interaction.
+Each interacting or disturbed galaxy is visually classified into its stage, which ranges from galaxies being close pairs, to overlapping and disturbed, to disturbed and distinct to finally coalescing.
+This follows the classification methods of developing algorithms for staging of interaction\citep{2019MNRAS.490.5390B,2022ApJ...937...97C}.
 
@@
 This is the largest visually classified interacting galaxy catalogue to date.
-This sample was created using the new ESA Datalabs\footnote{ESA Datalabs: link} platform and the convolutional neural network machine
-\texttt{Zoobot} \citep{2022MNRAS.509.3966W, 2023JOSS....8.5312W}.
+This sample was created using the new ESA Datalabs\footnote{ESA Datalabs: link} platform and the convolutional neural network machine \texttt{Zoobot} \citep{2022MNRAS.509.3966W, 2023JOSS....8.5312W}.
 This classified all sources in the Hubble Source Catalogue \citep{2016AJ....151..134W} from the Hubble Space Telescope (HST) archives into interacting or non-interacting.
@@
 
-In this work, we cross match this catalogue with the Cosmic Evolutionary Survey (COSMOS) survey\footnote{DOI: \href{https://www.ipac.caltech.edu/doi/irsa/10.26131/IRSA178}{10.26131/IRSA178}}.
+We cross match this catalogue with the Cosmic Evolutionary Survey (COSMOS) survey\footnote{DOI: \href{https://www.ipac.caltech.edu/doi/irsa/10.26131/IRSA178}{10.26131/IRSA178}}.
 This provides us with ancillary data for a subset of the OR23 catalogue.
-This ancillary data contains many galactic parameters of interest and we explore how they evolve with different stages of interaction.
-We define four distinct stages that occur over the course of the full dynamical timescale of interaction, from the two galaxies approaching each other to full coalescence.
-We primarily focus on the evolution of the stellar masses, star formation rates, surrounding environment and AGN classification from various COSMOS catalogues across the full dynamical timescale of interaction.
-With the photometric redshifts available from COSMOS, we also confirm a set of interacting galaxies and close pairs to investage further parameters of interest.
-These include the trend of projected separation of the galactic pairs on star formation rate as well as the change with mass ratio.
+This ancillary data contains many galactic parameters of interest and we explore how they evolve with our defined stages of interaction.
+We primarily focus on the evolution of the stellar masses, star formation rates and AGN classification from various COSMOS catalogues.
+We utilise the photometric redshifts available from COSMOS to confirm a set of interacting galaxies and close pairs to draw on trends with projected separation.
 
-%, comparing to the work of \citet{2022ApJ...940....4S} a different study using COSMOS to investigate these latter relations.
-
-This paper is laid out as follows in Section \ref{data} we explain the OR23 and COSMOS catalogues, and describe the process of catalogue matching especially focused on accurate de-duplication and cross-matching selection from the different catalogues.
-Section \ref{method} describes the methods by which we split the interacting systems into their different stages, and how we identify the secondary galaxies to each identified interacting galaxy.
-We also discuss our processes of calculating projected separations.
-In Section \ref{results} we describe and discuss our results, and their implications, and compare to previous works focused on investigating different stages of interaction.
+This paper is laid out as follows in Section \ref{data} we explain the OR23 and COSMOS catalogues, and describe the process of catalogue matching especially focused on accurate de-duplication and cross-matching between the different catalogues.
+Section \ref{method} describes the methods by which we split the interacting systems into stages, and how we identify the secondary galaxies in each pair.
+In Sections \ref{results:SF_stage} and \ref{results:AGN_stage} we show our results of star formation and active galactic nuclei evolution with interaction stage and present an initial discussion.
+These are followed in Section \ref{discussion} where we compare to previous works and put our results in the context of the field.
 Finally, Section \ref{conclusion} we make concluding remarks and discuss future work to better our constraints.
@@
 Hereafter in this paper, when referring to an interacting galaxy we are referring to a galaxy which has undergone one or multiple flybys by a secondary galaxy and caused tidal disturbance.
-A merging galaxy is the final state of these flybys, where two or more systems have or are about to coalesce to form a highly morphologically irregular system.
+A merging galaxy is the final state of these flybys, where two or more systems have or are about to coalesce to form a morphologically irregular system.
 
@@
 \subsection{The O'Ryan+23 Catalogue}
-\noindent We utilise the interacting galaxy catalogue created in OR23.
-While the full process of its creation is detailed there, we briefly describe it here.
-This sample of interacting galaxies was created using a convolutional neural network - \texttt{Zoobot} - to search all final product data in the \textit{Hubble} Legacy Archive.
-A regular convolutional neural network classifies images by extracting features from them, and using this to output a solution.
-\texttt{Zoobot} differs by extracting features from an image, and then reduces them to a generalised representation (essentially, a small feature vector).
-The power of this is that it makes \texttt{Zoobot} incredibly generalisable.
-This is further reinforced by training it on citizen scientist responses to the Galaxy Zoo: DECaLS \citep{2022MNRAS.509.3966W} project to every task in that project.
-Thus, it can answer a host of questions as well as be very easily finetuned to new datasets and classification tasks.
-In OR23, it was easily finetuned on \textit{Hubble} data by using classifications from all previous Galaxy Zoo projects \citep{2008MNRAS.389.1179L}.
+\noindent The interacting galaxy catalogue we draw from is the OR23 catalogue of interacting galaxies.
+These systems are classified based on their visual morphology and, while the full process of its creation are detailed there, we will briefly describe it here.
+The morphological classifications were made by a convolutional neural network (CNN) - \texttt{Zoobot} - which searched all final product data in the \textit{Hubble} Legacy Archive.
+While a CNN primarily classifies images by extracting features from them \texttt{Zoobot} differs by extracting features from an image and reducing them to generalised representations.
+By learning the generalise representation of different galaxy morphologies, \texttt{Zoobot} is incredibly flexible and easy to transfer learn on different tasks and datasets.
+This is further reinforced by training it on citizen scientist responses to the Galaxy Zoo: DECaLS \citep{2022MNRAS.509.3966W} and using it to make classifications on multiple morphology questions at once.
+In OR23, using a small dataset of citizen science-classified interacting galaxies from Galaxy Zoo \citep{2008MNRAS.389.1179L} \texttt{Zoobot} was finetuned to \textit{Hubble} data.
 
 Cutouts of each source were created as single-band \textit{F814W} images at 150 $\times$ 150 pixels across.
-This choice was motivated by it having the highest number of final product FITS files associated with it, while the image size was kept small due to the high number of cutouts required to be stored.
 Source coordinates were found in the \textit{Hubble} Source Catalogue \citep{2016AJ....151..134W}.
-This corresponded to just over 92 million cutouts to create and sources to classify.
-Due to issue of classifying interacting galaxies by morphology alone an extremely conservative prediction score from \textit{Zoobot} was required.
+This corresponded to just over 92 million cutouts created and classified.
+Due to well known issues of classifying interacting galaxies by morphology alone (such as close pair contamination) an extremely conservative prediction score from \textit{Zoobot} was required to make a positive classification.
 This resulted in a very pure, but highly incomplete catalogue of 21,926 interacting galaxy systems.
@@
 
-However, in the OR23 catalogue, only the coordinates and the \textit{Hubble} Source catalogue are provided.
-For ancillary data, this catalogue must be matched to different data repositories.
-This is not a trivial task, as a large proportion of the OR23 catalogue is known to not exist in any existing astrophysical data repository.
-In this work, we opt to match the OR23 catalogue to the COSMOS catalogues.
+The OR23 catalogue only provided the coordinates and \textit{Hubble} Source catalogue ID for each source.
+Therefore, we must either calculate our own ancillary data or cross match with existing catalogues containing it.
+We elect to cross match the OR23 catalogue with the numerous catalogues of the COSMOS survey.
+The overall survey has numerous sub-catalogues ranging from calculations of galactic physical parameters to predictions on AGN classifications.
 
 \subsection{The COSMOS2020 Catalogue}
-We opt to match the OR23 catalogue with the catalogues of the COSMOS survey.
-Specifically, we elect to use the COSMOS2020 catalogue \citep{2022ApJS..258...11W}.
+In the COSMOS survey, there are multiple catalogues of galactic parameters such as star formation rates (SFR), stellar masses and line emissions.
+We elect to specifically use the COSMOS2020 catalogue \citep{2022ApJS..258...11W}.
 This catalogue has a wealth of ancillary information for just over 1.7 million sources in a 2 square degree area of the sky.
-Each source found in this area has been analysed with well used astronomical software, for our purposes primarily LePhare \citep{1999MNRAS.310..540A, 2006A&A...457..841I} and EAzY \citep{2008ApJ...686.1503B}.
-These provide two different measurements of the parameters we wish to investigate and match with stage.
-The first is the stellar masses of each our cross matched galaxies and the estimated star formation rates.
+Each source found in this area has been analysed with well known astronomical software (for our purposes, primarily  LePhare \citep{1999MNRAS.310..540A, 2006A&A...457..841I}, EAzY \citep{2008ApJ...686.1503B} and FAST \citep{2017MNRAS.465.3390A}).
+These provide estimates of the physical parameters of each source in the COSMOS2020 catalogue based on its measured broadband photometry.
+For our purposes, the most important parameters these calculate are the stellar masses and the estimated star formation rates of each source.
 We opt to simply use one of these two measurements in our analysis.
-For the stellar mass we use the LePhare measurement and for the star formation rates we use the EAzY measurements.
-Using either the vice versa of this, both EAzY or both LePhare measurements led to the degeneracy's within the underlying model Spectral Energy Distribution (SED) templates being revealed.
-Therefore, using these two opposing parameters gave realistic approximations of these photometrically approximated values.
+For the stellar mass we use the LePhare measurement and for the star formation rates we use the EAzY/FAST measurements.
+We compare the output masses and SFRs for our sources in Figure \ref{fig:difference-measures}.
+As shown, there can be wide scatter and disagreement between the two algorithms.
+We, therefore, elect to only use one software for each parameter and not to match the stellar masses and SFRs between them.
 
-As stated previously, the OR23 catalogue only contained the source ID, right ascension and declination of each interacting galaxy.
-Therefore, we had to cross match these with the COSMOS2020 catalogue right ascension and declination measurements.
-To do this, we searched the COSMOS2020 catalogue for any sources within 10" of the OR23 sources.
-If more than one COSMOS2020 source was within this radius, we took the closest source to the OR23 coordinates as the correct source.
-Upon matching based on coordinates, we conducted a de-duplication of the resultant catalogue based on COSMOS2020 ID, and reassigned COSMOS2020 sources to each duplication.
-If no further COSMOS2020 sources were within 10" of the OR23 source, then this was considered not to be cross matched.
-We find that, after this cross matching and de-duplication, 3,786 of the OR23 sources exist in the COSMOS2020 catalogue.
+\begin{figure}
+    \centering
+    \includegraphics[width=0.45\textwidth]{figures/mass-sfr-scatter.pdf}
+    \caption{Comparison of the measures of stellar mass and SFR using either LePhare or EAzY/FAST photometric codes to calculate them.
+If the algorithms agreed perfectly, the sources would lie on the blue 1:1 line.
+\textit{Left}: The scatter in the stellar masses between softwares.
+As shown, EAzY often seems to find larger stellar masses when compared to LePhare.
+\textit{Right}: Scatter in SFRs when measured with LePhare or EAzY.
+There is a large difference between the measures of LePhare and EAzY here, and therefore we opt to only use EAzY measures of the SFR through this work.}
+    \label{fig:difference-measures}
+\end{figure}
 
-We make two further cuts, based on the ancillary data available in the COSMOS2020 catalogue.
-First, there are many unphysical photometric measurements for the stellar mass or star formation rates.
-Therefore, we cut out these results as spurious.
-We only keep systems within a mass range of $6.5 \leq \log_{10} \text{M}_{*}(\text{M}_{\odot}) \leq 12.5$ and a star formation rate range of $-5 < \log_{10} \text{SFR} (M_{\odot}yr^{-1}) \leq 3.5$.
-Secondly, we institute a redshift cut of $z \leq 1.2$.
-This is to match the catalogue that will be later used to investigate the incidence of our sample of interacting galaxies with environment (detailed in Section \ref{data:environ}).
+We cross match between the OR23 catalogue with the COSMOS2020 catalogue by matching coordinates between them.
+We search the COSMOS2020 catalogue for any sources within 10" of the OR23 coordinates and make a list of any COSMOS2020 sources.
+If more than one COSMOS2020 source is found within this radius we take the source with the smallest angular separation from the OR23 coordinates as the correct source.
+Once we have identified one COSMSO2020 source for every OR23 ID, we de-duplicate based on COSMOS2020 ID and redo the coordinate matching process with any duplicate matches.
+If no further COSMOS2020 sources were within 10" of the OR23 source, then we the OR23 source not in the COSMOS2020 catalogue.
+We find 3,786 of the OR23 sources exist in the COSMOS2020 catalogue.
+
+Once matched, we remove any sources with unphysical photometric measurements for the stellar mass or star formation rates.
+We then further reduce our sample by only keeping sources within the a mass range of $6.5 \leq \log_{10} \text{M}_{*}(\text{M}_{\odot}) \leq 12.5$ and a star formation rate range of $-5 < \log_{10} \text{SFR} (M_{\odot}yr^{-1}) \leq 3.5$.
+To also nullify the effect of surface brightness dimming that may occur when attempting to classify tidal features of interacting galaxies, we institute a redshift cut of $z \leq 1.2$.
+This also makes our sample match the catalogue that will be later used to investigate the incidence of our sample of interacting galaxies with environment (detailed in Section \ref{data:environ}).
 Applying these cuts reduces our sample size to 3,689 interacting galaxies.
@@
 \subsection{Secondary Identification}\label{sec:sec-ident}
-\noindent As stated previously, the OR23 catalogue only identified interacting galaxy systems, not individual interacting galaxies.
-Therefore, we must find the secondary in each interaction using the COSMOS2020 catalogue.
-The size of the cutouts in this catalogue were also small, and therefore, the secondary did not often appear in the cutout in that project.
+\noindent As the OR23 catalogue only contains source coordinates and IDs, we must also manually identify the secondaries of many of our interacting systems.
 To find the secondaries, we apply three steps.
-First, a cutout surrounding the primary of each system was created.
-These cutouts were from the COSMOS cutout service, selecting HST-ACS tiles as the source of the cutouts in the $F814W$ filter.
-Each cutout had a 30" radius (corresponding to 1001 $\times$ 1001 pixels) centred and was centred on the primary galaxy.
+First, a cutout surrounding each OR23 source was created.
+These cutouts were from the COSMOS cutout service, selecting HST-ACS tiles in the $F814W$ filter.
+Each cutout had a 30" radius (corresponding to 1001 $\times$ 1001 pixels).
 The original OR23 cutout was also displayed next to the enlarged cutout.
-We then searched the COSMOS2020 catalogue for all sources within the cutout.
-Their positions and redshifts were recorded and used to annotate the cutout.
+We annotate each cutout with each sources COSMOS2020 ID and measured photometric redshift and error.
+By annotating each cutout with the sources photometric redshift and ID, we could visually assessed each cutout and give one of four following classifications to each: system disturbed but secondary could not be identified; secondary could be identified; cannot confirm galaxy is interacting; null redshift; incorrect primary assigned.
 
-We then visually assessed each annotated cutout, giving one of the four following classifications to each: system disturbed but secondary could not be identified; secondary could be identified; cannot confirm galaxy is interacting; null redshift; incorrect primary assigned.
-Our definition of a secondary galaxy was such that the secondary had to be within the cutout we were visually assessing and within $z=\pm0.1$ of the primary redshift.
-We use this cutoff as this is often used when calculating environment parameters \citep[e.g][]{2006MNRAS.373..469B} or defining interacting galaxies by close pairs \citep[e.g][]{2022ApJ...940....4S} based on the uncertainties present in using photometric redshift estimates from SED fitting.
-We define a null redshift as one outwith our redshift limits or NaN.
+To classify a secondary galaxy for our primary one, it had to be within the cutout we were visually assessing and within the recorded error of the primary photometric redshift.
+Using photometric redshift cutoffs in this way is often done when calculating environment parameters \citep[e.g][]{2006MNRAS.373..469B} or defining interacting galaxies by close pairs \citep[e.g][]{2022ApJ...940....4S}.
+A null redshift is defined as one outwith our redshift limits or NaN.
 A minority of the cutouts we visually assessed were found to have the incorrect primary at the centre.
-This was a result of our cross matching based on radius with the COSMOS catalogue.
+In these cases, we record the correct priamry galaxy ID and extract the ancillary data from the COSMOS2020 catalogue.
+We then attempt to find the secondary galaxy again for the corrected primary.
 
-Using these definitions, we find that of the 3,689 original systems cross-matched with COSMOS2020 2,209 could not have their secondary identified, 834 had a clear secondary, 446 could not be reliably classified as an interacting galaxy, 248 had a null redshift and 149 were the incorrect primary.
+Using these definitions, we find that of the 3,689 original systems cross-matched with COSMOS2020 2,283 could not have their secondary identified, 834 had a clear secondary, 446 could not be reliably classified as an interacting galaxy, 248 had a null redshift and 149 were the incorrect primary.
 Figure \ref{fig:secondary_selection} shows an example of each of our classifications.
@@
 % Define our classifications above.
-While initially surprising that the majority of our systems could not have a secondary identified, we found that it was mostly due to limitations in the COSMOS catalogue or the way in which we had conducted our secondary identification.
-To define a secondary galaxy, the object had to have a ID associated with it in the COSMOS2020 catalogue.
-However, when two systems were very close together and small enough, often they would be identified under a single COSMOS ID despite being two separate systems.
+While initially surprising that the majority of our systems could not have a secondary identified, we found that it was mostly due to limitations in the COSMOS catalogue or the way in which we conduct our secondary identification.
+Each potential secondary must have a COSMOS ID associated with it, however, when two systems were very close together and small enough they would be identified under a single COSMOS ID despite being two separate systems.
 The same also occurred when two systems were merging or interacting.
-The tidal features connecting the systems would lead to only one of them being identified in the catalogue, or when two cores appeared in one merging system.
-Figure \ref{fig:secondary_selection} specifically an example of two systems being close enough together that they have been identified under a single COSMOS2020 entry.
+The tidal features connecting the systems or coalescing systems would only be identified under one ID in the catalogue.
+Figure \ref{fig:secondary_selection} shows an example of two systems being close enough together that they have been identified under a single COSMOS2020 entry.
 Figure \ref{fig:secondaries_found} shows this disparity with the different types of interaction we observe.
@@
 Those galaxies which were found to be contamination (i.e., could not be reliably classified as interacting or having a null redshift) were removed from our sample.
-Galaxies that could not be reliably classified as interacting were those which showed little tidal distortion and had no systems nearby with a redshift approximately that of the primary.
-Often, these were systems that were overlapping but at different redshifts, systems with irregular morphologies of spiral arms or clumpy galaxies.
+Galaxies that could not be reliably classified as interacting as they showed little tidal distortion or had no neighbouring systems at a matching redshift were also removed.
+These systems were often overlapping but at different redshifts, or were systems with irregular morphologies of spiral arms or many clumpy galaxies.
 There was also many systems that were at high redshift ($z \geq 1$) where the resolution of the cutouts meant that features could not be discerned visually.
 
-Finally, we found that there were 149 systems which had been assigned to an incorrect primary.
-These were systems where the interacting galaxies were clearly in the cutout but some tidal debris or some nearby system had been assigned as the primary instead.
-This was a result of our catalogue matching based solely on separation between the OR23 coordinates and the COSMOS2020 source coordinates.
+Our final classification type was that the incorrect galaxy had been identified as the priamry galaxy.
+This was the case for 149 systems.
+These were systems where the interacting galaxies were clearly in the cutout but some tidal debris or some nearby system had been cross matched from COSMOS.
 We reassign these systems to the correct COSMOS IDs and then take them through the secondary identification process.
@@
 
-Each of the galaxies that have a confirmed secondary will be used in measuring effects of projected separation with star formation and AGN fraction.
-Therefore, we must define a control sample by which to compare to.
+For each galaxy in our sample, we find and define a mass- and redshift-matched control galaxy to investigate differences in their galactic parameters.
 We find these control galaxies from the COSMOS2020 catalogue.
 All galaxies within 0.01 dex of our sub-samples' stellar mass are selected from the catalogue, and within a $\pm$0.01 redshift slice.
-We then order the control galaxies to be whichever system is furthest from our target.
-Each control galaxy is then visually confirmed to be non-interacting and in isolation.
+We then define the control galaxy as the system furthest from our interacting galaxy.
+Each control galaxy is then visually confirmed to be non-interacting and have no nearby pairs.
 We also confirm that it does not already exist in the catalogue, and ensure there is no duplication in the control sample.
-Figure \ref{fig:matched-distributions} shows the mass distribution of our paired sub-sample of galaxies and their control, showing a closely similar mass distribution.
-With the previously defined cuts, we find a control galaxy for all but one of our galaxies with a confirmed secondary.
+Figure \ref{fig:matched-distributions} shows the mass distribution of our paired sub-sample of galaxies and their control, showing a mass distribution which is approximately the same as the interacting sample.
+With the previously defined cuts, we find a control galaxy for all but one of our interacting galaxies.
 
@@
 Both primary and secondary galaxies are within this distribution.
-From our sample of 4,135 interacting galaxies morphologically identified, 960 are confirmed galaxy pairs.
+From our sample of 4,181 interacting galaxies morphologically identified, 834 are confirmed galaxy pairs.
 This means that the secondary in the interacting galaxy system has been identified from morphology and photometric redshifts.}
@@
 \noindent As a result of using visual classification to find the secondary galaxy in each interaction, we were able to also confirm other interacting systems which had not been found in the OR23 catalogue.
-Primarily, these extra interacting galaxies were more systems that were involved in the interactions already recorded in OR23.
-The pipeline described previously was only used to find a secondary for each interacting galaxy, however in many cases more galaxies were involved.
-Other interacting galaxies that were added here were low redshift systems which would have appeared very large in the OR23 cutout.
-Details and tidal features were then lost in the original classification process.
-By looking at the larger COSMOS2020 cutouts used here, we were able to confirm these were interacting galaxies and add them to the catalogue.
-The final set of extra systems we added were often those that were close pairs, but physically in 3D space.
-While they had little tidal disruption - what the interacting galaxies were classified on in OR23 - with the photometric redshifts to hand, we could correctly identify them here.
+Primarily, these extra interacting galaxies are from systems which had more than one galaxy involved in the interaction.
+Our pipeline was built to only find a primary and secondary galaxy and, therefore, we add these extra systems through another pipeline.
+Other interacting galaxies that were added were low redshift systems which would have appeared very large in the small OR23 cutout.
+By looking at the larger COSMOS2020 cutouts, we are able to recover these galaxies and add them to this sample.
 
@@
 Thus, if we are heavily affected by this in our redshift range ($0.0 \leq z \leq 1.2$), we would see distinct signs of it in our selection function of our mergers.
-For instance, if all of our stage 4 classifications were actually high redshift stage 3 galaxies, we would observe this in our selection function.
-Therefore, Figure \ref{fig:redshift_selection} shows our selection functions across our redshift range for each defined stage in our interaction.
+For instance, if all of our stage 4 classifications were actually high redshift and high mass stage 3 galaxies, we would observe this in our selection function.
+Therefore, Figure \ref{fig:redshift_selection} shows our the distribution of stellar mass across our redshift range for each defined stage in our interaction.
 As shown, the distribution of masses across redshift that we find in our sample is reasonably consistent with each other.
-This means we are likely not affected by surface brightness dimming across our sample and our redshift range.
 
@@
 The second issue that could affect our sample is that of contamination by close pairs by projection effects rather than by galaxies which are physically close together.
-For the majority of these systems, we are limited to only having their calculated photometric redshift from the COSMSO2020 catalogue and not their well-constrained spectroscopic redshift.
+For the majority of these systems, we are limited to only having their photometric redshift from the COSMSO2020 catalogue and not their well-constrained spectroscopic redshift.
 As we are conducting visual classification, this issue is rather limited.
@@
 Each source is confirmed to have some kind of tidal feature f=present in the image, even if a secondary is not present in the image.
-There are, always, of course other galaxies in each image and there is no guarantee that the calcualted photometric redshift is correct.
-WE often find galaxies which are clearly interacting or paired, but with the photometric wildly different.
+There are, always, of course other galaxies in each image and there is no guarantee that the calculated photometric redshift is correct.
+We often find galaxies which are clearly interacting or paired, but with the photometric wildly different.
 In these cases, we defer to the redshift and only record one of the galaxies in our sample.
@@
 \section{METHOD: Environment, AGN and Interaction Stage} \label{method}
-In this section, we describe how we separate our sample of 4,181 interacting galaxies into separate stages.
-Each stage is defined to capture a different part of the interaction, and a different part of the dynamical history of the interaction.
-We want to compare different stages in the interaction to different physical underlying processes, such as star formation rate.
-Such parameters can be found in the COSMOS2020 catalogue.
-However, two fundamental properties we also want to compare with is that of AGN fraction evolution with time and that of environment, and the impacts this might have.
-
+A primary aim of this work is to investigate the evolution of different galactic parameters with stage of the interaction.
+Each stage is defined to capture a different part of the dynamical time and merger history.
+This stage also relates to the projected separation of galaxies with an identified secondary.
+Here, we fully define what we mean by interaction stage and which part of the dynamical time it covers.
+We also describe how we find AGN in our full sample and find measurements of the environment about each.
 The parameters required to calculate the AGN fraction are not found in the COSMOS2020, and we therefore must cross match with other catalogues to find the required parameters.
-We also describe the catalogue we use here to define the density parameter around each of our sources, and define how the environment is calculated there.
+We also describe the catalogue we use to define the environmental density about each of our sources.
+This is important to consider, as it is well known that measured SFRs of galaxies can be affected by environment, as well as existing biases in where interacting and merging galaxies reside.
+We, therefore, need to check that we have not introduced any environmental biases into our definition of interaction stage.
 
@@
 The primary goal of this work is to find if a relation exists between a host of galactic parameters, underlying physical processes and the stage of the interaction.
-We, therefore, need to define different stages for them.
-We have hinted at this in the previous section with Figure \ref{fig:secondaries_found}.
-We break our sample down into four stages:
+Each stage covers a different part of the dynamical history in an interaction and, in this case, we define it based on the morphology and projected separation between systems.
+WE define four dinstinct stages of interaction:
 
 \begin{itemize}
-    \item Stage 1: Systems which are well-separated with little to no morphological disturbance.
-    \item Stage 2: Close pairs showing either morphological distortion or physical connection by tidal features.
+    \item Stage 1: Systems which are well-separated with little to no morphological disturbance (Close pairs).
+    \item Stage 2: Close pairs showing morphological distortion while still in a pair or show a physical connection by tidal features.
     \item Stage 3: Well separated pairs with morphological disturbance or isolated galaxies with clear tidal features.
-    \item Stage 4: Highly disturbed systems with two or more cores within.
+    \item Stage 4: Highly disturbed systems with two or more cores within them.
 \end{itemize}
 
-\noindent Examples of each stage can be found in Figure \ref{fig:stages}. Each stage is designed to capture a different part of the interaction history of a system in the total dynamical time.
+\noindent Figure \ref{fig:stages} shows the original OR23 source cutouts of an example galaxy in each stage.
+There are degeneracies associated with this staging system, however.
+In this context, we define a degeneracy as when the interacting galaxies may be at two or more parts of the dynamical timescale and we have no way to tell without further information on the system.
 
@@
 
-Stage 1 of the interaction captures the first approach of the two systems.
-This is the time when the two galaxies potentials are beginning to have an effect on one another.
+Stage 1 of the interaction captures the first approach of the two systems and they are observed as a galactic pair.
 They have no morphological disturbance yet and, in our sample, are most often those galaxies with distinct disks.
-Hence, this stage has the highest number of if identified secondaries with every system having a secondary that can be visually classified.
-In this sample, we would expect no effects from the interaction to have began yet.
+At this point, we would expect no change in the underlying processes of the galaxies from their control samples.
+Interaction has not taken place yet, and the two systems are morphologically intact.
+By definition, this stage requires an identified secondary galaxy and therefore has the highest number of identified secondaries with every system having a secondary that can be visually classified.
+This is also the least degenerate part of the dynamical time we are sampling due to a criteria being no morphological disturbance.
+Therefore, it is unlikely that the galaxies would have already flown by each other.
 
-Stage 2 of the interaction is defined as the point where the two galaxies in the interaction are approaching or just passing the pericentre of the tidal encounter.
-For those galaxies before pericentre, we would expect the beginning of morphological disturbance or some irregularity in the two systems.
-Once the galaxies have passed pericentre, we would define it by much higher morphological disturbance, distortion and tidal debris.
-This requirement for morphological disturbance is how we differentiate stage 2 from stage 1 interacting galaxies.
-Throughout this stage of the interaction, in our sample, we see significant overlap or connection of the two systems in the form of tidal features and morphological distortion.
+Stage 2 of the interaction is defined as the point where the two galaxies in the interaction are are at or just passing the pericentre of the tidal encounter.
+At this point, we find the beginning of morphological disturbance, the beginning of the formation of tidal features and some tidal debris.
+Due to the two systems having to overlap or connect via tidal features - by definition - this is the stge that suffers most from limited identification of the secondary galaxy.
+The COSMOS2020 catalogue often defines these two systems as a single system, and therefore, we lack information about their secondary.
+This stage is also highly degenerate in the context of the dynamical timescale of the interaction.
+Without further information, we are unable to define whether the galaxies involved at this stage are at the first, second, third, etc passage of the tidal encounter.
+We also do not know if they are just passing pericentre on the first pass, or if they are approaching pericentre on more than one pass.
 
-Stage 3 interacting galaxies are described as those interacting systems where the systems have approached apocentre from each other.
-In many of cases of this stage, if the galaxies have sufficient velocity, the galaxies will escape each other and not coalesce.
-Hence, galaxies at this stage often could not have a secondary galaxy identified in our visual assessment.
-We purely describe a galaxy as stage 3 based on significant tidal and morphological disturbance.
+Stage 3 describes those interacting systems where the two disks are fully separated and distinct from one another.
+They must have some morphological disturbance associated with them, but do not require a secondary galaxy to be put into this stage as if the galaxies have sufficient velocity they would escape from each other and, therefore, their secondary could be outwith our COSMOS2020 cutouts used to visually identify them.
+This is reflected in an even distribution of finding the primary and secondary in this stage.
+This stage is also defines a large part of the dynamical timescale.
+It spans from separating from the secondary and after pericentre, to moving out to the apocentre of the interaction (or escaping with sufficient velocity), to falling back in towards the secondary galaxy again.
+Without velocity information, we have no way of finding if the galaxy is moving away or moving towards its secondary.
 
@@
 If the two galaxies do not have sufficient velocity to escape one another, then they go on to coalesce and ultimately merge.
-We define this stage such that the sample is of galaxies just before this coalescence and the two cores remain distinct.
-However, it is important to note that this stage may be contaminated by some post-merger remnants.
-In this context, we define a stage 4 galaxy as one with significant morphological disturbance but with multiple cores present in the disks.
-At this stage, the interaction is at it's most violent with complete disruption of both galactic disks.
-We also expect star formation rate to increase significantly in this stage.
-This is important to note, as high star forming at specific redshifts in the $F814W$ filter may appear like a second core within a galactic disk.
-At this point, we would be observing a post-merger remnant rather than the point just before coalescence.
-Therefore, to mitigate potential contamination in from the post-merger stage we only classify stage 4 galaxies as those with highly disrupted disks and second cores close to the primary core (and not far out in the disk).
+We define this stage through the severe morphological disturbance of the galaxy involved as well as the existence of a second core within it.
+While we attempt to capture only pre- or ongoing-coalescing systems, it is important to note that this stage is degenerate to post-merger remnants which will also be accepted by our criteria.
+Post-merger remnants are systems where coalescence has been completed and immediately after will be highly morphologically disturbed and difficult to distinguish from those systems with merging ongoing.
+At this stage, we would expect the interaction will be at it's most violent with complete disruption of both galactic disks and likely increased star formation across the disk.
 
 Our four stage approach is not a new one, and many other works have utilised it to differentiate different parts of the dynamical history of a galaxy interaction \citep{2022ApJ...937...97C, 2023ApJ...952..122G}.
-It is, however, important to note its limitations.
-First, this is a simplified view of the dynamical timescale of an interaction.
-We have assumed that an interaction begins, the pair have enough velocity to escape or they coalesce and that is representative of the full dynamical timescale.
-We have not considered systems where there are multiple flybys before coalescence or systems where there are multiple members at different stages of the interaction.
-This is a particular concern when looking at stages 2 and 3.
-For instance, the effects could be enhanced or diminished over multiple flybys, and we have no way to capture this.
+We have noted the degeneracy of each stage as we have described them.
+Thus, we can now put this fully into the context of the dynamical timescale.
+Over a typical interaction, we would expect the galaxy pair to always move from stage 1 to stage 2 in the early times of the dynamical timescale.
+Then, dependent on the velocity of the system, the galaxy pair will either move straight into stage 4 of classification and begin to merge or it will move into stage 3.
+This change from stage 2 into stage 3 can then take many branching paths dependent on the elocity in the system.
+If the galaxies have sufficient velocity, stage 3 will be their end state until the tidal features slowly dissipate.
+If they do not have velocity to escape on another, the system will move from stage 3 back into stage 2.
+This could then happen for many cycles until finally the galaxies enter stage 4 and coalesce.
+Figure \ref{fig:illustration} shows the branching paths that the galaxies can take through each stage.
+Note, these are created using the PySPAM restricted numerical simulation (O'Ryan et al.
+in prep.) and are for illustrative purposes only.
 
-We relate our classification of stage to projected separations between systems, more often used in the literature, by using our confirmed galaxy pair subsample.
+\begin{figure*}
+    \centering
+    \includegraphics{}
+    \caption{Sorry, I wan't able to create this figure in the editing phase of this paper! But this will be added as soon as I have a small breather, absolutely love the idea of it.}
+    \label{fig:illustration}
+\end{figure*}
+
+More commonly, in the literature, rather than using the stage of an interaction based on morphology we use the projected separation of the two systems.
+To explore the difference between using our staging system and the projected separation, as well as to ensure we recover the expected relations, we measure the projected separations of our confirmed galaxy pairs.
 Figure \ref{fig:proj-seps} shows the stage classification with projected separation between the two pairs.
-The projected separation is measured by taking the average of the best fit photometric redshifts between the two galaxies, and converting their angular separation to a physical one.
-The most dinstinct separation in stages in between stage 2 and stage 3.
-Here, we see that stage 2 is dominated by systems with a projected separation $<$35kpc while stage 3 is dominated $25 \leq s_{proj} \leq 100$ kpc.
-This is to be expected from our definitions of stage.
+We measure this by taking the average of the best fit photometric redshifts between the two galaxies, and converting their angular separation to a physical one.
+The most distinct projected separation ($s_{proj}$) in stages is between stage 2 and stage 3.
+Here, we see that stage 2 is dominated by systems with $s_{proj}<$35kpc while stage 3 is dominated $25 \leq s_{proj} \leq 100$ kpc.
 Stage 2 is visually classified as systems which are highly morphologically disturbed, while either being morphologically linked to each other or overlapping.
 Those galaxy pairs with large projected separations are pairs which are very large in angular size, while still overlapping or morphologically linked.
-If this criteria is not met, then the system becomes a stage 3 interaction where the two galaxies in the pair are completely dinstinct.
+If this criteria is not met, then the system becomes a stage 3 interaction where the two galaxies in the pair are completely distinct.
 There is some overlap between the projected separations of stage 2 and stage 3 as this is somewhat dependent on the angular size of the two systems involved in the interaction.
 
-We will investigate the parameters which are proxies for the underlying physical processes of our sample and interpret them.
-We will investigate whether we see have a bias in our systems based on environment, whether we find increased AGN activity and if we observe enhancement in star formation with stage.
-The star formation rate is already present in the COSMOS2020 catalogue from both EAzY and LePhare.
-For the environment parameter and whether AGN are detected, we cross match to two further catalogues.
-We describe these catalogues here, our process of cross matching and the new sample sizes we have in each subsample.
+We will use the projected separation to investigate relations between AGN activity and if we observe enhancement in star formation with stage.
+The SFR is already present in the COSMOS2020 catalogue from both EAzY/FAST and LePhare.
+To ensure that any enhancements are from interaction alone, we must ensure we have no bias' in the environment distribution of our sample and identify AGN.
+We, therefore, cross match to two further catalogues COSMOS catalogues containing the required information.
 
@@
 However, in this work, we utilise the existing environmental density catalogue produced by \citet{2017ApJ...837...16D}.
-This catalogue was created specifically for the COSMOS survey, and has a measured density for all sources with mass $\log(\frac{M}{M_\odot}) \geq 9.6$ and out to a redshift of 1.2.
-In this catalogue, they calculate not only the density, but also the density parameter $\delta$ and assign each source to a field, filament or cluster classification.
+This catalogue was created specifically for the COSMOS survey, and has a measured density for all sources with mass $\log(\frac{M}{M_\odot}) \geq 9.6$ and $z \leq 1.2$.
+\citet{2017ApJ...837...16D} calculate not only the density, but also the density parameter $\delta$ and assign each source to a field, filament or cluster classification.
 For a full description of how they calculate the environment and density field see \citet{2015ApJ...805..121D} and \citet{2017ApJ...837...16D}, but we will briefly describe it here.
 
-To build the density field throughout the COSMOS field, they first construct a set of overlapping redshift slices.
+To build the density field throughout the COSMOS field, \citet{2017ApJ...837...16D} first construct a set of overlapping redshift slices.
 Within each slice, a subset of the galaxies are selected such that the median of the probability distribution function (PDF) of their photometric redshift is within it.
@@
 The result of this process, and the cuts defined previously, is a catalogue of $\approx$45,000 galaxies with their densities accurately measured.
-As advised with the catalogue, we remove any sources which are flagged as uncertain.
-This is recorded in the catalogue.
-This leaves us with $\approx$39,000 sources with which to cross match the OR23 sample.
+We remove any sources which are flagged as uncertain from the catalogue (a flag existing within it) providing us with $\approx$39,000 sources with which to cross match the OR23 sample.
 We apply the same cuts to our sample as applied in \citet{2017ApJ...837...16D}, and only consider those systems with a mass $\log(\frac{M}{M_\odot}) \geq 9.6$.
-To cross match with our sample, we simply utilise the COSMOS2015\_ID which is recorded in the COSMOS2020 catalogue which corresponds to the ID in the \citet{2017ApJ...837...16D} catalogue.
-We find that every source in our COSMOS2020 sample has a COSMOS2015 ID associated with it, and therefore we fully match the reduced catalogue.
-
+To cross match with our sample, we simply utilise the COSMOS2015\_ID which exists in both the COSMOS2020 catalogue and the \citet{2017ApJ...837...16D} catalogue.
 Upon applying the mass cut to our sample, we find that we are matching 2,800 sources to the \citet{2017ApJ...837...16D} catalogue.
@@
 \subsection{Classifying AGN}\label{sec:agn-clsf}
-\noindent We will also investigate the affect of interaction stage upon the AGN activity within the galaxies involved.
-Unfortunately, the outputs of EAzY and LePhare do not provide us with photometric estimates of the line fluxes needed to define an AGN on a Baldwin, Philips and Terlevich (BPT) diagram.
-Therefore, we cannot directly identify if a galaxy is only star forming, has nuclear activity or is a composite.
-So, we turn to cross-matching our sample to three different catalogues which contain the required information.
-We use the Chandra COSMOS Legacy Survey Multiwavelength Catalogue \citep{2016ApJ...817...34M} and the COSMOS VLA 3GHz survey \citep{2017A&A...602A...6S, 2017A&A...602A...3D}.
-Each source has an AGN, star forming or composite classification is within the catalogue.
+\noindent We will also investigate the effect of interaction stage on AGN activity throughout our sample.
+As the COSMOS2020 catalogue does not contain the relevant parameters to make this calculation, we turn to the Chandra COSMOS Legacy Survey Multiwavelength Catalogue \citep{2016ApJ...817...34M} and the COSMOS VLA 3GHz survey \citep{2017A&A...602A...6S, 2017A&A...602A...3D}.
+Both of these catalogues span the entire COSMOS area, and contain detailed classifications of the sources they find.
+The Chandra survey spans the X-ray range of wavelengths, and successfully identified numerous X-ray AGN.
+The VLA 3GHz survey is a radio survey, and we use this to find the radio AGN through our sample.
 
-% Need a small paragraph here about these two catalogues and their differences.
-
-Again, our cross match process is very much the same as previously described.
+Our cross match process is very much the same as previously described.
 We use the previously identified COSMOS2020 source coordinates and conduct a radial search of 10".
 If more than one source is within this radius, we match on the closest source.
-The two catalogues derived from the COSMOS survey do not contain IDs which overlap with the COSMOS2020 catalogue, therefore we must do it based on coordinates.
-We conduct our matching in serial, starting from the \citet{2017A&A...602A...6S} catalogue and then to the Chandra survey.
+We first find matches of radio AGN using the VLA 3GHz survey catalogue and then search the Chandra survey.
 At every step, if we find a match in the relevant catalogue, we remove it from subsequent searches in other catalogues and take the first classification as the correct one.
@@
 We also investigate cross matching with the MPA-JHU catalogue \citep{2003MNRAS.341...33K, 2004MNRAS.351.1151B, 2007ApJS..173..267S}, however, found that all matches were already represented by the VLA and Chandra surveys.
-Therefore, we only utilise these two catalogues in our sample.
+We also utilise the COSMOS XMM-survey and, again, find no new sources to add to our sample.
+While the ratio of AGN to star forming galaxies in our sample seems large compared to other works, it is important to note that this is a result of limited matching between the catalogues.
+Of the 4,181 galaxies in our sample, only 1,214 appeared at all in either the VLA or Chandra catalogues.
+Any galaxy which did not appear in these catalogues, we discard as unclassified.
 
-While the ratio of AGN to star forming galaxies in our sample seems large compared to other works, it is important to note that this is a result of limited matching between the catalogues.
-Of the 4,182 galaxies in our sample, only 1,214 appeared at all in either the VLA or Chandra catalogues.
-Any galaxy which did not appear in these catalogues, we discard as unclassified.
-Therefore, we require these catalogues to specifically show us if a galaxy is star forming or not before we classify it as such.
-
-\section{STAR FORMATION EVOLUTION WITH INTERACTION STAGE}\label{results}
+\section{STAR FORMATION EVOLUTION WITH INTERACTION STAGE}\label{results:SF_stage}
 \subsection{Controlling for Interaction Stage}
-\noindent With our samples selected we investigate the change in multiple parameters with stage of the interaction.
-As stated previously, the four stages of interaction are designed to capture the main different parts of galaxy interaction.
+\noindent With the above samples selected, we investigate the change in multiple parameters with stage of the interaction.
+The four stages of interaction are designed to capture the main different parts of galaxy interaction.
 First, we show the results of breaking down our sample into stages with relation to the star formation and mass of our sample.
 We utilise the estimates of these parameters that exist in the COSMOS2020 catalogue itself.
-We have the option to use either the measured estimates from LePhare or EAzY.
-We opt to use the stellar mass measured from LePhare and the star formation rate measured with EAzY for our final results.
-We choose this as using any other combination reveals the degeneracys of the SED template fitting conducted in either of the underlying softwares.
-Figure \ref{fig:difference-measures} shows how the two measures differ from each other.
-As shown, EAzY measures larger stellar masses compared to LePhare while the scatter in SFR is very large.
+Then, we utilise our subsample of galaxy pairs to recover the relationship between projected separation and star formation enhancement (SFE).
+We then further break this measure down into it's component stages.
 
-\begin{figure}
-    \centering
-    \includegraphics[width=0.45\textwidth]{figures/mass-sfr-scatter.pdf}
-    \caption{Comparison of the measures of stellar mass and SFR using either LePhare or EAzY photometric codes to calculate them.
-\textit{Left}: The scatter in the stellar masses between softwares.
-As shown, EAzY often seems to find larger stellar masses when compared to LePhare.
-\textit{Right}: Scatter in SFRs when measured with LePhare or EAzY.
-There is a large difference between the measures of LePhare and EAzY here, and therefore we opt to only use EAzY measures of the SFR through this work.}
-    \label{fig:difference-measures}
-\end{figure}
-
-As the measure of the masses between the softwares is similar, we can interchange which mass we use in these measurements.
-However, with the very large scatter of the SFRs between the softwares, we opt to only use the EAzY measurement.
-% Where do these differences come from?
-What potential impact could this have on our results?
-
-With the measures of stellar mass and SFR selected, we break down our sample into their different stages.
-Figure \ref{fig:sfr-mass} shows the breakdown of these parameters with stage.
+Figure \ref{fig:sfr-mass} shows the breakdown of stellar mass and SFR with stage.
 On a population scale, there is clear evolution in the star formation rate from stage 1 through to stage 4.
 In stage 1, where the galaxies are distinct from one another with no clear morphological disturbance, we clearly see two populations of galaxies.
-These are the blue, star-forming and red sequences.
-The contours of number density in Figure \ref{fig:sfr-mass} bring out this population.
-In stage 2, when the galaxies are at pericentre, this red sequence remains but is highly diminished while the star forming sequence remains constant.
+These are the blue, star-forming galaxies and red sequence of galaxies.
+The blue contours in Figure \ref{fig:sfr-mass} show increasing number density in the population into the blue cloud.
+In stage 2, when the galaxies are actively interacting and overlapping, this red sequence remains but is highly diminished while there is no change in the blue cloud.
 Stage 3 shows a similar effect, where the red sequence reduces again before finally in stage 4 the red sequence completely disappears.
+Through these, the blue cloud remains highly populated and hosts the majority of galaxies in the sample.
 
@@
 However, this result could also be due to many other factors rather due to interaction stage.
-For instance, if the mass distribution of our sources evolves as well, it could just be that we are selecting higher mass systems in stage 4 when compared to stage 1.
+For instance, if the mass distribution of our sources evolves as well, we could simply be selecting higher mass systems as we increase stage.
 This would have the result of systems in stage 4 having, on average, higher SFRs than those in stage 1 and appearing like we had evolution in the star forming population with stage.
 Another effect that could cause this relation to appear would be our selection was highly dependent on galactic environment.
-It is well known that environment and star formation are closely linked, and that classifying interacting galaxies by morphology classifiers can weight up the cluster environment over galaxies in the field.
-In Section \ref{sec:env-cont}, we control for the environment in our sample and show that this is not an issue.
+It is well known that environment and star formation are closely linked, and that classifying interacting galaxies by morphology classifiers can weight up galaxies in cluster environments over galaxies in the field.
+In Section \ref{sec:env-cont}, we control for the environment in our sample and show that this is not the case.
 Here, we investigate the question of the evolution of the mass distribution that could give us this result.
@@
 We can quantify the similarity of the mass distributions, and then the SFR distributions, using well known statistical tests.
-We opt to use two different tests: the KS-test and the Shapiro-Wilkes test.
-The KS-test is excellent at comparing different weighted distributions to each other, while the Shapiro-Wilkes test compares these distributions to other well known functions (in our case, the normal function).
-Thus, by weighting the mass distributions and using a KS-test, we will be able to quantify how alike the mass distributions are and then compare this to the weighted distribution of the SFRs.
-The weighting scheme we utilise normalises the distributions such that each bin in the distribution had the same number of sources within it.
-Therefore, any bins with few than the average number of sources will be weighted up while those bins with more will be weighted down.
-These weights applied to the mass distribution are then applied to the SFR distribution so the counts in each bin are, essentially, the same.
+We opt to use two different tests: the Kolmogorov-Smirnov \citep[KS-test;][]{an1933sulla} and Anderson-Darling \citep[AD-test;][]{stephens_74}.
+The KS-test is excellent at comparing different weighted distributions and indicating if they are drawn from the same parent sample.
+The AD test tests for this similarity as well, and we utilise both to ensure consistency and robustness in our measurements.
+First, we create weighted distributions of stellar mass.
+The weighting scheme we utilise balances the distributions such that each bin could be assumed to have the same number of sources within it.
+Therefore, any bins with fewer than a certain number of sources will be weighted up while those bins with more will be weighted down.
+These weights applied to the mass distribution are then applied to the SFR distribution as to control for stellar mass in this distribution.
 
@@
 Figure \ref{fig:weighted-mass} shows the weighted mass distributions through the four different stages.
-These appear highly similar, and we conduct Kolmogorov-Smirnov \citep[KS-test;][]{an1933sulla} and Anderson-Darling \citep[AD-test;][]{stephens_74} tests to compare each distribution.
-In each test, we calculate the value of the KS test and a p-value which is the probability that each distribution is drawn from the same parent distribution.
-For each mass distribution, we find that p-value of the KS test is approximately one.
-Thus, it is not unreasonable to assume that the galaxies between each of our samples are drawn from the same parent sample and are very similar.
-Figure \ref{fig:weighted-sfr} shows the SFR distributions while being weighted and controlled for mass.
+These appear highly similar, however to statistically measure the similarity we apply our KS- and AD-tests to them.
+We chain the KS- and AD- test through each distribution and calculate the value of the test values and a p-value.
+This p-value represents the probability that each distribution is drawn from the same parent distribution.
+For each mass distribution, we find that p-value of both tests is approximately one.
+Thus, proving that the distribution ins tellar mass though each stage is very similar, and no stellar mass evolution is occurring.
+Figure \ref{fig:weighted-sfr} shows the SFR distributions while being weighted by stellar mass.
 When comparing stages 1 and 2, 1 and 3, 1 and 4, 2 and 4 and 3 and 4, the p-values are $\ll$0.05.
-Thus, we can reject the null hypothesis for these distributions and assume they are from different parent samples and are not identical.
+This allows us to reject the null hypothesis for these distributions and assume they are from different parent samples and are very disimilar.
 However, for comparing stages 2 and 3, the p-value of the KS test is $\approx$0.90.
 Thus, while these distributions are likely to be not identical, they are very similar in the parent sample they have been drawn from.
-\textbf{Thus, for the same mass distribution through each stage of interaction, the star formation distribution radically changes from stage 1 to stage 2 and from stage 3 to stage 4, while remaining reasonably similar from stage 2 to stage 3.}
+\textbf{For the same mass distribution through each stage of interaction, the star formation distribution radically changes from stage 1 to stage 2 and from stage 3 to stage 4, while remaining reasonably similar from stage 2 to stage 3.}
 
-Putting this result into the context of the dynamical timescale of an interaction, it shows there are three separate stages star formation evolution in these systems.
-The first is the change from isolated SFRs to interacting SFRs.
-Here, the SFR between galaxies which are close pairs and those that are at pericentre are radically different.
-This difference persists through to stage 3 - where the galaxies are at pericentre in the interaction.
+Putting this result into the context of the dynamical timescale of an interaction, it shows there are distinct points at which the SFR changes in these systems.
+The first is when the interacting system moves from being a close pair to actually morphologically disturbing each other in a close flyby.
+This difference, most likely enhancement, then persists through through to stage 3 - where the galaxies remain highly disturbed but are no longer overlapping with their secondary.
 The SFR distribution remains approximately the same between these two, meaning the forces that drive and affect star formation remain equivalent between these two stages.
@@
 
-We also control for redshift in our examination of this result.
-While the red sequence is significantly reduced across stage, it is important that we put this into the context of the star forming main sequence of galaxies.
-We expect that, due to an interaction, the population of starbursting and quiescent galaxies will change with stage.
-Therefore, we define a star forming main sequence through across redshift.
+We further examine this result by controlling for redshift and making specific classification of galaxy type.
+While the red sequence is significantly reduced across across each stage, it is difficult to ascertain the change in the galaxies within the blue cloud.
+We expect that, due to an interaction, the population of starbursting and quiescent galaxies will change.
+Therefore, we define a star forming main sequence (SFMS) through across redshift.
 This allows us to classify each source based on its SFR independently of redshift.
-To define the star forming main sequence (SFMS), we follow the example of \citet{2019MNRAS.484.4360A}.
+To define the star forming main sequence, we follow the example of \citet{2019MNRAS.484.4360A}.
 There, they define the star forming main sequence as a function of galactic stellar mass and redshift as
@@
 \noindent We split our sample into its different stages and apply these criteria.
-Figure \ref{fig:sfr-clsf} shows the ratio between the expected SFMS SFR and the found SFR in COSMOS.
+Figure \ref{fig:sfr-clsf} shows the ratio between the expected SFMS SFR and the measured SFR in the COSMOS2020.
 This clearly shows a large increase in galaxies classified as starburst from stages 1 to 4 and a large reduction in the number of quenched systems.
-Figure \ref{fig:sfr-clsf-bar} shows the change in fraction of the different galaxy classifications through stage.
-These Figures reflect the results found in Figure \ref{fig:sfr-mass}.
+Figure \ref{fig:sfr-clsf-bar} shows the change in fraction of the different galaxy classifications through stage, reflecting the results found in Figure \ref{fig:sfr-mass}.
 Initially, in stage 1, we find that the majority of our galaxies lie on the SFMS or just below it.
-There also exists a small population of galaxies which are classified as a starburst with a population of quiescent galaxies that is roughly double the fraction.
+There also exists a small population of galaxies which are classified as starburst with a population of quiescent galaxies that is roughly double the starburst fraction.
 As we move through the interaction stage, we see that the quiescent galaxy fraction gradually decreases to the point of almost non-existence in stage 4 galaxies.
@@
 The fraction of galaxies on the SFMS remains dominant throughout, however, we do find the fraction of sub-MS galaxies significantly reduced.
+Thus, we find that, in general, the SFR of these galaxies is increasing with interaction stage (though, not in stage 2 - 3), but not hugely.
+It appears to have sub-MS and quiescent galaxies move up and join the SFMS (as it remains dominant).
+But, many galaxies from the SFMS are moved upwards and into a starbursting phase.
 
@@
 
-% So, what does this all mean?
-Thus, we find that throughout the different stages of interaction the star formation within the systems is being driven upwards.
-We have found here is that this process of increasing SFR and galaxies being driven to starburst begins from the pericentre of the first interaction.
-Simulations have long showed that there is a peak in SFR initially in an interaction, followed by a slow reduction to a final enhanced level in the post-merger stage.
-However, due to the initial starburst, it is often shown that the gas within the galaxy is either quickly used up and the galaxy quenches or it is heated to the point that star formation becomes very inefficient.
-Thus, what we would expect to see here is that stages 2 and 4 would have the highest fractions of galaxies undergoing a starburst and the smallest quiescent fractions.
-
-Our work here is found to be correct by both simulations and previous works on when the starburst occurs in an interacting galaxy.
-We observe significant change in the starburst and quiescent fractions from stage 1 to 2 and stage 3 to 4.
-Thus, the initial part of the interaction appears to have a significant impact on the SFR (and, therefore, the gas content) of the galaxies involved.
-This enhanced star formation then persists through the interaction, even when the other galaxy approaches the apocentre of the interaction.
-This is seen by the relatively little change in the SFR classifications from stage 2 to 3.
-While the fraction of MS galaxies does increase slightly, the fraction of starburst galaxies remains essentially constant.
-There is also no major change in the quiescent fraction either.
-However, it is interesting to note that the sub-MS fraction does decrease.
-Thus, the transition to stage 2 to stage 3 of an interaction may bring with it slight enhancement in the SFR, but not on the scale of the other transitions in interaction stage.
-We then see clear evidence for a second starburst is being driven by the merging of the systems that goes beyond even the enhanced from the initial pericentre passage.
-
-So, what does the SFR evolution look like from our results?
-As the interactors approach each other, they are representative of a control sample where there is a population of quiescent, MS and starburst galaxies.
-However, upon transitioning from stage 1 to 2, the disturbance due to interaction provokes increased fragmentation of a galaxies gas and leads to an increase in star formation.
-This is true even of the galaxies which have very little gas remaining, as the quiescent fraction reduces significantly in our sample.
-This enhancement persists from stage 2 to stage 3, where we see no major change in the classification fractions.
-Then, upon merging and transitioning to stage 4, we find that even the most gas-empty galaxies begin forming stars quickly.
-
 Now, it is important to note the parameter space that we are searching in these examples.
-We are probing major interactions between galaxies, where the resultant tidal features that form would be classifiable in an image.
+We are probing interactions between galaxies of high mass, where the resultant tidal features that form would be classifiable in an image.
 Hence, even those mergers which are considered dry - with very little gas - would be capable of driving major rejuvenation in the star formation of these systems.
-To conclude, \textbf{we find clear, statistically robust evolution of a galaxys' SFR with interaction stage.
-The SFR changes dramatically from stage 1 to 2 and stage 3 to 4 - at the pericentre and coalescence of the interaction.
-Existing simulations of galaxy interactions support this interpretation of when star formation changes.}
+However, we do not see a significant increase in the starbursting population until we the two galaxies begin to actually coalesce.
+However, \textbf{we find clear, statistically robust evolution of a galaxys' SFR with interaction stage.
+The SFR changes dramatically from stage 1 to 2 and stage 3 to 4 - after the initial passage of closest approach and at the point of coalescence of the interaction.}
 
 \subsection{Projected Separation and Star Formation Enhancement}
-\noindent To further confirm this result, we directly investigate the relation between the star formation enhancement (SFE) and the projected separation using our confirmed sub-sample of galaxy pairs.
-This sample is significantly smaller than our non-pair sample: containing 480 pairs or 960 galaxies.
+\noindent We directly investigate the relation between the star formation enhancement (SFE) and the projected separation using our confirmed sub-sample of galaxy pairs.
+This sample is significantly smaller than our non-pair sample: containing 480 pairs or 960 galaxies (we have also added some pairs from the additional interacting galaxy sample).
 Upon sub-dividing this into different stages we find 310 stage 1 galaxies, 146 stage 2 galaxies and 498 stage 3 galaxies.
@@
 
-To measure the SFE of our galaxy pairs, we directly compare the to the control sample that was also created with this sub-sample and defined in Section \ref{sec:sec-ident}.
-We separate our galaxy pair sample into different bins based on the projected separation between them.
+To measure the SFE of our galaxy pairs, we directly compare to the mass- and redshift-matched control sample that was also created with this sub-sample and defined in Section \ref{sec:sec-ident}.
+We separate our galaxy pairs into different bins based on the projected separation between them.
 We find that the bulk of our sample has a projected separation between the two galaxies of $\leq$50kpc.
@@
 
-We create distributions based on these bins of projected separation: one of interacting galaxies and the other of our control galaxies.
-We then take the average of each bin separately, before dividing each distribution by the other.
-By taking the average of each bin, we are finding the total excess of the SFR caused by interaction alone and then comparing it to what we would expect from non-interacting galaxies in the same bin.
+We create two projected separation distributions: one of interacting galaxies and the other of our control galaxies.
+We then take the average of each bin.
+By taking the average of each bin, we find the total excess of the SFR caused by interaction alone and then comparing it to what we would expect from non-interacting galaxies in the same bin.
 Note, that the control galaxy relation to the projected separation is meaningless as they are not paired.
@@
 On the left of the plot, we have the distribution for the full galaxy pair sample, without taking account of stage.
-The error bars are calculated based on the counts within the bin and errors on the underlying SFRs of the galaxies within.
+The errors on our measurements are calculated as the standard deviation from the mean within the bin.
 The dashed black line represents no enhancement in SFR, as the average SFR in the interacting galaxy sample would be equal to the average SFR in the control sample.
 We find at very small projected separation a SFR enhancement of 1.87 which gradually decreases with projected separation down to approximately 1 at 117.5kpc.
+
 On the right, we break the galaxy pair sample into different stages and plot out the resultant enhancement in star formation.
 This shows very different behaviour in enhancement dependent on the stage of the interaction.
-
-In stage 1, we find that the star formation is very weakly enhanced, at a level of approximately 1.25.
-As we increase the projected separation bins, the enhancement then changes around an enhancement of 1, even dropping below 1 at 40kpc.
+In stage 1, we find that the star formation is very weakly enhanced, and with no overall structure.
+The enhancement moves around 1 through the distribution, with some enhancement being a result of low number counts in the bin.
 Taking into account the errors on our measurements, the true value of the enhancement could be around 1 for the entire projected separation distribution.
@@
 After 150kpc, our galaxy pair sample does not have the counts to make robust estimates of the SFE.
-
-Finding that the SFE declines with projected separation is not an unexpected.
-Previous works also find this and even match our results \citep{2000ApJ...530..660B, 2008AJ....135.1877E, 2013MNRAS.433L..59P}.
-Where our result differs is by taking into account the stages of the interaction.
-\textbf{While using only projected separation is a proxy for stage, we find the actual SFE is also dependent on the time of in the dynamical timescale the interaction is}.
-For instance, all of our stage 2 systems have high SFE of greater than 1.5 no matter the projected separation between them.
-This shows that the morphological connection and overlap of the two systems is driving the enhancement.
-Then, moving to stage 3 with low projected separation, we see the SFE grows even larger to 2.5.
-The galaxy pair will be just at the point of breaking overlap and morphological connection here, only just moving away from pericentre here.
-Simulations have predicted that once the two systems are just passed pericentre and moving away from each other, the two galaxies will undergo an intense delayed starburst \citep{2015MNRAS.448.1107M}.
-We see this effect in the sudden increase in SFE as the two galaxies disconnect from each other and begin to move away from one another.
-
-These distributions of SFE paint a picture of the disturbance and change in the SFRs of these systems throughout the interaction, we will summarise here.
-First, in stage 1, the two systems move towards one another (or away with little disturbance) with no SFE and matching the control.
-Upon entering into stage 2, the galaxies SFR dramatically increases due to the morphological disturbance of the two disks and potential overlapping and linking of the two systems.
-Then, once the two systems are past pericentre and enter into stage 3 to flyby one another, the gravitational torques on the two systems take hold and star formation is, again, dramatically increased.
-This increase relaxes as the systems move towards apocentre and higher projected separations.
-
 However, it is important to note that this result has been found with a sample of 960 interacting galaxies in their pairs.
@@
 
-We conduct weighted KS and AD tests on the environment distributions, and confirm they are likely drawn from the same parent sample.
-The resultant p-values are $\approx$1 when comparing between the distributions.
+We conduct weighted KS and AD tests on the environment distributions, and confirm they are likely drawn from the same parent sample, with the resultant p-values $\approx$1 the distributions.
 Thus, there are no biases in our stage selection with environment, and it fair to assume that the evolution in the SFR with stage is due to interaction, not environment.
@@
 
-\section{Nuclear Activity with Interaction Stage}
+\section{Nuclear Activity with Interaction Stage}\label{results:AGN_stage}
 \noindent We now cross match our sample with the two AGN catalogues and methods described in Section \ref{sec:agn-clsf}.
@@
 
-Applying KS- or AD- tests these, however, reveals values close to 1 and therefore it is very likely that these distributions have been drawn from the same parent sample.
+Applying KS- or AD- tests these, however, reveals p-values close to 1 and therefore it is very likely that these distributions have been drawn from the same parent sample.
 However, due to the low counts of AGN and SFGs in our sample, using KS- and AD-tests to verify this is not optimal.
@@
 We define the AGN fraction as the ratio of number of confirmed AGN divided by the number confirmed AGN and SFGs in the sample.
+This is then weighted by the relevant sizes of each subsample and the number of unclassified sources in each.
 Errors on each point are found by bootstrapping.
@@
 We measure the errors on our sample from bootstrapping the underlying low-count population of AGN and SFGs and comparing to the change in fraction measured.
-Thus, while our inital values show a general increase, because of the large error bars, there could be no increase at all with stage to even a slight decline.
-
-However, finding that AGN fraction increases with stage is inline with other works \citep{2011MNRAS.418.2043E, 2023ApJ...942..107S} which often find an increase in AGN fraction with projected separation.
-Stage can also be considered as a proxy for the projected separation of the two systems, where stage 4 will be systems with the smallest projected separation and stage 3 being the largest separation.
-This matches what we find here, with stage 4 systems having the highest fraction of AGN compared to stage 1 systems.
-What is different in our results, however, is the change in AGN fraction from stage 2 to 3.
-While we see a large increase in AGN fraction from stage 1 to 2, this enhancement holds from stage 2 to 3.
-Again, this is not an unusual result and works such as \citet{2011MNRAS.418.2043E} show that the enhancement of nuclear ignition can actually be delayed in galaxy interaction.
-Thus, we only see the final ignition in the later part of the dynamical time than the initial flyby.
+Thus, while our initial values show a general increase, because of the large error bars, there could be no increase at all with stage to even a slight decline.
 
@@
 As expected, we find that with increasing projected separation the number of confirmed AGN and SFGs decreases.
-However, in the AGN distribution, we find two contributing components in it.
+In the AGN distribution, we find two contributing components in it.
 The first is a peak in the projected separation distribution is from 0kpc-25kpc.
@@
 
-Thus, the observed enhancement in AGN across a range of different projected separations if primarily due to different parts of the dynamical time of an interaction.
-The peak in nuclear activity, as expected, is within stage 2 galaxies which are close to pericentre in their interaction.
-However, as we move to higher projected separations and towards stage 3 of the interaction, the number of AGN begins to decrease.
-This implies, following other works, that enhancement occurs early in the interaction, when the systems are at pericentre from each other and with the smaller the pericentre, the more likely it is of nuclear ignition.
-The nuclear ignition from stage 2 can then be switched off again as we move to higher projected separation and stage 3.
-Finally, as the interaction begins to move into coalescence, we find another large increase in the AGN fraction which indicates that AGN activity becomes enhanced.
-Therefore, \textbf{when finding the AGN fraction of interacting systems it is important to consider the stage, and relate this to the projected separation of the system.}
+We find that the AGN fraction generally increases with interaction stage, however, it again remains constant from stage 2 to stage 3.
+This indicates that the mechanism driving AGN ignition in interaction is primarily at the point of the closest approach between the two systems.
+This is further reinforced when the system begins to merge, and we see the AGN fraction increase significantly in our sample.
+When we investigate the AGN number counts with respect to the projected separation of systems, we find that it gradually declines over the projected separation.
+However, we find two peaks; first clearly in stage 2 of the interaction where the galaxies are overlapping and secondly in the early parts of stage 3.
+This could be evidence of a delayed AGN ignition depending on the underlying parameters of the interaction.
+Thus, \textbf{we find that the AGN fraction generally increases with stage, however, the mechanisms responsible for an increase in the fraction primarily occur when the two systems are at pericentre or are actually merging.
+We find evidence of a delay of ignition, as there is an increase in fraction at a early projected separations in stage 3}.
 
-\section{Discussion}
+\section{Discussion}\label{discussion}
 \subsection{Interaction Stage and Projected Separation}
+\noindent Finding evolution with interaction stage is not a new idea in the field.
+Multiple works have found increases in SFE and SFR as a function of projected separation of pairs of galaxies \citep{2000ApJ...530..660B, 2008AJ....135.1877E, 2013MNRAS.433L..59P}.
+Projected separation is often seen as a proxy for the point in the dynamical time of the interaction that is being measured.
+It is likely that, when the galaxies in the pair are closer together, they are closer to coalescence in the dynamical time and can be thought of as a linear progression in the interaction from being close pairs to coalescence.
+However, what this fails to capture is the larger complexity of interaction.
+Without morphological consideration, we are unable to tell whether galaxies at close projected separation are actually about to coalesce or are simply at the closest point of flying by each other.
+
+We find that throughout the different stages of interaction the SFR within the systems is increasing.
+Observations of interacting galaxies at various stages have found increased gas inflows into the nuclear regions of the galaxies which lead to enhancement in SFR there over their outer reaches \citep{2015A&A...579A..45B}.
+This is often confirmed with deep observations of individual systems, which capture snapshots of different parts of the dynamical timescale of the interaction \citep{2022MNRAS.514.2769K}.
+Our study utilises numerous snapshots of the dynamical time of interaction in attempt to build a full picture of the change in SFR.
+We have found here is that this process of increasing SFR and galaxies being driven to starburst begins from the pericentre of interaction.
+Multiple simulation works, which have the ability to model the entire dynamical history, show that this is to be expected \citep{2007A&A...468...61D, 2013MNRAS.430.1901H, 2015MNRAS.452.2984K, 2021MNRAS.503.3113M}.
+Often, these works show an initial dramatic increase in the SFR of interacting systems followed by an exponential decline through the dynamical time before increasing dramatically again at either a second passage or coalescence.
+\citet{2015MNRAS.448.1107M} is a direct example of this SF history through the merger history.
+
+Our results differ here as we do not find an exponential decrease in the SFR as move from stage 2 systems to stage 3 systems.
+As stated previously, observational work does support a continued increase in SFE in galaxies to projected separations of out to 80kpc - well into our defined stage 3 systems \citep[for further examples, see][]{2008MNRAS.385.1903L, 2012MNRAS.426..549S}.
+However, it is important to note that our stage 3 defined classification is a `wide net' that captures many systems that may be very soon after the initial passage in the dynamical timescale.
+The criteria defining stage 2 and stage 3 are simply that the galaxies must be no longer connected or overlapping morphologically with tidal features.
+They must only be distinct and separate galaxies.
+Therefore, our found large enhancement in stage 3 may be from interacting systems which are only just out of the pericentre passage and not enough time has passed for the rapid decline in SFR to begin.
+
+Nonetheless, we still find a disappearance of the red sequence in stage 3 systems which may come as unexpected to when compared to simulations.
+It is important to note, however, that this is not the same as saying that a large proportion of the stage 3 systems are classified as starbursting galaxies.
+While previously mentioned simulations approximate an initial large starburst before rapid decline, we find the interacting galaxy population is pushed being quiescent / sub the star forming main sequence to being on the star forming main sequence.
+Therefore, it may be more likely that the impact of interaction on star formation is not to suddenly cause rapid star formation in the aforementioned starburst before declining, but rather to gradually increase a galaxy's SFR up and into the blue cloud of galaxies.
+This could be supported by the surprising lack of rapidly quenched post-interaction galaxies found in both observations \citep{2017ApJ...845..145W} and simulations \citep{2020MNRAS.493.3716H, 2021MNRAS.504.1888Q}.
+\textbf{Thus, the impact of interaction on star formation is may not be a catastrophic increase in star formation that leads to quenching but, rather, a small increase in galaxies to use whatever gas they have into star formation}.
+% Expand?
+
+This idea can be brought further forward by considering the large increase in starbursting galaxies we find when going from stage 2 / stage 3 to stage 4 galaxies.
+Stage 4 represents, in our sample, galaxies that are undergoing the final coalescence of the two systems involved.
+We find that the point of final coalescence leads to a large increase in the fraction of starbursting galaxies as well as the almost complete disappearance of the quiescent and sub-main sequence fraction of galaxies.
+Thus, from this result we can conclude that during coalescence galaxies undergo a huge starburst and enhancement in star formation which will quickly lead to their quenching.
+This is also supported by works such as \citet{2022MNRAS.517L..92E}, which find that galaxies post-coalescence are 30-60 times more likely than control galaxies to have rapidly shut down star formation.
+
+Thus, we can conclude, that for merging galaxies if gas is present within them, star formation will increase and change our classification of the galaxy.
+We will observe a sudden increase in the star formation rates of these systems followed by a rapid quenching as the gas is used up entirely.
+This is completely at odds when compared to galaxies that move into stage 3 and do not merge.
+These stage 3 systems will then slowly lose their enhancement over a long period of time, and return to star forming at their expected rate, whereas only moving into a stage 4 galaxy will lead to a starburst which may incur rapid quenching.
+
+Such a conclusion would also, therefore, explain the often quite large divide in the literature between whether interaction actually leads to enhancement or not.
+The only part of the interaction which actually causes the enhancement, and is the forking point, is that of stage 2 - where the two galaxies overlap and are at pericentre.
+From this point, if the galaxies then move off to stage 3 and escape, we will see a gradual decline in the SFE with the stage 3 galaxy only minorly increased in its star formation classification.
+Whereas, if the galaxies move into a stage 4 interaction and merge, that is where we see the catastrophic results of a major starburst and the complete using and of all the gas in the systems.
+Thus, leading to a large fraction of quenched post-merger galaxies, but only after the initial coalescence.
 
 \subsection{Interaction Stage and AGN}
+\noindent The evolution of the AGN fraction in interacting galaxies is similar to that of the evolution of star formation.
+It has often been found with projected separation the AGN fraction increases.
+There are multiple observational works that show this \citep{2007MNRAS.375.1017A, 2013MNRAS.435.3627E, 2020ApJ...904..107S} as well as works on cosmological simulations which support these conclusions \citep{2023MNRAS.519.4966B}.
+In simulations, the increased likelihood of nuclear ignition comes from the sudden increase in gas density in the galactic core which naturally leads to increased black hole accretion and ignition.
+Observations of interacting galaxies are often interesting, as they contain examples of duel AGN and individual examples \citep[e.g.][]{2017MNRAS.470L..49E, 2021ApJ...923...36S} or investigate the increase in the AGN fraction in only the merger / post-merger stage \citep{2020A&A...637A..94G}.
 
-\subsection{Comparison to Simulations}
+We find an increasing AGN fraction with both stage and projected separation, before the galaxy merging and coalescence takes place.
+This is supported with other works which specifically look at AGN fraction with projected separation \citep{2011MNRAS.418.2043E, 2023ApJ...942..107S}.
+However, we specifically find that the AGN fraction increases rapidly from stage 1 to stage 2 and stage 3 to stage 4.
+Again, it holds quite constant between stages 2 and 3.
+This shows, again, shows two distinct end stages of interaction which can colour our interpretation of the link between AGN and interaction.
+It appears, from our results, that the AGN fraction is driven up during the points in the dynamical time when interacting galaxies are actually flying past each other and being morphologically disturbed.
+There is evidence that the onset of nuclear ignition from interaction may be delayed \citep{2011MNRAS.418.2043E}, or even flicker \citep{2015MNRAS.451.2517S} after ignition.
+Both of these possibilities are reflected distributions of AGN fraction with stage and projected separation.
+
+Again, it is important to note the rather `wide net' that our stage classification takes.
+There is overlap between our stage 2 and stage 3 classifications at high stage 2 projected separation and low stage 3 projected separations.
+However, these stages naturally lead onto one another.
+Therefore, what see in the bi-modal distribution of AGN fraction with projected separation in Figure \ref{fig:sfg-agn-proj} are two peaks.
+The second of these peaks is at the cross over point of stage 2 to stage 3; the point at which (if the two galaxies have just flown by each other) a delayed AGN ignition coult take place.
+This is also reflected in Figure \ref{fig:agn-stage} where we see a slight increase in AGN fraction in stage 3.
+This is likely from the ignition of nuclear activity taking place over a large period of time with a delay being involved from the initial flyby.
+Other works do also support this interpretation.
+
+We also see a dramatic increase in AGN fraction in stage 4 systems, where coalescence is just beginning or has occurred.
+Multiple works show that this is as expected.
+\citet{2023MNRAS.519.4966B} has used cosmological simulations to show that we expect a large increase in AGN fraction at coalescence, and even for sometime into the post-merger phase.
+This is supported by measured AGN fractions in post-merger galaxies.
+Here, we see that the enhancement actually begins in stage 2, before the coalescence has even begun, but the actual coalescence is what sends it into overdrive.
+This is matches observations mentioned previously of increased gas densities in nuclear regions and cores, and that stage 4 is when this really occurs in earnest,
+
+However, to more fully study this, we would need a larger sample of confirmed AGN and star forming galaxies from existing photometry or catalogues to make more decisive conclusions based on stage.
+In this work, we were limited to a small number of AGN and star forming galaxies across each stage.
+When compared to our paired sample, we do not have the numbers to also divide into stage again.
+Therefore, Figure \ref{fig:sfg-agn-proj} shows the global AGN number count with projected separtion.
+We show that the two peaks are due to different stages of the interaction, however, these are using very low number counts and should be treated carefully.
 
 \section{Conclusions}\label{conclusion}
- - Restate the Results \\
- - What's the next steps of this project?
-    - Hint at what I would do in a Fellowship.
+\noindent In this work, we investigate the evolution of multiple parameters and processes in galaxy interaction with interaction stage.
+We use the \citet{2023ApJ...948...40O} catalogue of interacting galaxies and cross match it with the COSMOS survey to gain ancillary data.
+This gives us a sample of 4,135 interacting galaxies of which 960 have a confirmed secondary from available photometric redshift data.
+We use visual morphology as well as angular separation to split our sample into four distinct stages: (1) close pair, (2) morphologically disturbed and overlapping, (3) morphologically disturbed and distinct, (4) merging.
+Each stage is designed to capture a different part of the dynamical timescale of the interaction.
+We then cross match these samples with existing catalogues of environment and active galactic nuclei for further study.
+
+% Stage and SFR
+We first split our sample of galaxies into their different stages and investigate their evolution with stellar mass and star formation rate.
+We conduct Kolmogorov-Smirnov and Anderson-Darling tests to show the mass distribution of our sample does not change with stage, while the star formation rate changes dramatically.
+This change in star formation rate from stage 1 to 4 is found in the red sequence of galaxies reducing to the point of disappearance.
+This is further confirmed by sub-classifying each sampled stage into starbursting, main sequence and quiescent galaxies.
+We find that as the galaxies move from stage 1 to stage 2 the fraction of starbursting galaxies increases while the quiescent galaxy fraction reduces.
+In stage 4, the starbursting fraction increases dramatically while almost no quiescent galaxies exist in the sample.
+This implies that the mechanisms responsible for enhancement in star formation in interacting galaxies is dominant from stage 1 to stage 2 and in the final coalescence of the system.
+We find that, for all of our galaxies, some enhancement in star formation is observed.
+
+% SFR and projected separation
+To further investigate this change in enhancement, we investigate our sub-sample of galaxy pairs and compare it to a mass and redshift matched control sample.
+We bin our projected separations and measure the ratio between the average interacting SFR and control SFR in each bin.
+We find, across the whole subsample, a general increase in star formation efficiency as we move to smaller projected separation.
+The highest found enhancement is below 10kpc.
+However, when broken down into their consituent stages, we find dramatically different behaviour in the star formation efficiency.
+This is best seen in stage 2 enhancement, which does not seem to change with projected separation, while there is a dramatic decrease in stage 3 enhancement from 2.5 at 10kpc down to 1.2 at 100kpc.
+This shows that just using projected separation as a proxy for stage will leave out crucial information to the underlying causes and mechanisms fueling star formation enhancement.
+To confirm that the effects observed here are not related to biases in the environment, we investigate its relation to our staged sample.
+We find that the environment is consistent between all stages, with no biases existing.
+
+% Stage and AGN
+Finally, we investigate the change in AGN activity across our whole sample.
+We find that, on average, the AGN fraction increases with stage.
+This is also true when related to the projected separation, where we find an almost bi-modal distribution.
+This is from a higher than average AGN fraction existing in the stage 2 and stage 3 samples, likely driven by stochastic inflows of gas during the interaction.
+We also find that the AGN fraction is highest in merging and merged galaxies.
+
+% What does it mean?
+While the results with projected separation are not unexpected, those with the different stages very much are.
+We have shown that one cannot simply use the projected separation of interacting galaxies as a proxy for the stage ongoing.
+We find very different behaviour in the star forming behavior of interacting galaxies based on stage they are at in the dynamical timescale of the interaction.
+We find the beginning of an enhancement in star formation occurs in stage 2, where the two galaxies are moving past each other at pericentre.
+Then, through to stage 3 the enhancement remains although with no further increase.
+There is then another dramatic starburst in stage 4, where the two galaxies actually begin to undergo the merging processes.
+However, the results are not so clear for AGN.
+While we find, definitively, that the AGN fraction increases with stage we are plagued by low counts and selection effects in these results.
+This is due to the limited classifications available of active galactic nuclei in our sample.
+
+% Future Work
+Our work shows the importance of considering morphological stage when considering interaction, and that there is a fine interplay between underlying proesses and the point of the dynamical timescale.
+We require larger samples of correctly staged galaxies to further understand and exploit what these relations are, and how to best investigate when and where star formation and its enhancement occurs.
+This is also particularly true of the relation between active galactic nuclei and the interaction stage, where we are unable to have the sample size to definitively draw conclusions from our results.
 

### 2023-12-11 paper-source/main.tex
Updated .tex source with new figure and integrated to the paper.

@@
 
-Once matched, we remove any sources with unphysical photometric measurements for the stellar mass or star formation rates.
+Once matched, we remove any sources with non-physical photometric measurements for the stellar mass or star formation rates.
 We then further reduce our sample by only keeping sources within the a mass range of $6.5 \leq \log_{10} \text{M}_{*}(\text{M}_{\odot}) \leq 12.5$ and a star formation rate range of $-5 < \log_{10} \text{SFR} (M_{\odot}yr^{-1}) \leq 3.5$.
@@
 A minority of the cutouts we visually assessed were found to have the incorrect primary at the centre.
-In these cases, we record the correct priamry galaxy ID and extract the ancillary data from the COSMOS2020 catalogue.
+In these cases, we record the correct primary galaxy ID and extract the ancillary data from the COSMOS2020 catalogue.
 We then attempt to find the secondary galaxy again for the corrected primary.
@@
 Each stage covers a different part of the dynamical history in an interaction and, in this case, we define it based on the morphology and projected separation between systems.
-WE define four dinstinct stages of interaction:
+We define four distinct stages of interaction:
 
@@
 \noindent Figure \ref{fig:stages} shows the original OR23 source cutouts of an example galaxy in each stage.
-There are degeneracies associated with this staging system, however.
+There are degeneracy's associated with this staging system, however.
 In this context, we define a degeneracy as when the interacting galaxies may be at two or more parts of the dynamical timescale and we have no way to tell without further information on the system.
@@
 Then, dependent on the velocity of the system, the galaxy pair will either move straight into stage 4 of classification and begin to merge or it will move into stage 3.
-This change from stage 2 into stage 3 can then take many branching paths dependent on the elocity in the system.
+This change from stage 2 into stage 3 can then take many branching paths dependent on the velocity in the system.
 If the galaxies have sufficient velocity, stage 3 will be their end state until the tidal features slowly dissipate.
@@
 Figure \ref{fig:illustration} shows the branching paths that the galaxies can take through each stage.
-Note, these are created using the PySPAM restricted numerical simulation (O'Ryan et al.
-in prep.) and are for illustrative purposes only.
+Note, these are created using the Advanced Python Stellar Animation Module restricted numerical simulation \citep[][O'Ryan et al., in prep.]{2016A&C....16...26W} and are for illustrative purposes only.
 
@@
     \centering
-    \includegraphics{}
-    \caption{Sorry, I wan't able to create this figure in the editing phase of this paper! But this will be added as soon as I have a small breather, absolutely love the idea of it.}
+    \includegraphics[width=0.95\textwidth]{figures/stage-evolution.jpg}
+    \caption{The progression through an interaction using our stage definitions.
+In stage 1, we have two systems that are approaching each other but exhibit no tidal features.
+This is before the point of closest approach has occurred.
+This is followed by an intial stage 2: the systems are approximately at their closest approach.
+This stage is often mistaken, in the COSMOS catalogue, for being of only one source.
+Clear tidal features exist with major disturbance in the two disks.
+This is followed by stage 3, where there are two distinct cores with clear tidal features.
+However, after this point, there are two outcomes to the system depending on the galactic velocities.
+If the secondary has the escape velocity, the system will remain a stage 3 interaction until the tidal features dissipate (and no longer are in our sample).
+If they do not have enough energy, the system will return to stage 2 of the encounter and then begin to merge at stage 4.
+Images are from the Advanced Python Stellar Particle Annimation Module interacting galaxy algorithm described in O'Ryan et al.
+(in prep.) and based on the stellar particle animation module algorithm described in \citet{2016A&C....16...26W}.}
     \label{fig:illustration}
@@
 \textit{Top left}: The stellar mass and star formation rate of Stage 1 of our sample.
-Here, the interacting galxies are simply close pairs with little to no morphological disturbance.
+Here, the interacting galaxies are simply close pairs with little to no morphological disturbance.
 There are clearly two populations here: a main, star forming sequence forming the main population and a smaller red sequence.
@@
 The only part of the interaction which actually causes the enhancement, and is the forking point, is that of stage 2 - where the two galaxies overlap and are at pericentre.
-From this point, if the galaxies then move off to stage 3 and escape, we will see a gradual decline in the SFE with the stage 3 galaxy only minorly increased in its star formation classification.
+From this point, if the galaxies then move off to stage 3 and escape, we will see a gradual decline in the SFE with the stage 3 galaxy only having a minor increase in its star formation classification.
 Whereas, if the galaxies move into a stage 4 interaction and merge, that is where we see the catastrophic results of a major starburst and the complete using and of all the gas in the systems.
@@
 When compared to our paired sample, we do not have the numbers to also divide into stage again.
-Therefore, Figure \ref{fig:sfg-agn-proj} shows the global AGN number count with projected separtion.
+Therefore, Figure \ref{fig:sfg-agn-proj} shows the global AGN number count with projected separation.
 We show that the two peaks are due to different stages of the interaction, however, these are using very low number counts and should be treated carefully.

### 2024-01-16 paper-source/main.tex
Major update to error calculation. Updated names of stages to reflect what they are.

@@
 \begin{abstract}
-   Abstract will go here.
+   Galaxy interaction and merging have fundamental impacts on galactic evolution.
+From increases in star formation, to morphology, to activation of nuclear activity, galaxy interaction is thought to play a role.
+However, at what point in the interaction do these effects occur?
+In this work, we break down a large sample of identified interacting galaxies and split them into four distinct stages based on their interaction morphology.
+Each stage captures a different part of the dynamical timescale of interaction; from the systems approaching each other to actually merging.
+We cross match this large sample with the COSMOS field to provide ancillary data and each galaxys' underlying parameters.
+We then investigate the relation between stage, mass, star formation, and nuclear activation.
+Using Kolmogorov-Smirnov tests, we find that the distribution of star formation rates rapidly changes with stage for an equivalent mass distribution.
+We find a rapidly shrinking red sequence with stage, and a large increase in the fraction of starburst galaxies at the point of coalescence.
+We also find that the fraction of active galactic nuclei is static through most of the interaction, until it dramatically increases at coalescence.
+We discuss these results, and compare them with the more prevalent stage diagnostic of projected separation between galaxy pairs.
+We find interesting behaviour that is morphology and stage dependent in our samples star formation rates which is not captured by only using the projected separation.
+We show that morphological stage and, more specifically, the point in time of the underlying dynamical timescale an interaction occupies is as important to consider as its projected separation.
+We conclude this work with discussions on how this could be applied to larger, more complete datasets of interacting galaxies with available ancillary data.
 \end{abstract}
@@
 Often, the stage of an interaction is approximated by measuring different parameters with the projected separation between two systems.
-Early works showed that there was significant star formation enhancement (SFE) in galaxy pairs with small separations \citep{2003MNRAS.346.1189L ,2008AJ....135.1877E, 2022ApJ...940....4S}.
+Early works showed that there was significant star formation enhancement (SFE) in galaxy pairs with small separations \citep{2003MNRAS.346.1189L,2008AJ....135.1877E, 2022ApJ...940....4S}.
 A connection was also found between the projected separation in galaxy pairs and the AGN fraction where, once again, the AGN fraction appears to increase with decreasing projected separation \citep{2009MNRAS.399.2172R, 2011MNRAS.418.2043E, 2017MNRAS.465.2671G, 2021ApJ...909..124S}.
@@
 Figure \ref{fig:agn-frac-time} shows the changing AGN fraction with interaction stage.
-We find that the AGN fraction generally increases with interaction stage.
-There is a large increase from stage 1 to 2, followed by the fraction mostly remaining unchanged until stage 3.
-Then, in stage 4 we measure another large jump in the AGN fraction.
+We find that the AGN fraction generally remains static with stage.
+There is a small decrease increase from stage 1 to 2, followed by the fraction mostly remaining unchanged until stage 3.
+Then, in stage 4 we measure a large jump in the AGN fraction.
 However, before we discuss this result further, we must point out that the large error bars on our measurements and the low number counts of confirmed AGN and SFG make this difficult to interpret.
-We measure the errors on our sample from bootstrapping the underlying low-count population of AGN and SFGs and comparing to the change in fraction measured.
-Thus, while our initial values show a general increase, because of the large error bars, there could be no increase at all with stage to even a slight decline.
+We measure the errors as the standard deviation about the mean in each stage.
+Thus, while our initial values show relatively little change, because of the large error bars, there could be increase with stage to even a further decline.
 
@@
 
-We find that the AGN fraction generally increases with interaction stage, however, it again remains constant from stage 2 to stage 3.
+We find the AGN fraction only increases at the point of coalescence in interaction: stage 4.
 This indicates that the mechanism driving AGN ignition in interaction is primarily at the point of the closest approach between the two systems.
-This is further reinforced when the system begins to merge, and we see the AGN fraction increase significantly in our sample.
 When we investigate the AGN number counts with respect to the projected separation of systems, we find that it gradually declines over the projected separation.
@@
 This could be evidence of a delayed AGN ignition depending on the underlying parameters of the interaction.
-Thus, \textbf{we find that the AGN fraction generally increases with stage, however, the mechanisms responsible for an increase in the fraction primarily occur when the two systems are at pericentre or are actually merging.
+Thus, \textbf{we find that the AGN fraction is generally unchanged with stage, however, the mechanisms responsible for an increase in the fraction primarily occur when the two systems are actually merging.
 We find evidence of a delay of ignition, as there is an increase in fraction at a early projected separations in stage 3}.
@@
 In simulations, the increased likelihood of nuclear ignition comes from the sudden increase in gas density in the galactic core which naturally leads to increased black hole accretion and ignition.
+To satisfy these conditions, actual coalescence of the two systems are required.
 Observations of interacting galaxies are often interesting, as they contain examples of duel AGN and individual examples \citep[e.g.][]{2017MNRAS.470L..49E, 2021ApJ...923...36S} or investigate the increase in the AGN fraction in only the merger / post-merger stage \citep{2020A&A...637A..94G}.
 
-We find an increasing AGN fraction with both stage and projected separation, before the galaxy merging and coalescence takes place.
+We find peaks in the AGN fraction with projected separation, before the galaxy merging and coalescence takes place.
 This is supported with other works which specifically look at AGN fraction with projected separation \citep{2011MNRAS.418.2043E, 2023ApJ...942..107S}.
-However, we specifically find that the AGN fraction increases rapidly from stage 1 to stage 2 and stage 3 to stage 4.
-Again, it holds quite constant between stages 2 and 3.
-This shows, again, shows two distinct end stages of interaction which can colour our interpretation of the link between AGN and interaction.
-It appears, from our results, that the AGN fraction is driven up during the points in the dynamical time when interacting galaxies are actually flying past each other and being morphologically disturbed.
+However, we specifically find that the AGN fraction increases rapidly in stage 4 and holds quite constant between stages 1 to 3.
+This shows, again, shows two distinct effects of interaction which can colour our interpretation of the link between AGN and interaction.
+It appears, from our results, that the AGN fraction is driven up during the points in the dynamical time when the inner parts of the galaxy are majorly disturbed, and not by the simple movement of gas and dust into the core during the two galaxies passing each other.
 There is evidence that the onset of nuclear ignition from interaction may be delayed \citep{2011MNRAS.418.2043E}, or even flicker \citep{2015MNRAS.451.2517S} after ignition.
-Both of these possibilities are reflected distributions of AGN fraction with stage and projected separation.
+Both of these possibilities are reflected distributions of AGN fraction with projected separation.
 
@@
 Therefore, what see in the bi-modal distribution of AGN fraction with projected separation in Figure \ref{fig:sfg-agn-proj} are two peaks.
-The second of these peaks is at the cross over point of stage 2 to stage 3; the point at which (if the two galaxies have just flown by each other) a delayed AGN ignition coult take place.
+The second of these peaks is at the cross over point of stage 2 to stage 3; the point at which (if the two galaxies have just flown by each other) a delayed AGN ignition could take place.
 This is also reflected in Figure \ref{fig:agn-stage} where we see a slight increase in AGN fraction in stage 3.
 This is likely from the ignition of nuclear activity taking place over a large period of time with a delay being involved from the initial flyby.
-Other works do also support this interpretation.
 
@@
 The highest found enhancement is below 10kpc.
-However, when broken down into their consituent stages, we find dramatically different behaviour in the star formation efficiency.
+However, when broken down into their constituent stages, we find dramatically different behaviour in the star formation efficiency.
 This is best seen in stage 2 enhancement, which does not seem to change with projected separation, while there is a dramatic decrease in stage 3 enhancement from 2.5 at 10kpc down to 1.2 at 100kpc.
@@
 Finally, we investigate the change in AGN activity across our whole sample.
-We find that, on average, the AGN fraction increases with stage.
-This is also true when related to the projected separation, where we find an almost bi-modal distribution.
-This is from a higher than average AGN fraction existing in the stage 2 and stage 3 samples, likely driven by stochastic inflows of gas during the interaction.
+We find that, on average, the AGN fraction remains constant with stage until the point of coalescence.
+However, when looking at project separation, we find an almost bi-modal distribution.
+This could be evidence for a delayed ignition in the AGN present in those systems undergoing an interaction.
+However, it is difficult to draw this conclusion definitively due to small number counts.
 We also find that the AGN fraction is highest in merging and merged galaxies.
@@
 % What does it mean?
-While the results with projected separation are not unexpected, those with the different stages very much are.
-We have shown that one cannot simply use the projected separation of interacting galaxies as a proxy for the stage ongoing.
-We find very different behaviour in the star forming behavior of interacting galaxies based on stage they are at in the dynamical timescale of the interaction.
+While the results with projected separation are not unexpected, those with the different stages are.
+We have shown that one cannot simply use the projected separation of interacting galaxies as a proxy for the stage of the interaction.
+We find very different behaviour in the star forming behavior of interacting galaxies based on stage which are at in the dynamical timescale of the interaction.
 We find the beginning of an enhancement in star formation occurs in stage 2, where the two galaxies are moving past each other at pericentre.
-Then, through to stage 3 the enhancement remains although with no further increase.
+Then, through to stage 3, the enhancement remains although with no further increase.
 There is then another dramatic starburst in stage 4, where the two galaxies actually begin to undergo the merging processes.
-However, the results are not so clear for AGN.
-While we find, definitively, that the AGN fraction increases with stage we are plagued by low counts and selection effects in these results.
-This is due to the limited classifications available of active galactic nuclei in our sample.
 
 % Future Work
-Our work shows the importance of considering morphological stage when considering interaction, and that there is a fine interplay between underlying proesses and the point of the dynamical timescale.
+Our work shows the importance of considering morphological stage when considering interaction, and that there is a fine interplay between underlying processes and dynamical timescale of an interaction.
 We require larger samples of correctly staged galaxies to further understand and exploit what these relations are, and how to best investigate when and where star formation and its enhancement occurs.

### 2024-01-22 paper-source/main.tex
Updated code based on Brookes comments. Preparing to update to send to collaborators.

@@
 However, at what point in the interaction do these effects occur?
-In this work, we break down a large sample of identified interacting galaxies and split them into four distinct stages based on their interaction morphology.
-Each stage captures a different part of the dynamical timescale of interaction; from the systems approaching each other to actually merging.
-We cross match this large sample with the COSMOS field to provide ancillary data and each galaxys' underlying parameters.
-We then investigate the relation between stage, mass, star formation, and nuclear activation.
-Using Kolmogorov-Smirnov tests, we find that the distribution of star formation rates rapidly changes with stage for an equivalent mass distribution.
-We find a rapidly shrinking red sequence with stage, and a large increase in the fraction of starburst galaxies at the point of coalescence.
-We also find that the fraction of active galactic nuclei is static through most of the interaction, until it dramatically increases at coalescence.
+In this work, we divide a large sample of interacting galaxies in the COSMOS field into four distinct stages based on their interaction morphology.
+Each stage captures a different part of the dynamical timescale of interaction.
+We then probe the relation between stage, mass, star formation, and nuclear activity.
+We find that the distribution of star formation rates rapidly changes with stage for an equivalent mass distribution.
+We find a shrinking red sequence with stage, and an increase in the fraction of starburst galaxies from 0.1 as close pairs to 0.38 at the point of coalescence.
+We also find that the fraction of active galactic nuclei is static through most of the interaction, until it increases at coalescence.
 We discuss these results, and compare them with the more prevalent stage diagnostic of projected separation between galaxy pairs.
-We find interesting behaviour that is morphology and stage dependent in our samples star formation rates which is not captured by only using the projected separation.
-We show that morphological stage and, more specifically, the point in time of the underlying dynamical timescale an interaction occupies is as important to consider as its projected separation.
-We conclude this work with discussions on how this could be applied to larger, more complete datasets of interacting galaxies with available ancillary data.
+We find morphology and stage dependence in the rate of star formation which is not captured by using the projected separation.
+We show that the point in time of the underlying dynamical timescale an interaction occupies is as important to consider as its projected separation.
+
 \end{abstract}
@@
 \section{Introduction}\label{introduction}
-\noindent Galaxy interaction and merging is of fundamental importance to our current theories of galaxy formation and evolution.
-Our current cosmological theory, $\Lambda$CDM dictates that structure is expected to form and assemble hierarchically \citep{1978MNRAS.183..341W, 2001MNRAS.328..726S, 2013MNRAS.436.1765M}.
-Thus, understanding the underlying processes that occur in galaxy interaction and merging are paramount to understanding cosmological theories.
-It is well known that many underlying processes are triggered or enhanced due to galaxy interaction.
-The clearest result of interaction is the disruption of galactic morphology, the acceleration of disks to spheroidal systems and the formation of tidal features \citep{1972ApJ...178..623T, 1977ApJ...212..616T, 2005MNRAS.357..753G, 2009MNRAS.397..802H}, increases in star formation rates when compared to the general galaxy population \citep{1991ApJ...370L..65B, 2006ApJ...652...56B, 2014MNRAS.437.2137S, 2015ApJ...807L..16K} and, potentially, their rapid quenching \citep{2013MNRAS.430.1901H, 2023RAA....23i5026D}.
-There is also evidence to suggest that interaction plays a role in the ignition of active galactic nuclei (AGN) \citep{2011MNRAS.418.2043E, 2015ApJ...806..219C, 2023MNRAS.523.4164H}.
-Therefore, with interaction having such an affect on the galaxies we see - over a long time period - understanding galaxy interaction is fundamental to understanding galaxy evolution.
-
-To fully map out the effect of galaxy interaction, we must understand its impact on galaxies through the entire merger history and dynamical timescale of the interaction.
-As each observation only provide snapshots of different parts of the dynamical timescale across different merger histories, it is imperative we have large samples to capture the full history.
-The most obvious place to start with mapping the full dynamical histories is with simulations.
-Previous works find sudden increases in star formation occurs early in the dynamical timescale of the interaction \citep{2008MNRAS.384..386C, 2019MNRAS.490.2139R}, however, confirming this definitive link observationally remains elusive \citep{2023ApJ...958...96R}.
-The same studies could also be done for nuclear activation as well as quenching of interacting systems \citep{2011MNRAS.418.2043E, 2018PASJ...70S..37G, 2023ApJ...942..107S}.
-
-Achieving such study in the dynamical history of an interaction with observations is more difficult.
-While we cannot directly measure the full dynamical timescale for individual systems, we can create large samples of interacting galaxies which are representative over the dynamical history.
-The first interacting galaxy sample (the \citet{1966ApJS...14....1A} catalogue) contained only 318 systems, while more recent samples have been created either by machine learning classification \citep{2019A&A...626A..49P, 2023A&A...669A.141S}, visual classification by citizen scientists \citep{2010MNRAS.401.1043D} or by photometric parameterisation \citep{2004AJ....128..163L, 2023MNRAS.522....1N}.
-With larger samples, we can approximate different parts of the dynamical time them into their constituent stages.
-However, each sample has always been plagued by contamination and a loss of statistical significance when broken down into stages.
-It is notoriously difficult, from morphology alone, to select interacting or merging galaxies.
-
-Often, the stage of an interaction is approximated by measuring different parameters with the projected separation between two systems.
-Early works showed that there was significant star formation enhancement (SFE) in galaxy pairs with small separations \citep{2003MNRAS.346.1189L,2008AJ....135.1877E, 2022ApJ...940....4S}.
+\noindent To fully map out the effect of galaxy interaction, we must understand its impact through various merger histories and across the full dynamical timescale of the interaction.
+The dynamical timescale is the full time of the interaction, from the two galaxies approaching each other to flying by and escaping or merging.
+We cannot observe a full, continuous interaction and have to rely on many observations to provide snapshots of the dynamical timescale we can piece together.
+This, however, makes it difficult to conclusively find link the dynamical timescale to physical processes.
+Often, observational samples are too small to be fully representative or deep studies of individual systems are required to identify the dynamical timescale \citep{2000ApJ...530..660B, 2012A&A...539A..45L, 2014A&A...567A.132W}.
+We gain insights from works focused on simulations, where the dynamical timescale can be directly recorded.
+They find sudden increases in star formation occurs at the mid-point of the dynamical timescale, as the two systems flyby \citep{2008MNRAS.384..386C, 2019MNRAS.490.2139R, 2021MNRAS.503.3113M}.
+However, confirming this observationally remains elusive \citep{2023ApJ...958...96R}.
+Observational confirmation is also difficult with nuclear activation and quenching of interacting systems \citep{2011MNRAS.418.2043E, 2018PASJ...70S..37G, 2023ApJ...942..107S}.
+
+While cannot directly measure the full dynamical timescale for individual systems, we can create large samples of interacting galaxies contain systems spanning the full dynamical history.
+Attempts to create such a sample have been either by machine learning classification \citep{2019A&A...626A..49P, 2023A&A...669A.141S}, visual classification by citizen scientists \citep{2010MNRAS.401.1043D} or by photometric parameterisation \citep{2004AJ....128..163L, 2023MNRAS.522....1N}.
+However, as stated previously, each sample has always been plagued by contamination and a loss of statistical significance when broken down into stages.
+
+An alternate approach to directly measuring the dynamical timescale of an interaction has been to infer it from the projected separation between the two systems.
+Early works showed that there was significant star formation enhancement (SFE) in galaxy pairs with small separations \citep{2003MNRAS.346.1189L,2008MNRAS.385.1903L, 2008AJ....135.1877E, 2022ApJ...940....4S}.
 A connection was also found between the projected separation in galaxy pairs and the AGN fraction where, once again, the AGN fraction appears to increase with decreasing projected separation \citep{2009MNRAS.399.2172R, 2011MNRAS.418.2043E, 2017MNRAS.465.2671G, 2021ApJ...909..124S}.
-However, using projected separation as a proxy for the stage in dynamical time of an interacting history overlooks which part of the dynamical history the interaction is at.
-For instance if a galaxy pair is found to have small projected separation, without visually confirming the morphology, it is difficult to ascertain if the galaxies are just approaching each other or just passed each other.
-The differences between these being paramount to understanding the effects of interaction on the galaxies involved.
-
-In this work, we split a large sample of interacting galaxies into four specific stages based from their morphology.
+However, using projected separation as a proxy for the stage in dynamical time of an interacting history overlooks which part of the dynamical history the interaction is.
+For instance, if a galaxy pair is found to have small projected separation, without visually confirming the morphology, it is difficult to ascertain if the galaxies are just approaching each other or have just passed each other.
+Extended morphological tracers can help break this degeneracy, which is critical to our understanding of the effects of interaction.
+
+In this Chapter, we split our large sample of interacting galaxies found in Chapter \ref{chapter2} into four specific stages based on their morphology.
 Each stage is designed to capture different parts of the dynamical time of an interaction.
-Each interacting or disturbed galaxy is visually classified into its stage, which ranges from galaxies being close pairs, to overlapping and disturbed, to disturbed and distinct to finally coalescing.
+The stages range from galaxies being close pairs, to overlapping and disturbed, to disturbed and distinct to finally coalescing.
 This follows the classification methods of developing algorithms for staging of interaction\citep{2019MNRAS.490.5390B,2022ApJ...937...97C}.
 
-We elect to use the newly created interacting galaxy catalogue created by \citet{2023ApJ...948...40O} (hereafter, OR23) which found a sample of 21,926 interacting galaxy systems.
-This is the largest visually classified interacting galaxy catalogue to date.
-This sample was created using the new ESA Datalabs\footnote{ESA Datalabs: link} platform and the convolutional neural network machine \texttt{Zoobot} \citep{2022MNRAS.509.3966W, 2023JOSS....8.5312W}.
-This classified all sources in the Hubble Source Catalogue \citep{2016AJ....151..134W} from the Hubble Space Telescope (HST) archives into interacting or non-interacting.
-Once this was done, a rigorous process of de-duplication, contamination removal and visual inspection was conducted.
-
-We cross match this catalogue with the Cosmic Evolutionary Survey (COSMOS) survey\footnote{DOI: \href{https://www.ipac.caltech.edu/doi/irsa/10.26131/IRSA178}{10.26131/IRSA178}}.
-This provides us with ancillary data for a subset of the OR23 catalogue.
-This ancillary data contains many galactic parameters of interest and we explore how they evolve with our defined stages of interaction.
+We focus here on the subset of our sample in the Cosmic Evolutionary Survey (COSMOS) survey\footnote{DOI: \href{https://www.ipac.caltech.edu/doi/irsa/10.26131/IRSA178}{10.26131/IRSA178}}.
+This provides us with ancillary data which contains many galactic parameters of interest and we explore how they evolve with our defined stages of interaction.
 We primarily focus on the evolution of the stellar masses, star formation rates and AGN classification from various COSMOS catalogues.
-We utilise the photometric redshifts available from COSMOS to confirm a set of interacting galaxies and close pairs to draw on trends with projected separation.
-
-This paper is laid out as follows in Section \ref{data} we explain the OR23 and COSMOS catalogues, and describe the process of catalogue matching especially focused on accurate de-duplication and cross-matching between the different catalogues.
-Section \ref{method} describes the methods by which we split the interacting systems into stages, and how we identify the secondary galaxies in each pair.
+We use the photometric redshifts available from COSMOS to confirm a set of interacting galaxies and close pairs to draw on trends with projected separation.
+
+This Chapter is laid out as follows in Chapter \ref{data} we briefly summarise the COSMOS catalogue, and describe the process of catalogue matching especially focused on accurate de-duplication and cross-matching.
+Chapter \ref{method} describes the methods by which we split the interacting systems into stages, and how we identify the secondary galaxies in each pair.
 In Sections \ref{results:SF_stage} and \ref{results:AGN_stage} we show our results of star formation and active galactic nuclei evolution with interaction stage and present an initial discussion.
-These are followed in Section \ref{discussion} where we compare to previous works and put our results in the context of the field.
-Finally, Section \ref{conclusion} we make concluding remarks and discuss future work to better our constraints.
-
-Where necessary, we use a Flat $\Lambda$CDM cosmology with $H_0$ = $70$\,km/s/Mpc and $\Omega_M = 0.3$.
-Hereafter in this paper, when referring to an interacting galaxy we are referring to a galaxy which has undergone one or multiple flybys by a secondary galaxy and caused tidal disturbance.
-A merging galaxy is the final state of these flybys, where two or more systems have or are about to coalesce to form a morphologically irregular system.
-
-\section{DATA: Catalogue Matching \& Secondary Identification} \label{data}
-\subsection{The O'Ryan+23 Catalogue}
-\noindent The interacting galaxy catalogue we draw from is the OR23 catalogue of interacting galaxies.
-These systems are classified based on their visual morphology and, while the full process of its creation are detailed there, we will briefly describe it here.
-The morphological classifications were made by a convolutional neural network (CNN) - \texttt{Zoobot} - which searched all final product data in the \textit{Hubble} Legacy Archive.
-While a CNN primarily classifies images by extracting features from them \texttt{Zoobot} differs by extracting features from an image and reducing them to generalised representations.
-By learning the generalise representation of different galaxy morphologies, \texttt{Zoobot} is incredibly flexible and easy to transfer learn on different tasks and datasets.
-This is further reinforced by training it on citizen scientist responses to the Galaxy Zoo: DECaLS \citep{2022MNRAS.509.3966W} and using it to make classifications on multiple morphology questions at once.
-In OR23, using a small dataset of citizen science-classified interacting galaxies from Galaxy Zoo \citep{2008MNRAS.389.1179L} \texttt{Zoobot} was finetuned to \textit{Hubble} data.
-
-Cutouts of each source were created as single-band \textit{F814W} images at 150 $\times$ 150 pixels across.
-Source coordinates were found in the \textit{Hubble} Source Catalogue \citep{2016AJ....151..134W}.
-This corresponded to just over 92 million cutouts created and classified.
-Due to well known issues of classifying interacting galaxies by morphology alone (such as close pair contamination) an extremely conservative prediction score from \textit{Zoobot} was required to make a positive classification.
-This resulted in a very pure, but highly incomplete catalogue of 21,926 interacting galaxy systems.
-This is the largest catalogue of interacting galaxies directly found to date.
-
-The OR23 catalogue only provided the coordinates and \textit{Hubble} Source catalogue ID for each source.
-Therefore, we must either calculate our own ancillary data or cross match with existing catalogues containing it.
-We elect to cross match the OR23 catalogue with the numerous catalogues of the COSMOS survey.
-The overall survey has numerous sub-catalogues ranging from calculations of galactic physical parameters to predictions on AGN classifications.
-
+These are followed in Chapter \ref{discussion} where we compare to previous works and put our results in the context of the field.
+Finally, in Chapter \ref{conclusion} we make concluding remarks and discuss future work to better our constraints.
+
+\section{Data: Catalogue Matching \& Secondary Identification} \label{data}
 \subsection{The COSMOS2020 Catalogue}
@@
 We elect to specifically use the COSMOS2020 catalogue \citep{2022ApJS..258...11W}.
-This catalogue has a wealth of ancillary information for just over 1.7 million sources in a 2 square degree area of the sky.
-Each source found in this area has been analysed with well known astronomical software (for our purposes, primarily  LePhare \citep{1999MNRAS.310..540A, 2006A&A...457..841I}, EAzY \citep{2008ApJ...686.1503B} and FAST \citep{2017MNRAS.465.3390A}).
-These provide estimates of the physical parameters of each source in the COSMOS2020 catalogue based on its measured broadband photometry.
-For our purposes, the most important parameters these calculate are the stellar masses and the estimated star formation rates of each source.
-We opt to simply use one of these two measurements in our analysis.
-For the stellar mass we use the LePhare measurement and for the star formation rates we use the EAzY/FAST measurements.
+This catalogue has a wealth of ancillary information approximately 1.7 million sources in a 2 square degree area of the sky.
+Each source has been analysed with well known astronomical software (for our purposes, primarily \texttt{\texttt{LePhare}} \citep{1999MNRAS.310..540A, 2006A&A...457..841I}, \texttt{\texttt{EAzY}} \citep{2008ApJ...686.1503B} and \texttt{\texttt{FAST}} \citep{2017MNRAS.465.3390A}).
+These provide estimates of the physical parameters of each source based on its measured broadband photometry.
+For our purposes, the parameters of interest are the stellar masses and the estimated star formation rates of each source.
+For the stellar mass we use the best fit \texttt{LePhare} measurement and for the star formation rates we use the best fit \texttt{EAzY}/\texttt{FAST} measurements.
 We compare the output masses and SFRs for our sources in Figure \ref{fig:difference-measures}.
 As shown, there can be wide scatter and disagreement between the two algorithms.
-We, therefore, elect to only use one software for each parameter and not to match the stellar masses and SFRs between them.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.45\textwidth]{figures/mass-sfr-scatter.pdf}
-    \caption{Comparison of the measures of stellar mass and SFR using either LePhare or EAzY/FAST photometric codes to calculate them.
+We tested different combinations of \texttt{EAzY} and \texttt{LePhare} stellar masses and SFRs to find which would be best to use in this work.
+We found that using the same algorithm in both parameters revealed the degeneracies of using discrete templates to fit the broad band photometry in the underlying parameter space.
+Therefore, we elect to inter-mix the algorithms and use the best fit \texttt{LePhare} stellar mass and best fit \texttt{EAzY} SFR measurement.
+
+\begin{figure}
+\centering
+\includegraphics[width=\columnwidth]{figures/mass-sfr-scatter.pdf}
+\caption[Comparison of the measures of stellar mass and SFR using either \texttt{LePhare} or \texttt{EAzY}/\texttt{FAST} photometric codes to calculate them.]{Comparison of the measures of stellar mass and SFR using either \texttt{LePhare} or \texttt{EAzY}/\texttt{FAST} photometric codes to calculate them.
 If the algorithms agreed perfectly, the sources would lie on the blue 1:1 line.
 \textit{Left}: The scatter in the stellar masses between softwares.
-As shown, EAzY often seems to find larger stellar masses when compared to LePhare.
-\textit{Right}: Scatter in SFRs when measured with LePhare or EAzY.
-There is a large difference between the measures of LePhare and EAzY here, and therefore we opt to only use EAzY measures of the SFR through this work.}
+As shown, \texttt{EAzY} often seems to find larger stellar masses when compared to \texttt{LePhare}.
+\textit{Right}: Scatter in SFRs when measured with \texttt{LePhare} or \texttt{EAzY}.}
 \label{fig:difference-measures}
@@
 
-We cross match between the OR23 catalogue with the COSMOS2020 catalogue by matching coordinates between them.
-We search the COSMOS2020 catalogue for any sources within 10" of the OR23 coordinates and make a list of any COSMOS2020 sources.
-If more than one COSMOS2020 source is found within this radius we take the source with the smallest angular separation from the OR23 coordinates as the correct source.
-Once we have identified one COSMSO2020 source for every OR23 ID, we de-duplicate based on COSMOS2020 ID and redo the coordinate matching process with any duplicate matches.
-If no further COSMOS2020 sources were within 10" of the OR23 source, then we the OR23 source not in the COSMOS2020 catalogue.
-We find 3,786 of the OR23 sources exist in the COSMOS2020 catalogue.
+Our sample of interacting galaxies has been de-duplicated, but the COSMOS2020 catalogue is not specifically a de-duplicated merger catalogue.
+We cross match between our sample and the COSMOS2020 catalogues using a position search within $10^{\prime\prime}$ of our sample coordinates.
+Once we have identified the nearest COSMOS2020 source for each interacting galaxy ID, we de-duplicate based on COSMOS2020 ID and redo the coordinate matching process with any duplicate matches.
+If no further COSMOS2020 sources were within 10" of the source, then we classify the source as not in the COSMOS2020 catalogue.
+We find 3,786 of the our sources exist in the COSMOS2020 catalogue.
 
 Once matched, we remove any sources with non-physical photometric measurements for the stellar mass or star formation rates.
-We then further reduce our sample by only keeping sources within the a mass range of $6.5 \leq \log_{10} \text{M}_{*}(\text{M}_{\odot}) \leq 12.5$ and a star formation rate range of $-5 < \log_{10} \text{SFR} (M_{\odot}yr^{-1}) \leq 3.5$.
-To also nullify the effect of surface brightness dimming that may occur when attempting to classify tidal features of interacting galaxies, we institute a redshift cut of $z \leq 1.2$.
-This also makes our sample match the catalogue that will be later used to investigate the incidence of our sample of interacting galaxies with environment (detailed in Section \ref{data:environ}).
+We then further reduce our sample by only keeping sources within a mass range of $6.5 \leq \log_{10} \text{M}_{*}(\text{M}_{\odot}) \leq 12.5$ and a star formation rate range of $-5 < \log_{10} \text{SFR} (\text{M}_{\odot}\text{yr}^{-1}) \leq 3.5$.
+We also opt to institute a redshift cut of $z \leq 1.2$.
+Beyond this redshift, we find that identification of tidal features becomes difficult due to surface brightness dimming and we risk mis-identifying the stages of the interacting galaxies.
+This also matches the redshift cut applied to the environment catalogue we cross match with in Chapter \ref{data:environ}.
 Applying these cuts reduces our sample size to 3,689 interacting galaxies.
@@
 \subsection{Secondary Identification}\label{sec:sec-ident}
-\noindent As the OR23 catalogue only contains source coordinates and IDs, we must also manually identify the secondaries of many of our interacting systems.
+\noindent As the catalogue described in Chapter \ref{chapter2} only contains source coordinates and IDs, we must also manually identify the secondaries of many of our interacting systems.
 To find the secondaries, we apply three steps.
-First, a cutout surrounding each OR23 source was created.
+First, a cutout surrounding each source was created.
 These cutouts were from the COSMOS cutout service, selecting HST-ACS tiles in the $F814W$ filter.
 Each cutout had a 30" radius (corresponding to 1001 $\times$ 1001 pixels).
-The original OR23 cutout was also displayed next to the enlarged cutout.
+The original cutout from Chapter \ref{chapter2} was also displayed next to the enlarged cutout.
 We annotate each cutout with each sources COSMOS2020 ID and measured photometric redshift and error.
-By annotating each cutout with the sources photometric redshift and ID, we could visually assessed each cutout and give one of four following classifications to each: system disturbed but secondary could not be identified; secondary could be identified; cannot confirm galaxy is interacting; null redshift; incorrect primary assigned.
-
-To classify a secondary galaxy for our primary one, it had to be within the cutout we were visually assessing and within the recorded error of the primary photometric redshift.
+By annotating each cutout with the sources photometric redshift and ID, we visually assessed each cutout and gave one of the four following classifications to each: system disturbed but secondary could not be identified; secondary could be identified; cannot confirm galaxy is interacting; null redshift (0 or NaN); incorrect primary assigned.
+
+To associate a secondary galaxy for each primary, the galaxy had to be within the cutout we were visually assessing and within the recorded error of the primary photometric redshift.
 Using photometric redshift cutoffs in this way is often done when calculating environment parameters \citep[e.g][]{2006MNRAS.373..469B} or defining interacting galaxies by close pairs \citep[e.g][]{2022ApJ...940....4S}.
-A null redshift is defined as one outwith our redshift limits or NaN.
+A null redshift is defined as outwith our redshift limits, 0 or NaN.
 A minority of the cutouts we visually assessed were found to have the incorrect primary at the centre.
 In these cases, we record the correct primary galaxy ID and extract the ancillary data from the COSMOS2020 catalogue.
-We then attempt to find the secondary galaxy again for the corrected primary.
+We then attempted to find the secondary galaxy again for the corrected primary.
 
@@
 \includegraphics[width=\textwidth]{figures/cutouts_ex.pdf}
-    \caption{An example of each visual classification made on the cross matched sample.
-From left to right these are the secondary could not be identified, the primary had a clear secondary, the primary could not be reliably classified as an interacting galaxy, the redshift was null and the incorrect primary was identified in OR+23.
+\caption[An example of each visual classification made on the cross matched sample.]{An example of each visual classification made on the cross matched sample.
+These are: (A) where the secondary could not be identified, (B) the primary had a clear secondary, (C) the primary could not be reliably classified as an interacting galaxy, (D) the redshift was null and (E) the incorrect primary was identified.
 Based on these classifications, we either add the secondary galaxies to the sample or we remove the contamination from it.
@@
 While initially surprising that the majority of our systems could not have a secondary identified, we found that it was mostly due to limitations in the COSMOS catalogue or the way in which we conduct our secondary identification.
-Each potential secondary must have a COSMOS ID associated with it, however, when two systems were very close together and small enough they would be identified under a single COSMOS ID despite being two separate systems.
+Each potential secondary must have a COSMOS ID associated with it, however, when two systems are very close together and small enough they were identified under a single COSMOS ID despite being two separate systems.
 The same also occurred when two systems were merging or interacting.
 The tidal features connecting the systems or coalescing systems would only be identified under one ID in the catalogue.
-Figure \ref{fig:secondary_selection} shows an example of two systems being close enough together that they have been identified under a single COSMOS2020 entry.
+Figure \ref{fig:secondary_selection} panel C) shows an example of two systems being close enough together that they have been identified under a single COSMOS2020 entry.
 Figure \ref{fig:secondaries_found} shows this disparity with the different types of interaction we observe.
@@
 \centering
-    \includegraphics[width=0.45\textwidth]{figures/visualisation_classification.pdf}
-    \caption{Where a secondary could be identified at different stages in the interaction.
+\includegraphics[width=\columnwidth]{figures/visualisation_classification.pdf}
+\caption[Where a secondary could be identified at different stages in the interaction.]{Where a secondary could be identified at different stages in the interaction.
 The reasoning for such disparity in secondaries identified is due to the relative distance each the secondary would be from the primary at each stage.
@@
 The same was true for those interacting systems approaching pericentre or merging.
-When the secondary was near apocentre, often it would be outwith the cutout we were using for visual classification.}
+When the secondary was near apocentre, often it would be outside the cutout we were using for visual classification.}
 \label{fig:secondaries_found}
@@
 
-Those galaxies which were found to be contamination (i.e., could not be reliably classified as interacting or having a null redshift) were removed from our sample.
-Galaxies that could not be reliably classified as interacting as they showed little tidal distortion or had no neighbouring systems at a matching redshift were also removed.
-These systems were often overlapping but at different redshifts, or were systems with irregular morphologies of spiral arms or many clumpy galaxies.
-There was also many systems that were at high redshift ($z \geq 1$) where the resolution of the cutouts meant that features could not be discerned visually.
-
-Our final classification type was that the incorrect galaxy had been identified as the priamry galaxy.
+Those galaxies which were found to be contamination (i.e., could not be reliably classified as interacting as they showed little tidal distortion or had no neighbouring systems at a matching redshift or having a redshift of 0) were removed from our sample.
+Galaxies that could not be reliably classified as interacting were also removed.
+These systems were often overlapping but at different redshifts, or were systems with irregular morphologies of spiral arms or a clumps were present.
+There was also many systems that were at high redshift ($z > 1$) where the resolution of the cutouts meant that features could not be discerned visually.
+
+Our final classification type was that the incorrect galaxy had been identified as the primary galaxy.
 This was the case for 149 systems.
-These were systems where the interacting galaxies were clearly in the cutout but some tidal debris or some nearby system had been cross matched from COSMOS.
+These were systems where the interacting galaxies were clearly in the cutout but some tidal debris or some nearby system had been matched from COSMOS.
 We reassign these systems to the correct COSMOS IDs and then take them through the secondary identification process.
 
-By the end of this pipeline, we find a sample size of 3,829 interacting galaxies.
+By the end of this selection method, we find a sample size of 3,829 interacting galaxies.
 We conduct a de-duplication based on the COSMOS2020 ID, which reduces the sample back down to 3,547 interacting galaxies.
-This shows that many of the secondaries we had identified for the different systems were already found in the OR23 catalogue.
 The remaining systems are each visually confirmed interacting and disturbed galaxies based on their morphology and photometric redshift as measured in the COSMOS2020 catalogue.
 
-For each galaxy in our sample, we find and define a mass- and redshift-matched control galaxy to investigate differences in their galactic parameters.
+For each galaxy in our sample, we define a mass- and redshift-matched control galaxy to investigate differences in their galactic parameters.
 We find these control galaxies from the COSMOS2020 catalogue.
-All galaxies within 0.01 dex of our sub-samples' stellar mass are selected from the catalogue, and within a $\pm$0.01 redshift slice.
+All galaxies within 0.01 dex of our samples stellar mass are selected from the catalogue, and within a $\pm0.01$ redshift slice.
 We then define the control galaxy as the system furthest from our interacting galaxy.
@@
 \centering
-    \includegraphics[width=0.45\textwidth]{figures/mass-matching-pairs.pdf}
-    \caption{The mass distribution of the paired interacting galaxy sample and the control sample.
-Both primary and secondary galaxies are within this distribution.
-From our sample of 4,181 interacting galaxies morphologically identified, 834 are confirmed galaxy pairs.
-This means that the secondary in the interacting galaxy system has been identified from morphology and photometric redshifts.}
+\includegraphics[width=\columnwidth]{figures/mass-matching-pairs.pdf}
+\caption[The mass distribution of the paired interacting galaxy sample and the control sample.]{The mass distribution of the paired interacting galaxy sample and the control sample.
+Both primary and secondary galaxies are within this distribution.}
 \label{fig:matched-distributions}
@@
 \subsection{Finding Additional Systems}
-\noindent As a result of using visual classification to find the secondary galaxy in each interaction, we were able to also confirm other interacting systems which had not been found in the OR23 catalogue.
-Primarily, these extra interacting galaxies are from systems which had more than one galaxy involved in the interaction.
-Our pipeline was built to only find a primary and secondary galaxy and, therefore, we add these extra systems through another pipeline.
-Other interacting galaxies that were added were low redshift systems which would have appeared very large in the small OR23 cutout.
+\noindent As a result of using visual classification to find the secondary galaxy in each interaction, we were able to also confirm other interacting systems which had not been found in our catalogue.
+Primarily, these extra interacting galaxies are from systems which had more than two galaxies involved in the interaction.
+Our selection process was built to only find a primary and secondary galaxy and, therefore, we add these extra systems into our sample manually.
+Other interacting galaxies that were added were low redshift systems which would have appeared to completely fill the cutout of the classification process in Chapter \ref{chapter2}.
 By looking at the larger COSMOS2020 cutouts, we are able to recover these galaxies and add them to this sample.
@@
 Upon conducting a de-duplication of these with the sample already found, this was reduced to 634 interacting systems.
-This gives us a total sample size of 4,181 which we use through the rest of this work.
-
-\subsection{Redshift Effects on Visual Classification}
-\noindent There are two limits when using visual morphology to find interacting galaxies.
-The first is the limitation of being able to characterise tidal features with increasing redshift.
-As the redshift increases, surface brightness dimming of the systems may lead to a lack of visual confirmation in the tidal features of different objects.
-Thus, if we are heavily affected by this in our redshift range ($0.0 \leq z \leq 1.2$), we would see distinct signs of it in our selection function of our mergers.
-For instance, if all of our stage 4 classifications were actually high redshift and high mass stage 3 galaxies, we would observe this in our selection function.
-Therefore, Figure \ref{fig:redshift_selection} shows our the distribution of stellar mass across our redshift range for each defined stage in our interaction.
-As shown, the distribution of masses across redshift that we find in our sample is reasonably consistent with each other.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.45\textwidth]{figures/stage-selection.pdf}
-    \caption{Redshift vs Mass distribution for each stage of interaction we have defined.
+This gives us a total flux-limited sample size of 4,181.
+
+\subsection{Creating the Mass-Limited Sample}
+\noindent We now investigate the distribution of our sample between mass and redshift.
+Figure \ref{fig:redshift_selection} shows the resultant distribution from our flux limited sample.
+In order to ensure that our results are not biased by a redshift-dependent mass/luminosity limit, we institute a cut in the mass of the interacting systems.
+Thus, creating a mass limited sample.
+We elect to use a mass cut of $\log(\frac{M}{M_\odot}) \geq 9.25$, shown by the blue dashed line in Figure \ref{fig:redshift_selection}.
+This specific cut is motivated by two reasons.
+First, this is the lowest mass system which is still observed in our the coalescing sample at $z = 1.2$.
+The second reason is that such a mass cut is approximately the one made in the environment catalogue we will describe later in Chapter \ref{data:environ}.
+There we make a cut of $\log(\frac{M}{M_\odot}) \geq 9.6$, we find that decreasing the mass cut to $\log(\frac{M}{M_\odot}) \geq 9.25$ does not make major differences to our results.
+Thus, we opt to use a lower mass cut to increase the number of galaxies in our sample.
+Making such a cut reduces our flux-limited sample of 4,181 to a mass-limited sample of 3,384 interacting galaxies.
+
+\begin{figure}
+\centering
+\includegraphics[width=\columnwidth]{figures/redshift-limitations.pdf}
+\caption[Redshift vs Mass distribution for each stage of interaction we have defined.]{Redshift vs Mass distribution for the four stages of interaction.
+We separate those systems with an identified secondary (in red) from those where no secondary could be found.
+The dashed blue line shows the mass cuts we make for our mass-limited sample and is set at $\log(\frac{M}{M_\odot}) \geq 9.25$.
+As shown here, the distribution of systems across redshift and mass is consistent for all stages in our sample.
 This is important as we use tidal distortion and the existence as tidal features as a fundamental for our classification methodology.
-As shown here, the distribution of systems across redshift and mass is consistent for all stages in our sample.
-Therefore, we are likely not affected by this in our analysis.}
+Therefore, we are likely not affected by this in our analysis.
+We find that our ability to identify pairs is primarily affected by stage and not redshift.}
 \label{fig:redshift_selection}
@@
 
-The second issue that could affect our sample is that of contamination by close pairs by projection effects rather than by galaxies which are physically close together.
-For the majority of these systems, we are limited to only having their photometric redshift from the COSMSO2020 catalogue and not their well-constrained spectroscopic redshift.
-As we are conducting visual classification, this issue is rather limited.
-The criteria on all of our sources besides stage 1 is that they must be morphologically disturbed.
-Each source is confirmed to have some kind of tidal feature f=present in the image, even if a secondary is not present in the image.
-There are, always, of course other galaxies in each image and there is no guarantee that the calculated photometric redshift is correct.
-We often find galaxies which are clearly interacting or paired, but with the photometric wildly different.
-In these cases, we defer to the redshift and only record one of the galaxies in our sample.
-This approach, however, means we must be careful to investigate the effects of environment on our galaxies as disturbance by, say, ram pressure stripping can appear like tidal features.
-
-\section{METHOD: Environment, AGN and Interaction Stage} \label{method}
+Throughout this Chapter, we will use our mass-limited sample in our analysis.
+This gives us uniform sensitivity across our volume.
+However, we also conducted the same analysis described below with the flux-limited sample and the qualitative conclusions of this Chapter did not change.
+
+\subsection{Sample Count Summary}\label{sec:sample-summary}
+\noindent Thus, to briefly sumarise this chapter, we have applied multiple cuts and additions to our initial sample of interacting galaxies.
+We have gone from an initial sample of 3,689 matched galaxies with COSMOS to a mass-limited sample of 3,384 galaxies.
+This mass-limited sample of galaxies is the one we will use throughout this work.
+In the mass-limited paired sample there are 338 pairs or 676 galaxies.
+
+\section{Method: Environment, AGN and Interaction Stage} \label{method}
 A primary aim of this work is to investigate the evolution of different galactic parameters with stage of the interaction.
@@
 This stage also relates to the projected separation of galaxies with an identified secondary.
-Here, we fully define what we mean by interaction stage and which part of the dynamical time it covers.
+Here, we define the short hand for the interaction stages and which part of the dynamical time they cover.
 We also describe how we find AGN in our full sample and find measurements of the environment about each.
@@
 Each stage covers a different part of the dynamical history in an interaction and, in this case, we define it based on the morphology and projected separation between systems.
-We define four distinct stages of interaction:
+We have already encountered the four stages we will investigate in Figures \ref{fig:matched-distributions} and \ref{fig:redshift_selection} and now define a short hand name to refer to them as well as fully describe the part of the dynamical history they represent.
+These are:
 
 \begin{itemize}
-    \item Stage 1: Systems which are well-separated with little to no morphological disturbance (Close pairs).
-    \item Stage 2: Close pairs showing morphological distortion while still in a pair or show a physical connection by tidal features.
-    \item Stage 3: Well separated pairs with morphological disturbance or isolated galaxies with clear tidal features.
-    \item Stage 4: Highly disturbed systems with two or more cores within them.
+    \item Separated: Systems which are well-separated with little to no morphological disturbance (Close pairs).
+    \item Pericentre: Close pairs showing morphological distortion while still in a pair or show a physical connection by tidal features.
+    \item Apocentre: Well separated pairs with morphological disturbance or isolated galaxies with clear tidal features.
+    \item Merging: Highly disturbed systems with a secondary core present.
 \end{itemize}
 
-\noindent Figure \ref{fig:stages} shows the original OR23 source cutouts of an example galaxy in each stage.
+\noindent Our four stage approach is not a new one, and many other works have utilised it to differentiate different parts of the dynamical history of a galaxy interaction \citep[e.g][]{2022ApJ...937...97C, 2023ApJ...952..122G}.
+
+Figure \ref{fig:stages} shows the original source cutouts used in Chapter \ref{chapter2} to give an example of each stage.
 There are degeneracy's associated with this staging system, however.
@@
 \centering
-    \includegraphics[width=0.45\textwidth]{figures/examples-stages.pdf}
-    \caption{Examples of the four stages we split our interacting galaxy sample into.
-Stage 1: A close pair with confirmed redshift matching.
-Stage 2: Two distinct systems interacting with tidal features forming.
-Stage 3: A tidally disturbed system with no secondary present, likely at apocentre.
-Stage 4: A galaxy with multiple cores while highly disturbed.
+\includegraphics[width=\columnwidth]{figures/examples-stages.pdf}
+\caption[Examples of the four stages we split our interacting galaxy sample into.]{Examples of the four stages we split our interacting galaxy sample into.
+Separated: A close pair with confirmed redshift matching.
+Pericentre: Two distinct systems interacting with tidal features forming.
+Apocentre: A tidally disturbed system with no secondary present, likely at apocentre.
+Merging: A galaxy with multiple cores while highly disturbed.
 At the final stage before coalescence.}
@@
 
-\begin{figure*}
-    \centering
-    \includegraphics[width=0.95\textwidth]{figures/projected-seps.pdf}
-    \caption{The projected separations of the confirmed galaxy pairs in our sample.
-This confers with other works the definition of our different stages.
-Stage 1 can be at any projected separation, however, we have visually confirmed that these sources are not morphologically disturbed.
-Stage 2 is dominated by systems with small projected separation as, by definition, they must be morphologically linked or overlapping.
-Those systems at larger separation are very large systems whose morphology categorise them as stage 2.
-Finally, stage 3 galaxies are those which are visually confirmed to be fully morphologically separated and tidally disturbed.
-The bulk of these lie in a range of 25 - 100kpc in projected separation from each other.
-There is some overlap between stage 2 and stage 3 in projected separation, as their visual classification is also dependent on the system size.}
-    \label{fig:proj-seps}
-\end{figure*}
-
-Stage 1 of the interaction captures the first approach of the two systems and they are observed as a galactic pair.
-They have no morphological disturbance yet and, in our sample, are most often those galaxies with distinct disks.
+The separated stage of the interaction captures the first approach of the two systems and they are observed as a galactic pair.
+They have no morphological disturbance and, in our sample, are most often those galaxies with distinct disks.
 At this point, we would expect no change in the underlying processes of the galaxies from their control samples.
@@
 By definition, this stage requires an identified secondary galaxy and therefore has the highest number of identified secondaries with every system having a secondary that can be visually classified.
-This is also the least degenerate part of the dynamical time we are sampling due to a criteria being no morphological disturbance.
-Therefore, it is unlikely that the galaxies would have already flown by each other.
-
-Stage 2 of the interaction is defined as the point where the two galaxies in the interaction are are at or just passing the pericentre of the tidal encounter.
+This is also the least degenerate part of the dynamical time we are sampling due to a criteria of no morphological disturbance.
+Therefore, it is unlikely that the galaxies have already made a passage.
+
+The pericentre stage of the interaction is defined as the point where the two galaxies in the interaction are at or just passing the pericentre of the tidal encounter.
 At this point, we find the beginning of morphological disturbance, the beginning of the formation of tidal features and some tidal debris.
@@
 Without further information, we are unable to define whether the galaxies involved at this stage are at the first, second, third, etc passage of the tidal encounter.
-We also do not know if they are just passing pericentre on the first pass, or if they are approaching pericentre on more than one pass.
-
-Stage 3 describes those interacting systems where the two disks are fully separated and distinct from one another.
-They must have some morphological disturbance associated with them, but do not require a secondary galaxy to be put into this stage as if the galaxies have sufficient velocity they would escape from each other and, therefore, their secondary could be outwith our COSMOS2020 cutouts used to visually identify them.
+We also do not know if they are approaching or have just passed pericentre.
+
+The apocentre stage describes those interacting systems where the two disks are fully separated and distinct from one another.
+They have some morphological disturbance associated with them, but do not require a secondary galaxy to be put into this stage.
+If the galaxies have sufficient velocity they would escape from each other and, therefore, their secondary could be beyond our COSMOS2020 cutouts used to visually identify them.
 This is reflected in an even distribution of finding the primary and secondary in this stage.
-This stage is also defines a large part of the dynamical timescale.
+This stage also defines a large part of the dynamical timescale.
 It spans from separating from the secondary and after pericentre, to moving out to the apocentre of the interaction (or escaping with sufficient velocity), to falling back in towards the secondary galaxy again.
@@
 
-Finally, stage 4 represents the final step of a galaxy interaction.
-If the two galaxies do not have sufficient velocity to escape one another, then they go on to coalesce and ultimately merge.
+Finally, the merging stage represents the final step of a galaxy interaction.
+If the two galaxies do not have sufficient velocity to escape one another they coalesce and ultimately merge.
 We define this stage through the severe morphological disturbance of the galaxy involved as well as the existence of a second core within it.
@@
 Post-merger remnants are systems where coalescence has been completed and immediately after will be highly morphologically disturbed and difficult to distinguish from those systems with merging ongoing.
-At this stage, we would expect the interaction will be at it's most violent with complete disruption of both galactic disks and likely increased star formation across the disk.
-
-Our four stage approach is not a new one, and many other works have utilised it to differentiate different parts of the dynamical history of a galaxy interaction \citep{2022ApJ...937...97C, 2023ApJ...952..122G}.
+At this stage, we would expect the interaction will be at its most violent with complete disruption of both galactic disks and likely increased star formation across the galaxy.
+
 We have noted the degeneracy of each stage as we have described them.
 Thus, we can now put this fully into the context of the dynamical timescale.
-Over a typical interaction, we would expect the galaxy pair to always move from stage 1 to stage 2 in the early times of the dynamical timescale.
-Then, dependent on the velocity of the system, the galaxy pair will either move straight into stage 4 of classification and begin to merge or it will move into stage 3.
-This change from stage 2 into stage 3 can then take many branching paths dependent on the velocity in the system.
-If the galaxies have sufficient velocity, stage 3 will be their end state until the tidal features slowly dissipate.
-If they do not have velocity to escape on another, the system will move from stage 3 back into stage 2.
-This could then happen for many cycles until finally the galaxies enter stage 4 and coalesce.
+Over a typical interaction, we would expect the galaxy pair to move from being separated to the pericentre of the interaction in the early times of the dynamical timescale.
+Then, dependent on the velocity of the system, the galaxy pair will either move straight into the merging stage of classification and begin to coalesce or it will move towards the apocentre stage.
+This change from pericentre to apocentre can then take two branching paths dependent on the velocity in the system.
+If the galaxies have sufficient velocity, the apocentre stage will be their end state until the tidal features slowly dissipate.
+If they do not have enough velocity to escape on another, the system will move from the apocentre stage back into the pericentre stage.
+This could then happen for many cycles until finally the galaxies enter the merging stage and coalesce.
 Figure \ref{fig:illustration} shows the branching paths that the galaxies can take through each stage.
-Note, these are created using the Advanced Python Stellar Animation Module restricted numerical simulation \citep[][O'Ryan et al., in prep.]{2016A&C....16...26W} and are for illustrative purposes only.
+These images are created using the Advanced Python Stellar Animation Module restricted numerical simulation, described in Chapter \ref{chapter4}, and are for illustrative purposes only here.
 
@@
 \centering
-    \includegraphics[width=0.95\textwidth]{figures/stage-evolution.jpg}
-    \caption{The progression through an interaction using our stage definitions.
-In stage 1, we have two systems that are approaching each other but exhibit no tidal features.
+\includegraphics[width=\textwidth]{figures/stage-evolution.jpg}
+\caption[The progression through an interaction using our stage definitions.]{The progression through an interaction using our stage definitions.
+In the separated stage, we have two systems that are approaching each other but exhibit no tidal features.
 This is before the point of closest approach has occurred.
-This is followed by an intial stage 2: the systems are approximately at their closest approach.
+This is followed by an intial pericentre stage: the systems are approximately at their closest approach.
 This stage is often mistaken, in the COSMOS catalogue, for being of only one source.
 Clear tidal features exist with major disturbance in the two disks.
-This is followed by stage 3, where there are two distinct cores with clear tidal features.
+This is followed by the apocentre stage, where there are two distinct cores with clear tidal features.
 However, after this point, there are two outcomes to the system depending on the galactic velocities.
-If the secondary has the escape velocity, the system will remain a stage 3 interaction until the tidal features dissipate (and no longer are in our sample).
-If they do not have enough energy, the system will return to stage 2 of the encounter and then begin to merge at stage 4.
-Images are from the Advanced Python Stellar Particle Annimation Module interacting galaxy algorithm described in O'Ryan et al.
-(in prep.) and based on the stellar particle animation module algorithm described in \citet{2016A&C....16...26W}.}
+If the secondary has the escape velocity, the system will remain an apocentre stage interaction until the tidal features dissipate (and no longer are in our sample).
+If they do not have enough energy, the system will return to the pericentre stage of the encounter and then begin to coalesce in the merging stage.
+Images are from the Advanced Python Stellar Particle Animation Module interacting galaxy algorithm described in Chapter \ref{chapter4} and based on the stellar particle animation module algorithm described in \citet{2016A&C....16...26W}.}
 \label{fig:illustration}
@@
 
-More commonly, in the literature, rather than using the stage of an interaction based on morphology we use the projected separation of the two systems.
+As described previously, in the literature, rather than using the stage of an interaction based on morphology the projected separation of the two systems is used.
 To explore the difference between using our staging system and the projected separation, as well as to ensure we recover the expected relations, we measure the projected separations of our confirmed galaxy pairs.
@@
 We measure this by taking the average of the best fit photometric redshifts between the two galaxies, and converting their angular separation to a physical one.
-The most distinct projected separation ($s_{proj}$) in stages is between stage 2 and stage 3.
-Here, we see that stage 2 is dominated by systems with $s_{proj}<$35kpc while stage 3 is dominated $25 \leq s_{proj} \leq 100$ kpc.
-Stage 2 is visually classified as systems which are highly morphologically disturbed, while either being morphologically linked to each other or overlapping.
+The most distinct projected separation ($s_{\mathrm{proj}}$) in stages is between the pericentre and apocentre stages.
+Here, we see that the percentre stage is dominated by systems with $s_{\mathrm{proj}}<$35kpc while the apocentre stage is dominated $25 \leq s_{\mathrm{proj}} \leq 100$ kpc.
+The pericentre stage is visually classified as systems which are highly morphologically disturbed, while either being morphologically linked to each other or overlapping.
 Those galaxy pairs with large projected separations are pairs which are very large in angular size, while still overlapping or morphologically linked.
-If this criteria is not met, then the system becomes a stage 3 interaction where the two galaxies in the pair are completely distinct.
-There is some overlap between the projected separations of stage 2 and stage 3 as this is somewhat dependent on the angular size of the two systems involved in the interaction.
-
-We will use the projected separation to investigate relations between AGN activity and if we observe enhancement in star formation with stage.
-The SFR is already present in the COSMOS2020 catalogue from both EAzY/FAST and LePhare.
-To ensure that any enhancements are from interaction alone, we must ensure we have no bias' in the environment distribution of our sample and identify AGN.
-We, therefore, cross match to two further catalogues COSMOS catalogues containing the required information.
+If this criteria is not met, then the system becomes an apocentre stage interaction where the two galaxies in the pair are completely distinct.
+There is some overlap between the projected separations of the pericentre and apocentre stage as this is somewhat dependent on the angular size of the two systems involved in the interaction.
+
+\begin{figure*}
+\centering
+\includegraphics[width=\textwidth]{figures/projected-seps.pdf}
+\caption[The projected separations of the confirmed galaxy pairs in our sample.]{The projected separations of the confirmed galaxy pairs in our sample.
+This confers with other works the definition of our different stages.
+The separated stage can be at any projected separation, however, we have visually confirmed that these sources are not morphologically disturbed.
+The pericentre stage is dominated by systems with small projected separation as, by definition, they must be morphologically linked or overlapping.
+Those systems at larger separation are very large systems whose morphology categorise them as at the pericentre stage.
+Finally, apocentre stage galaxies are those which are visually confirmed to be fully morphologically separated and tidally disturbed.
+The bulk of these lie in a range of 25 - 100kpc in projected separation from each other.
+There is some overlap between the pericentre and apocentre stages in projected separation, as their visual classification is also dependent on the system size.}
+\label{fig:proj-seps}
+\end{figure*}
+
+Figure \ref{fig:proj-seps-limits} shows the overlap between our four stages in projected separation.
+It also shows the limitations in our sample of finding the secondary galaxy in the interaction.
+This, primarily, is at low redshift where a larger projected separation represents a larger angular separation on the sky.
+This is a limitation of using visual confirmation of the secondary within a cutout of limited angular size.
+Thus, we see at low redshift ($z < 0.2$) we only identify pairs of galaxies with projected separation below $50kpc$.
+Towards our limiting redshift, however, we are able to identify galaxy pairs down to a projected separation of 10kpc, as well as out to 200kpc.
+
+% Need to integrate this figure.
+\begin{figure*}
+\centering
+\includegraphics[width=\textwidth]{figures/redshift-proj-sep-diagnostic.pdf}
+\caption[The measured distribution of projected separation with redshift.]{The measured distribution of projected separation with redshift.
+As we have made redshift cuts out to $z = 1.2$, we investigate the limitations on the projected separations we can successfully identify across our volume.
+We find that we can successfully identify secondary galaxies and their projected separations down to 10kpc to $z=1.2$.
+This is true across defined interaction stage.
+We find, because of the defined size of our cutouts, the limitation of finding the secondary galaxy is at low redshift.}
+\label{fig:proj-seps-limits}
+\end{figure*}
+
+We will use the projected separation to investigate relations between AGN activity and if we observe enhancement in star formation.
+The SFR is already present in the COSMOS2020 catalogue as measured using \texttt{EAzY}/\texttt{FAST}.
+To ensure that any enhancements are from interaction alone, we must ensure we have no biases in the environment distribution of our sample.
+First, we describe how we classify the environment of each of our matches.
 
 \subsection{Matching to Environment Catalogue}\label{data:environ}
-\noindent There is no measure of the environmental density in the COSMOS2020 catalogue.
+\noindent It is well known that the environment has a direct impact on the observed SFR of galaxies.
+A galaxy in a cluster environment has, on average, a higher SFR than those in the field \citep{2006MNRAS.373..469B}.
+Thus, if any of our stage classifications are biased towards one environment or another, it could impact our results.
+
+There is no measure of the environmental density in the COSMOS2020 catalogue.
 Such a measure is often calculated in numerous ways, such as the N-nearest neighbour \citep{2006MNRAS.373..469B}, different Bayesian metrics \citep{2008ApJ...674L..13C} or estimating it from Voronoi Tesselation \citep{2021inas.book...57V}.
-However, in this work, we utilise the existing environmental density catalogue produced by \citet{2017ApJ...837...16D}.
+However, in this Chapter, we use the existing environmental density catalogue produced by \citet{2017ApJ...837...16D}.
 This catalogue was created specifically for the COSMOS survey, and has a measured density for all sources with mass $\log(\frac{M}{M_\odot}) \geq 9.6$ and $z \leq 1.2$.
@@
 Then, from this subset, they calculate the weighted surface density within the redshift slice.
-The weighting is based upon the PDF of the photmetric redshift present within the redshift slice.
+The weighting is based upon the PDF of the photometric redshift present within the redshift slice.
 These weights significantly reduce the effects of projection effects.
@@
 The result of this process, and the cuts defined previously, is a catalogue of $\approx$45,000 galaxies with their densities accurately measured.
-We remove any sources which are flagged as uncertain from the catalogue (a flag existing within it) providing us with $\approx$39,000 sources with which to cross match the OR23 sample.
+We remove any sources which are flagged as uncertain from the catalogue (a flag in it) providing us with $\approx$39,000 sources with which to cross match the sample from Chapter \ref{chapter2}.
 We apply the same cuts to our sample as applied in \citet{2017ApJ...837...16D}, and only consider those systems with a mass $\log(\frac{M}{M_\odot}) \geq 9.6$.
-To cross match with our sample, we simply utilise the COSMOS2015\_ID which exists in both the COSMOS2020 catalogue and the \citet{2017ApJ...837...16D} catalogue.
-Upon applying the mass cut to our sample, we find that we are matching 2,800 sources to the \citet{2017ApJ...837...16D} catalogue.
+To cross match with our sample, we use the COSMOS2015\_ID which exists in both the COSMOS2020 catalogue and the \citet{2017ApJ...837...16D} catalogue.
+Upon applying the mass cut to our sample, we find 2,800 matches to the \citet{2017ApJ...837...16D} catalogue.
 Upon matching based upon the COSMOS2015 ID, we find that 628 sources in our sample do not exist in the environment catalogue.
@@
 
-Our cross match process is very much the same as previously described.
-We use the previously identified COSMOS2020 source coordinates and conduct a radial search of 10".
-If more than one source is within this radius, we match on the closest source.
+Our matching process is similar to previously described matching processes.
+We use the previously identified COSMOS2020 source coordinates and select the nearest source with in a 10" matching radius.
 We first find matches of radio AGN using the VLA 3GHz survey catalogue and then search the Chandra survey.
@@
 
-Applying our matching criteria, we find 1,059 classifications in the VLA 3GHz survey and 155 in the Chandra survey.
-These were split into 812 star forming galaxies and 402 AGN.
+Applying our matching criteria, we find 1,059 matches in the VLA 3GHz survey and 155 in the Chandra survey.
+From existing flags within the catalogues, these were split into 812 star forming galaxies and 402 AGN.
 We also investigate cross matching with the MPA-JHU catalogue \citep{2003MNRAS.341...33K, 2004MNRAS.351.1151B, 2007ApJS..173..267S}, however, found that all matches were already represented by the VLA and Chandra surveys.
-We also utilise the COSMOS XMM-survey and, again, find no new sources to add to our sample.
+We also use the COSMOS XMM-survey and, again, find no new sources to add to our sample.
 While the ratio of AGN to star forming galaxies in our sample seems large compared to other works, it is important to note that this is a result of limited matching between the catalogues.
 Of the 4,181 galaxies in our sample, only 1,214 appeared at all in either the VLA or Chandra catalogues.
-Any galaxy which did not appear in these catalogues, we discard as unclassified.
-
-\section{STAR FORMATION EVOLUTION WITH INTERACTION STAGE}\label{results:SF_stage}
-\subsection{Controlling for Interaction Stage}
-\noindent With the above samples selected, we investigate the change in multiple parameters with stage of the interaction.
-The four stages of interaction are designed to capture the main different parts of galaxy interaction.
-First, we show the results of breaking down our sample into stages with relation to the star formation and mass of our sample.
-We utilise the estimates of these parameters that exist in the COSMOS2020 catalogue itself.
-Then, we utilise our subsample of galaxy pairs to recover the relationship between projected separation and star formation enhancement (SFE).
-We then further break this measure down into it's component stages.
+
+\subsection{Visual Classification: Sources of Contamination}
+\noindent Throughout the description of our sample, we have identified these interacting systems by a combination of visual classification and the best-fit photometric measurements from the COSMOS2020 catalogue.
+This introduces limitations which could bias or contaminate our sample.
+We identify three serious areas of bias or contamination: 1) error inherent from using only photometric redshift measurements, 2) failure of identification of tidal features at higher redshifts due to surface brightness dimming and reduction in angular size, and 3) mis-identification of tidal features as disturbances caused by other processes.
+In this subsection, we will address each of these points and quantify how they affect our sample.
+We will also discuss any how we mitigate these effects where appropriate.
+
+First, there is always an inherent error in using the photometric redshift measurements of galaxies.
+We briefly mentioned this when describing pericentre stage systems.
+There, we found $\sim50$ systems which were clearly morphologically disturbed with linking tidal features, but their photometric redshifts were such that they couldn't possibly be interacting.
+It is also possible that we have missed pair identifications in the separated stage (where no tidal features are expected) due to incorrect photometric redshifts.
+We wish to quantify both these effects.
+\citet{2022ApJS..258...11W} quantify the error in their photometric redshift calculations (which we use here) as $<1$\% for our redshift and flux range.
+They quantify the scatter in the distribution of photometric to spectroscopic redshifts is $0.025(1+z)$ within our redshift and flux range.
+This leads to a maximum error on our photometric redshifts in this range of $\pm0.06$.
+
+\begin{figure}
+\centering
+\includegraphics[width=\columnwidth]{figures/redshift_scatter.pdf}
+\caption[The scatter in photometric redshifts of our paired sample.]{The scatter in photometric redshifts of our paired sample.
+Left shows the scatter in the primary and secondary photometric redshift measurements.
+Right the measured difference in the primary and secondary photometric redshifts found in the left panel.
+The red dashed lines show the expected error at the maximum redshift of our sample.
+As shown, the bulk of the sample lies within this region.}
+\label{fig:redshift-scatter}
+\end{figure}
+
+To investigate the affected systems, we therefore look at the redshift distribution of our paired sample.
+Figure \ref{fig:redshift-scatter} shows the scatter in our found pairs as well as the difference between them from our visual classification.
+During the visual classification, we instituted a cut that each interacting pair must be within a photometric redshift difference of $\pm0.1$.
+To estimate our completeness, we apply a bootstrapping test to our sample and see the number of systems we may have removed from our sample with this cut.
+We create a simulated paired sample of 10,000 systems and apply an error measurement based on the photometric redshift errors.
+This gives a paired sample across our redshift sample at slightly different redshifts.
+We then apply our cut, and check how many systems we would remove due to the photometric error from the COSMOS2020 catalogue.
+We find that we would retain $\approx91$\% of the sample with this cut, given the photometric redshift error.
+This is a lower limit on what we have retained, as we have not considered possible tidal features that would have caused us to keep the system in our sample.
+Therefore, we are unlikely to have removed a large percentage of interacting galaxies due to the photometric redshift error and the cuts we have applied.
+
+The resultant scatter in photometric redshifts between the primary and secondary in our paired sample is shown on the left panel of Figure \ref{fig:redshift-scatter}.
+The right hand panel shows the distribution of the difference measured between the primary and secondary photo-$z$s, with the red dashed lines showing the maximum expected error on the photometric redshift measurement at the highest redshift of our sample.
+As shown, the bulk of our paired sample lies at very low redshift difference, meaning we are unlikely to have removed too many systems.
+This leads us to conclude that our pair selection process has been robust.
+
+The second limitation of our approach is the failure of identifying interacting systems at high redshift due to missing the tidal features of the system.
+This would be a combined result of the affects of surface brightness dimming of their disks and tidal features at high redshift and while also having a small angular size.
+The former issue is mitigated by our limiting of our sample to be within a range of $0 \leq z \leq 1.2$ and with our mass limit of $9.25 \leq \log \frac{M}{M_\odot} \leq 12.5$.
+The latter is more difficult as we have a standardised cutout size which does not depend the redshift, or angular size of the system.
+This means that if a system were at redshift 1.2, our pixel resolution corresponds to roughly $0.5\rm{kpc~pix}^{-1}$ limiting the tidal features we would be able to identify.
+With such a scale we are able to identify extended tidal features away from the galactic disk such as tidal arms, but lack the resolution to those features which would be much closer to the disk.
+Thus, those interacting systems which have formed features such as shells, small tidal bridges or stellar streams will be missing from our samples at higher redshifts.
+Thus, at high redshift, we are most sensitive to the separated, apocentre and merging stage interacting systems while lacking the required resolution to pickup more intermediate tidal features at the pericentre stage.
+
+To investigate how we are affected by this, we look at the change in found fraction of micro, minor and major interactions across our redshift range.
+The effect of surface brightness dimming will be related to the type of interaction we are observing, and the resultant flux distribution of the tidal features.
+To get an idea of this, we split out pair sample into its constituent interaction types based on the mass ratio.
+We define the mass ratio such that the primary galaxy contains the highest stellar mass in the pair.
+If there is more than two galaxies involved in the interaction, we take the primary galaxy to be the galaxy with the highest stellar mass in the system.
+We define three different interaction types based on the mass ratio: micro (where the mass ratio is less than 1:10), minor (where the mass ratio is between 1:10 and 1:3) and major (where the mass ratio is greater than 1:3).
+We would expect that major interactions would not be changed by surface brightness dimming across redshift as these interactions create strong tidal features.
+Micro interactions, on the other hand, will likely be highly affected by surface brightness dimming.
+Micro interactions are such that the secondary is often completely destroyed in the interaction, leaving stellar streams about the primary galaxy.
+These tidal features will be in the low surface brightness regime, where they will quickly be lost at high redshift.
+
+\begin{figure}
+\centering
+\includegraphics[width=\columnwidth]{figures/mass-ratio-limitation.pdf}
+\caption[The change in found interaction type across our redshift distribution.]{The change in found interaction type across our redshift distribution.
+We define interaction types from the mass ratio of paired galaxies in our paired sample.
+\textit{Bottom}: The distrition of different interaction types across redshift.
+\textit{Top}: The change in the fraction found of different interaction types with redshift.
+As expected, the minor and major interaction fractions remain consistent with redshift but the micro interaction fraction declines.
+This is a result of surface brightness dimming on the tidal features formed in the interactions.
+In a micro interaction, we would see the complete destruction of the secondary into stellar streams about the primary galaxy.
+Such a tidal feature would be in the low surface brightness regime, and quickly be lost at increasing redshift.
+However, the change in fraction we find across our redshift range is not high enough to alter our conclusions.}
+\label{fig:mass-ratio-limitation}
+\end{figure}
+
+Figure \ref{fig:mass-ratio-limitation} shows the distribution of interaction types across redshift.
+The bottom panel shows the distribution in galaxy counts across redshift for the mass-limited sample.
+The top panel shows the change in the fraction of each interaction type we find in each redshift bin.
+For the minor and major interactions, we see that there is little change in the fractions across our redshift distribution.
+However, as expected, with micro interactions we see a gradual decline in the found fraction with increasing redshift.
+This shows a loss in sensitivity to this interaction type but over our redshift distribution there is not significant change that could change our conclusions.
+Therefore, we show this as a warning to those who might use our methodology over a wider redshift distribution.
+
+The final limitation of our approach we discuss is of relying on visual classification to identify interacting galaxies.
+Besides the issue of close pairs (described in previous sections) there is also assuming the disturbance of the systems is due to interaction, and not from other processes.
+The most obvious process which could mimic tidal disturbance is that of ram pressure stripping (RPS).
+RPS is an effect of the galactic environment stripping out the gas within a galaxy, and causing the formation of what appears like debris about the galactic disk.
+It can also cause major disturbance and irregular morphology.
+Thus, this could easily be a form of high contamination in the apocentre and merging stages of our sample.
+The environment that RPS is most prevalent is that of a cluster environment.
+Therefore, if we are highly contaminated to identifying RPS galaxies as interacting galaxies, we would see a bias in the environment of our sample towards galaxy clusters.
+To check this, we measure the distributions of our galaxies in each environment with stellar mass.
+We use the sample matched to \citet{2017ApJ...837...16D} as described in Chapter \ref{data:environ}.
+
+Figure \ref{fig:dens-stage} shows the distribution of our matched samples with their density values with Figure \ref{fig:environ-fract} showing the change in environment fraction with stage.
+It is important to note that \citet{2017ApJ...837...16D} has a higher mass cutoff than we have implemented in our underlying sample.
+Therefore, this is showing the density of all systems $\log$M$_*$/ M$_\odot \geq$ 9.6.
+We conduct weighted Kolmogorov-Smirnov \citep[KS-test;][]{an1933sulla} and Anderson-Darling \citep[AD-test;][]{stephens_74} on the environment distributions.
+The KS-test is excellent at comparing different weighted distributions and indicating if they are drawn from the same parent sample.
+The AD test tests for this similarity as well, and we use both to ensure consistency and robustness in our measurements.
+These tests confirm they are likely drawn from the same parent sample, with the resultant $p$-values $\approx1$ the distributions.
+Thus, we can confidently state there are no biases in our stage selection with environment, and it fair to assume that any evolution we find between interaction stages is due to interaction and not due to biases in the environment of our stages samples.
+
+\begin{figure}
+\centering
+\includegraphics[width=\columnwidth]{figures/density-stage.pdf}
+\caption[The density about each of our sources matched with the \citet{2017ApJ...837...16D} catalogue.]{The density about each of our sources matched with the \citet{2017ApJ...837...16D} catalogue.
+As shown, there is no existing bias in the distribution of galactic environments throughout our stages.
+Therefore, that we have identified primarily tidal affects and not environmental ones.}
+\label{fig:dens-stage}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=\columnwidth]{figures/environment-fractions.pdf}
+\caption[The fraction of galaxies in each stage in different environments.]{The fraction of galaxies in each stage in different environments.
+This reinforces that there is no overarching bias between our samples for the cluster environment.
+In the cluster environment, RPS could lead to morphologies which appeared like tidal disturbance.}
+\label{fig:environ-fract}
+\end{figure}
+
+To reinforce this, Figure \ref{fig:dens-sfr-mass} shows the environment classification in our reduced stellar mass-SFR distribution.
+This shows that there is no ordered structure, or bias, in our sample with environment and further reinforces that the galactic environment is not responsible for effects we may find from interaction.
+The majority of our sample lie either within filaments or in the field.
+The environment which would have the most effect upon the SFRs of our sample is a cluster environment.
+However, the fraction of our sample within a cluster is never greater than $\sim20$\%.
+Therefore, the lack of information here does not have a large impact on this measurement.
+
+\begin{figure}
+\centering
+\includegraphics[width=\columnwidth]{figures/sfr-mass-density.pdf}
+\caption[The distribution of environment classifications through our sample.]{The distribution of environment classifications through our sample.
+This is only for sources with a $\log$M$_*$ / M$_\odot \geq$ 9.6.
+However, from this subsample, we see that there is no trend with environment and that the distribution is random throughout each stage.}
+\label{fig:dens-sfr-mass}
+\end{figure}
+
+Another source that could be of major contamination is in our merging stage sample.
+We have identified the merging stage as those systems with a disturbed disk and containing more than one core.
+Another such system that could be recognised by this description is that of a clumpy galaxy.
+Clumpy galaxies are systems with internal regions undergoing intense star formation.
+These regions appear like multiple other `cores' throughout the galactic disk which are actually clumps of young stellar populations.
+To avoid such contamination, we apply multiple criteria to mitigate the potential impact they might have.
+First, our redshift range spans a sufficient range that the found fraction of clumpy galaxies declines rapidly compared to the merger rate \citep{2022ApJ...931...16A}.
+This is particularly true at $0.15 \leq z \leq 1$.
+Previous works have found the peak of the fraction of clumpy galaxies at $z\approx2$ \citep{2014ApJ...786...15M, 2018ApJ...853..108G}, well beyond our redshift range.
+There are also two morphological distinctions that we use to our advantage to discern between merging and clumpy galaxies.
+Clumpy galaxies often exhibit more than one clump at different radii across the galactic disk \citep[with][finding a mean of 3.16 clumps per galaxy]{2022ApJ...931...16A}, making them easy to differentiate from a second core which would be close to the centre of a perturbed disk.
+We therefore remove potential merging galaxies which appear to have more than one `core' at different places of a non-perturbed disk ($\sim25$).
+With the low fraction of clumpy galaxies in our redshift range and an increased number of cores compared to mergers we are confident we have separated out potential contamination by clumpy galaxies.
+
+\subsection{Aside: Mass Ratios in Sample}
+Here, we briefly discuss the mass ratios we find of our identified pairs of interacting galaxies.
+Figure \ref{fig:mass-ratio} shows the distribution of interaction types through our subsample.
+We find that our sample is dominated by micro and minor interactions.
+
+\begin{figure}
+\centering
+\includegraphics[width=\columnwidth]{figures/mass-ratio-diagnostic.jpeg}
+\caption[The distribution of mass ratios in our paired sample and across each stage of interaction.]{The distribution of mass ratios in our paired sample and across each stage of interaction.
+These are separated into our previously defined interaction stages and the interaction type (based on mass ratio).
+We find that, overwhelmingly, our sample is dominated by micro and minor interactions.
+These are where the two systems have very different stellar masses.}
+\label{fig:mass-ratio}
+\end{figure}
+
+The mass ratio is known to have a direct impact on the potential enhancements we see in SFR and in AGN fraction.
+While we do not focus on the mass ratio throughout this work, due to the limited pair galaxy size, knowing that we are dominated by micro and minor interactions will inform us of the relations we expect to uncover from our analysis.
+This assumes, of course, the subsample of galaxy pairs is representative.
+With this note on the distribution of interaction types based on mass ratio in mind, we now look at the relation between the stellar mass of our systems and the SFRs through interaction stage.
+
+\section{Star Formation and AGN Evolution with Interaction Stage}\label{results:SF_stage}
+\subsection{Controlling for Interaction Stage}\label{results:int_stage}
+\noindent With our mass-limited sample selected, we investigate the change in multiple parameters with stage of the interaction.
+First, we show the results of breaking down our sample into stages with relation to the SFR and stellar mass of our sample.
+We use the estimates of these parameters that exist in the COSMOS2020 catalogue itself.
+Then, we use our subsample of galaxy pairs to recover the relationship between projected separation and star formation enhancement (SFE).
+We then further break this measure down into its component stages.
 
 Figure \ref{fig:sfr-mass} shows the breakdown of stellar mass and SFR with stage.
-On a population scale, there is clear evolution in the star formation rate from stage 1 through to stage 4.
-In stage 1, where the galaxies are distinct from one another with no clear morphological disturbance, we clearly see two populations of galaxies.
+On a population scale, there is clear evolution in the star formation rate from the separated stage through to the merging stage.
+In the separated stage, where the galaxies are distinct from one another with no clear morphological disturbance, we clearly see two populations of galaxies.
 These are the blue, star-forming galaxies and red sequence of galaxies.
 The blue contours in Figure \ref{fig:sfr-mass} show increasing number density in the population into the blue cloud.
-In stage 2, when the galaxies are actively interacting and overlapping, this red sequence remains but is highly diminished while there is no change in the blue cloud.
-Stage 3 shows a similar effect, where the red sequence reduces again before finally in stage 4 the red sequence completely disappears.
-Through these, the blue cloud remains highly populated and hosts the majority of galaxies in the sample.
-
-\begin{figure}
-    \centering
-    \includegraphics[width = 0.45\textwidth]{figures/sfr-mass-stages.pdf}
-    \caption{The LePhare stellar mass against the EAzY SFR across the different stages of the interaction.
+In the pericentre stage, when the galaxies are actively interacting and overlapping, this red sequence remains but is highly diminished while there is no change in the blue cloud.
+The apocentre stage shows a similar effect, where the red sequence reduces again before finally in merging the red sequence completely disappears.
+Through these, the blue cloud remains highly populated and hosts the majority of galaxies in the stage.
+
+\begin{figure}
+\centering
+\includegraphics[width = \columnwidth]{figures/sfr-mass-stages.pdf}
+\caption[The \texttt{LePhare} stellar mass against the \texttt{EAzY} SFR across the different stages of the interaction.]{The \texttt{LePhare} stellar mass against the \texttt{EAzY} SFR across the different stages of the interaction.
 The blue contours are 8 levels of density of the underlying populations in each frame.
-\textit{Top left}: The stellar mass and star formation rate of Stage 1 of our sample.
+\textit{Top left}: The stellar mass and star formation rate of the separated stage of our sample.
 Here, the interacting galaxies are simply close pairs with little to no morphological disturbance.
 There are clearly two populations here: a main, star forming sequence forming the main population and a smaller red sequence.
-\textit{Top right}: Stage 2 of the interaction, where the two interactors are close to pericentre.
+\textit{Top right}: pericentre stage of the interaction, where the two interactors are close to pericentre.
 The star forming sequence remains, but the red sequence is reduced significantly.
-\textit{Bottom left}: Stage 3 of the interaction, where the interactors are close to apocentre or escaped.
+\textit{Bottom left}: apocentre stage of the interaction, where the interactors are close to apocentre or escaped.
 Here, we see the almost complete disappearance of the red sequence.
-\textit{Bottom Right}: Stage 4 of the interaction, where the two systems are close to coalescence or have merged.
+\textit{Bottom Right}: merging stage of the interaction, where the two systems are close to or have coalescence.
 The red sequence of galaxies has completely disappeared.}
@@
 For instance, if the mass distribution of our sources evolves as well, we could simply be selecting higher mass systems as we increase stage.
-This would have the result of systems in stage 4 having, on average, higher SFRs than those in stage 1 and appearing like we had evolution in the star forming population with stage.
+This would have the result of systems in the merging stage having, on average, higher SFRs than those in the separated stage and appearing like we had evolution in the star forming population with stage.
 Another effect that could cause this relation to appear would be our selection was highly dependent on galactic environment.
-It is well known that environment and star formation are closely linked, and that classifying interacting galaxies by morphology classifiers can weight up galaxies in cluster environments over galaxies in the field.
-In Section \ref{sec:env-cont}, we control for the environment in our sample and show that this is not the case.
-Here, we investigate the question of the evolution of the mass distribution that could give us this result.
+However, we have already explored this possibility in Chapter \ref{data:environ} and found no bias in environment between the stages.
+Therefore, this is likely not the cause of this decrease in the red sequence population.
 
 We can quantify the similarity of the mass distributions, and then the SFR distributions, using well known statistical tests.
-We opt to use two different tests: the Kolmogorov-Smirnov \citep[KS-test;][]{an1933sulla} and Anderson-Darling \citep[AD-test;][]{stephens_74}.
-The KS-test is excellent at comparing different weighted distributions and indicating if they are drawn from the same parent sample.
-The AD test tests for this similarity as well, and we utilise both to ensure consistency and robustness in our measurements.
+We opt to conduct tests: KS and AD-tests.
 First, we create weighted distributions of stellar mass.
-The weighting scheme we utilise balances the distributions such that each bin could be assumed to have the same number of sources within it.
+The weighting scheme we use balances the distributions such that each bin could be assumed to have the same number of sources within it.
 Therefore, any bins with fewer than a certain number of sources will be weighted up while those bins with more will be weighted down.
@@
 \centering
-    \includegraphics[width = 0.45\textwidth]{figures/stellar-mass-dist.pdf}
-    \caption{The stellar mass distribution across the four stages. Each bin is weighted based on the counts in the smallest sub-sample in stage. This is stage 4 of interaction.}
+\includegraphics[width = \columnwidth]{figures/stellar-mass-dist.pdf}
+\caption[The stellar mass distribution across the four stages.]{The stellar mass distribution across the four stages.
+Each bin is weighted based on the counts in the smallest sub-sample in stage: the merging stage of the interaction.}
 \label{fig:weighted-mass}
@@
 \centering
-    \includegraphics[width=0.45\textwidth]{figures/sfr-dist.pdf}
-    \caption{SFR distribution weighted by mass across each stage. This weighting is based on our sample of stage 4.}
+\includegraphics[width=\columnwidth]{figures/sfr_dist.pdf}
+\caption[SFR distribution weighted by mass across each stage.]{SFR distribution weighted by mass across each stage. This weighting is based on our sample of merging stage.}
 \label{fig:weighted-sfr}
@@
 Figure \ref{fig:weighted-mass} shows the weighted mass distributions through the four different stages.
-These appear highly similar, however to statistically measure the similarity we apply our KS- and AD-tests to them.
-We chain the KS- and AD- test through each distribution and calculate the value of the test values and a p-value.
-This p-value represents the probability that each distribution is drawn from the same parent distribution.
-For each mass distribution, we find that p-value of both tests is approximately one.
-Thus, proving that the distribution ins tellar mass though each stage is very similar, and no stellar mass evolution is occurring.
+These appear similar, however, to statistically measure the similarity we apply our KS- and AD-tests to them.
+We chain the KS and AD test through each distribution and calculate the value of the test values and a $p$-value.
+This $p$-value represents the probability that each distribution is drawn from the same parent distribution.
+For each mass distribution, we find that $p$-value of both tests is $\approx1$.
+Thus, proving that the distribution in stellar mass though each stage is likely drawn from the same parent sample.
+
 Figure \ref{fig:weighted-sfr} shows the SFR distributions while being weighted by stellar mass.
-When comparing stages 1 and 2, 1 and 3, 1 and 4, 2 and 4 and 3 and 4, the p-values are $\ll$0.05.
-This allows us to reject the null hypothesis for these distributions and assume they are from different parent samples and are very disimilar.
-However, for comparing stages 2 and 3, the p-value of the KS test is $\approx$0.90.
+When comparing the separated and pericentre, separated and apocentre, separated and merging, pericentre and merging and apocentre and merging stages, the $p$-values are $\ll$0.05.
+This allows us to reject the null hypothesis for these distributions and assume they are from different parent samples.
+However, for comparing pericentre and apocentre stages, the $p$-value$=0.74$.
 Thus, while these distributions are likely to be not identical, they are very similar in the parent sample they have been drawn from.
-\textbf{For the same mass distribution through each stage of interaction, the star formation distribution radically changes from stage 1 to stage 2 and from stage 3 to stage 4, while remaining reasonably similar from stage 2 to stage 3.}
+For the same mass distribution through each stage of interaction, the star formation distribution changes from separated to pericentre stage and from apocentre to merging stage, while remaining similar from the pericentre to apocentre stage.
+The errors on these distributions are calculated using the methodology of \citet{2011PASA...28..128C}.
+In this approach, we assume that the error about our measurements is simply a measure of the limited samples we have of the underlying beta distribution of the full population.
+Thus, we can measure the confidence intervals around our measurement by using the beta distribution.
+We calculate the 68.3\% confidence interval about our found value, and use the distance between these values as our upper and lower errors.
 
@@
 The first is when the interacting system moves from being a close pair to actually morphologically disturbing each other in a close flyby.
-This difference, most likely enhancement, then persists through through to stage 3 - where the galaxies remain highly disturbed but are no longer overlapping with their secondary.
+This difference, most likely enhancement, then persists through to the apocentre stage - where the galaxies remain highly disturbed but are no longer overlapping with their secondary.
 The SFR distribution remains approximately the same between these two, meaning the forces that drive and affect star formation remain equivalent between these two stages.
-Finally, the SFR radically changes again when we approach the merging or post-merger stage of the interaction.
+Finally, the SFR changes again when we approach the merging or post-merger stage of the interaction.
 We can also say that this change is likely an enhancement in the SFR of the galaxies through the interaction due this change being driven by the disappearance of the red sequence through each stage.
 
-We further examine this result by controlling for redshift and making specific classification of galaxy type.
+We further examine this result by controlling for redshift and making specific classifications of galaxy star formation class.
 While the red sequence is significantly reduced across across each stage, it is difficult to ascertain the change in the galaxies within the blue cloud.
 We expect that, due to an interaction, the population of starbursting and quiescent galaxies will change.
-Therefore, we define a star forming main sequence (SFMS) through across redshift.
+Therefore, we define a star forming main sequence (SFMS) across redshift.
 This allows us to classify each source based on its SFR independently of redshift.
@@
 
-\noindent This finds the expected, main sequence, SFR of a galaxy at a given stellar mass, $M_*$, and redshift, z.
-
-The ratio of the measured galaxy SFR and the expected main sequence SFR is then taken. We then use this fraction to classify each galaxy into distinct bins. These are:
+\noindent This finds the expected main sequence SFR of a galaxy at a given stellar mass, $M_*$, and redshift, z.
+
+The ratio of the measured galaxy SFR and the expected main sequence SFR is then taken. We then use this fraction to classify each galaxy into distinct bins. These bins are:
 
 \begin{enumerate}[(i)]
-    \item Starburst galaxies. Here, the galaxy SFR is highly elevated compared to the SFMS. We follow \citet{2019MNRAS.484.4360A} and define a cutoff of $\log$SFR/SFR$_{\text{MS}} >$ 0.4.
-    \item Main sequence galaxy. The galaxy is within 0.4 dex of the SFMS and approximately has the expected SFR. Defined as $-0.4 < \log$SFR/SFR$_{\text{MS}} < 0.4$.
-    \item Sub-main sequence galaxy. A galaxy whose SFR is below the majority of the SFMS, but likely not quiescent. Defined as $-1.3 < \log$SFR/SFR $_{\text{MS}} < $ -0.4.
-    \item Quiescent (High) galaxy. A galaxy with an SFR in the top $\approx$50\% of the quiscent galaxy population. Defined as $-2.3 < \log$SFR/SFR $_{\text{MS}} <$ -1.3.
-    \item Quiescent (Low) galaxy. A galaxy with low SFR and very likely completely quenched. Defined as $\log$SFR/SFR $_{\text{MS}} <$ -2.3.
+    \item Starburst galaxies. Here, the galaxy SFR is highly elevated compared to the SFMS. We follow \citet{2019MNRAS.484.4360A} and define a cutoff of $\log$ SFR/SFR$_{\text{MS}} >$ 0.4.
+    \item Main sequence galaxy. The galaxy is within 0.4 dex of the SFMS and approximately has the expected SFR. Defined as $-0.4 < \log$ SFR/SFR$_{\text{MS}} < 0.4$.
+    \item Sub-main sequence galaxy. A galaxy whose SFR is below the majority of the SFMS, but likely not quiescent. Defined as $-1.3 < \log$ SFR/SFR $_{\text{MS}} < $ -0.4.
+    \item Quiescent (High) galaxy. A galaxy with an SFR in the top $\approx$50\% of the quiscent galaxy population. Defined as $-2.3 < \log$ SFR/SFR $_{\text{MS}} <$ -1.3.
+    \item Quiescent (Low) galaxy. A galaxy with low SFR and very likely completely quenched. Defined as $\log$ SFR/SFR$_{\text{MS}} <$ -2.3.
 \end{enumerate}
@@
 \noindent We split our sample into its different stages and apply these criteria.
-Figure \ref{fig:sfr-clsf} shows the ratio between the expected SFMS SFR and the measured SFR in the COSMOS2020.
-This clearly shows a large increase in galaxies classified as starburst from stages 1 to 4 and a large reduction in the number of quenched systems.
+Figure \ref{fig:sfr-clsf} shows the ratio between the expected SFMS SFR and the measured SFR in COSMOS2020.
+This clearly shows a large increase in galaxies classified as starburst from the separated to merging stages and a large reduction in the number of quenched systems.
 Figure \ref{fig:sfr-clsf-bar} shows the change in fraction of the different galaxy classifications through stage, reflecting the results found in Figure \ref{fig:sfr-mass}.
-Initially, in stage 1, we find that the majority of our galaxies lie on the SFMS or just below it.
+Initially, in the separated stage, we find that the majority of our galaxies lie on the SFMS or just below it.
 There also exists a small population of galaxies which are classified as starburst with a population of quiescent galaxies that is roughly double the starburst fraction.
-As we move through the interaction stage, we see that the quiescent galaxy fraction gradually decreases to the point of almost non-existence in stage 4 galaxies.
-The complete inverse is true in our starburst fraction.
-We find that this almost quadruples in the fraction of our sample over the course of the different stages of interaction.
+As we move through the interaction stage, we see that the quiescent galaxy fraction gradually decreases to the point of almost non-existence in the merging stage galaxies.
+The inverse is true in our starburst fraction.
+We find this almost quadruples over the course of the different stages of interaction.
 The fraction of galaxies on the SFMS remains dominant throughout, however, we do find the fraction of sub-MS galaxies significantly reduced.
-Thus, we find that, in general, the SFR of these galaxies is increasing with interaction stage (though, not in stage 2 - 3), but not hugely.
+We find that, in general, the SFR of these galaxies is increasing with interaction stage (though, not in the pericentre to apocentre stage).
 It appears to have sub-MS and quiescent galaxies move up and join the SFMS (as it remains dominant).
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=0.45\textwidth]{figures/sfr-clsf-dist.pdf}
-    \caption{Stellar mass against the ratio of measured SFR to the expected SFR if the galaxy was on the SFMS.
+\begin{figure*}
+\centering
+\includegraphics[width=\textwidth]{figures/sfr-clsf-dist.pdf}
+\caption[Stellar mass against the ratio of measured SFR to the expected SFR if the galaxy was on the SFMS.]{Stellar mass against the ratio of measured SFR to the expected SFR if the galaxy was on the SFMS.
 Black points are the individual sources, while the blue contours are as in Figure \ref{fig:sfr-mass}.
 The red dotted lines show the cutoffs for different galaxy classifications based on their SFR, with each cut off being defined by the text in blue.
+The histograms beside each plot show the change in counts.
 We find that through interaction stage, the quiescent galaxy population significantly reduces while the starburst population rapidly increases.
@@
 \label{fig:sfr-clsf}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.45\textwidth]{figures/sfr-clsf-bar.pdf}
-    \caption{The change in fraction of different galaxy classifications from the fraction of SFR to the expected SFR on the SFMS.
+\end{figure*}
+
+\begin{figure}
+\centering
+\includegraphics[width=\columnwidth]{figures/sfr-clsf-bar.pdf}
+\caption[The change in fraction of different galaxy classifications from the fraction of SFR to the expected SFR on the SFMS.]{The change in fraction of different galaxy classifications from the fraction of SFR to the expected SFR on the SFMS.
 While galaxies on the SFMS remain dominant through each sample across interaction stage, there is significant change in the starburst and quiescent populations.
-The starburst galaxy population moves from being roughly half the size of the quiescent population in stage 1 to completely dominating it in stage 4.
-This is occurring while the quiescent population is significantly reduced to almost non-existence in stage 4.}
+The starburst galaxy population moves from being roughly half the size of the quiescent population in the separated stage to completely dominating it in the merging stage.
+This is occurring while the quiescent population is significantly reduced to almost non-existence in the merging stage.}
 \label{fig:sfr-clsf-bar}
@@
 
-Now, it is important to note the parameter space that we are searching in these examples.
+It is important to note the parameter space that we are searching in these examples.
 We are probing interactions between galaxies of high mass, where the resultant tidal features that form would be classifiable in an image.
-Hence, even those mergers which are considered dry - with very little gas - would be capable of driving major rejuvenation in the star formation of these systems.
+The majority of our sample is minor interactions where one of the two systems is very highly perturbed by the interaction.
+In this parameter space, we would expect large increases in the SFRs.
 However, we do not see a significant increase in the starbursting population until we the two galaxies begin to actually coalesce.
-However, \textbf{we find clear, statistically robust evolution of a galaxys' SFR with interaction stage.
-The SFR changes dramatically from stage 1 to 2 and stage 3 to 4 - after the initial passage of closest approach and at the point of coalescence of the interaction.}
+Thus, the effect of the interaction itself may be to only enhance the SFR, while at coalescence we find the dramatic starburst.
+This can be argued from our results of clear, statistically robust change and evolution of a galaxy's SFR with interaction stage.
+The SFR changes dramatically from the separated to pericentre stage and apocentre to merging stage - after the initial passage of closest approach and at the point of coalescence of the interaction.
 
 \subsection{Projected Separation and Star Formation Enhancement}
-\noindent We directly investigate the relation between the star formation enhancement (SFE) and the projected separation using our confirmed sub-sample of galaxy pairs.
-This sample is significantly smaller than our non-pair sample: containing 480 pairs or 960 galaxies (we have also added some pairs from the additional interacting galaxy sample).
-Upon sub-dividing this into different stages we find 310 stage 1 galaxies, 146 stage 2 galaxies and 498 stage 3 galaxies.
-Only 3 stage 4 galaxies were in our confirmed galaxy pair sub-sample, and therefore we do not attempt to make inferences about this population.
-
-To measure the SFE of our galaxy pairs, we directly compare to the mass- and redshift-matched control sample that was also created with this sub-sample and defined in Section \ref{sec:sec-ident}.
+\noindent We directly investigate the relation between the SFE and the projected separation using our confirmed sub-sample of galaxy pairs.
+This sample is significantly smaller than our non-pair sample: containing 338 pairs or 676 galaxies (we have also added some pairs from the additional interacting galaxy sample).
+Upon sub-dividing this into different stages we find 228 separated galaxies, 102 pericentre galaxies and 342 apocentre galaxies.
+Only 4 merging galaxies were in our confirmed galaxy pair sub-sample, and therefore we do not attempt to make inferences about this population.
+
+To measure the SFE of our galaxy pairs, we directly compare to the mass- and redshift-matched control sample that was also created with this sub-sample and defined in Chapter \ref{sec:sec-ident}.
 We separate our galaxy pairs into different bins based on the projected separation between them.
@@
 We define a cutoff that each bin must contain at least 10 counts to be included in this plot and, therefore, by changing the bin widths with projected separation we are able to maintain some level of statistical robustness.
-We define our bins as [0.5, 10, 20, 50, 100, 125, 150] kpc.
+We define our bins as [0.5, 10, 20, 50, 100, 125] kpc.
 
@@
 We then take the average of each bin.
-By taking the average of each bin, we find the total excess of the SFR caused by interaction alone and then comparing it to what we would expect from non-interacting galaxies in the same bin.
+By taking the average of each bin, we find the total excess of the SFR caused by interaction alone and then compare it to what we would expect from non-interacting galaxies in the same bin.
 Note, that the control galaxy relation to the projected separation is meaningless as they are not paired.
 The control galaxies are simply mass and redshift matched to each interacting galaxy and used as a reference for what SFR we would expect of it had it not been interacting.
-Finally, we divide the the averaged interacting SFR distribution by the averaged control SFR distribution.
-This provides us with a measure of the excess star formation due to interaction, and the SFE when compared to the regular population.
+Finally, we divide the averaged interacting SFR distribution by the averaged control SFR distribution.
+This provides us with a measure of the excess star formation due to interaction, and the SFE when compared to the isolated population.
 
@@
 \centering
-    \includegraphics[width=0.95\textwidth]{figures/sfr-enhancement-projected-sep.pdf}
-    \caption{The projected separation against the star formation enhancement in average star formation at different bins of projected separation.
+\includegraphics[width=\textwidth]{figures/sfr-enhancement-projected-sep.pdf}
+\caption[The projected separation against the SFE in average star formation at different bins of projected separation.]{The projected separation against the SFE in average star formation at different bins of projected separation.
 Each bin must contain at least 10 counts to be considered.
@@
 \textit{Right}: As left but broken up into different stages of the interaction.
-Black markers are stage 1, red stage 2 and blue stage 3.
-We only investigate stages 1,2 and 3 as only three galaxy pairs were identified in stage 4.
-Here, we find a generally decreasing star formation enhancement with projected separation but very different individual behaviour dependent on the stage classification.}
+Black markers are the separated stage, red the pericentre stage and blue the apocentre stage.
+We limited our investigation to the separated, pericentre and apocentre stages as only three galaxy pairs were identified in the merging stage.
+We find a generally decreasing star formation enhancement with projected separation but very different individual behaviour dependent on the stage classification.}
 \label{fig:sfr-enhancement-sep}
@@
 On the left of the plot, we have the distribution for the full galaxy pair sample, without taking account of stage.
-The errors on our measurements are calculated as the standard deviation from the mean within the bin.
+The errors on our measurements are following the methodology of \citet{2011PASA...28..128C} and briefly described in Chapter \ref{results:int_stage}.
 The dashed black line represents no enhancement in SFR, as the average SFR in the interacting galaxy sample would be equal to the average SFR in the control sample.
-We find at very small projected separation a SFR enhancement of 1.87 which gradually decreases with projected separation down to approximately 1 at 117.5kpc.
+We find at very small projected separation a SFR enhancement of 1.74 which gradually decreases with projected separation down to approximately 1 at 117.5kpc.
 
@@
 This shows very different behaviour in enhancement dependent on the stage of the interaction.
-In stage 1, we find that the star formation is very weakly enhanced, and with no overall structure.
+In the separated stage, we find that the star formation is very weakly enhanced, and with no overall structure.
 The enhancement moves around 1 through the distribution, with some enhancement being a result of low number counts in the bin.
-Taking into account the errors on our measurements, the true value of the enhancement could be around 1 for the entire projected separation distribution.
 This is not unexpected.
-Stage 1 represents when the two galaxies are close pairs, but with no morphological disturbance.
+The separated stage represents when the two galaxies are close pairs, but with no morphological disturbance.
 Therefore, we would not expect significant, if any, enhancement in the SFR based on the projected separation.
-This is the stage with the lowest enhancement across projected separation, remaining close to 1.
-
-In stage 2, we see consistent enhancement with projected separation.
-It is also much larger than stage 1, with it being approximately 1.75 up to 1.90.
+This is the stage with the lowest enhancement across projected separation.
+
+In the pericentre stage, we see consistent enhancement with projected separation.
+It is also much larger than the separated stage, with it being approximately 1.6.
 In fact, the measured enhancement increases across the 50kpc of projected separation.
-However, accounting for the errors on these measurements and the declining counts in each bin, it is likely that the enhancement does drop as the projected separation increases.
-We see a very large enhancement in the overlapping stage 3 galaxies which overlap with the stage 2 measurements.
-The enhancement in stage 3 galaxies then rapidly declines as we move to higher projected separations.
+However, accounting for the errors on these measurements and the declining counts in each bin, it is likely that the enhancement remains constant as the projected separation increases.
+We see a very large enhancement in the overlapping apocentre stage galaxies which overlap with the pericentre stage measurements.
+The enhancement in apocentre stage galaxies then rapidly declines as we move to higher projected separations.
 After 150kpc, our galaxy pair sample does not have the counts to make robust estimates of the SFE.
-However, it is important to note that this result has been found with a sample of 960 interacting galaxies in their pairs.
-No stage 4 galaxies have been represented and in numerous projected separation bins the counts are small enough to have conclusion altering error bars.
-\textbf{Therefore, it is imperative that future works, with larger sample sizes not only look at the projected separation of the systems but the morphology as well.}
-
-\subsection{Controlling for Galactic Environment} \label{sec:env-cont}
-\noindent While we have found clear evidence of evolution in the SFR of interacting galaxies with stage, it is important we remove a potential source of contamination.
-It is well known that the environment has a direct impact on the observed SFR of galaxies.
-A galaxy in a cluster environment has, on average, a higher SFR than those in the field \citep{2006MNRAS.373..469B}.
-Thus, if any of our stage classifications are biased towards one environment or another, it could have severe consequences for our results.
-Therefore, we utilise the existing COSMOS environment catalogue described in \citet{2017ApJ...837...16D} to ensure there are no environmental biases in our staging.
-
-Upon applying the matching described in Section \ref{data:environ}, we break our samples into different environment measures with stage.
-Figure \ref{fig:dens-stage} shows the distribution of our matched samples with their density values.
-It is important to note that \citet{2017ApJ...837...16D} has a higher mass cutoff than we have implemented in our underlying sample.
-Therefore, this is showing the density of all systems $\log$M$_*$/ M$_\odot \geq$ 9.6.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.45\textwidth]{figures/density-stage.pdf}
-    \caption{The density about each of our sources matched with the \citet{2017ApJ...837...16D} catalogue.
-As shown, there is no existing bias in the distribution of galactic environments throughout our stages.
-This is confirmed by performing KS- and AD-tests.
-Therefore, we can conclude that the shown evolution in SFR with interaction stage is not due to environmental effects.}
-    \label{fig:dens-stage}
-\end{figure}
-
-We conduct weighted KS and AD tests on the environment distributions, and confirm they are likely drawn from the same parent sample, with the resultant p-values $\approx$1 the distributions.
-Thus, there are no biases in our stage selection with environment, and it fair to assume that the evolution in the SFR with stage is due to interaction, not environment.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.45\textwidth]{figures/sfr-mass-density.pdf}
-    \caption{The distribution of environment classifications through our sample.
-This is only for sources with a $\log$M$_*$ / M$_\odot \geq$ 9.6.
-However, from this subsample, we see that there is no trend with environment and that the distribution is random throughout each stage.
-Therefore, the effects of increasing SFR with interaction stage is not due to environmental effects.}
-    \label{fig:dens-sfr-mass}
-\end{figure}
-
-Figure \ref{fig:dens-sfr-mass} shows the environment classification in our reduced stellar mass-SFR distribution.
-This shows that there is no ordered structure, or bias, in our sample with environment and further reinforces that the galactic environment is not responsible for our proposed SFR evolution with stage.
-The majority of our sample lie either within filaments or in the field.
-The environment which would have the most effect upon the SFRs of our sample is a cluster environment.
-However, the fraction of our sample within a cluster is never greater than 10\%.
-It is important to note, however, that the galaxies most likely to lie in a cluster in our sample would be lower mass galaxies.
-However, these systems are not found in the red sequence where we see the most change in SFR due to interaction.
-Therefore, the lack of information here does not have a large impact on this measurement.
+However, it is important to note that this result has been found with a sample of 676 interacting galaxies in their pairs.
+No merging stage galaxies have been represented and in numerous projected separation bins the counts are small enough to have conclusion altering error bars.
+Therefore, it is imperative that future works, with larger sample sizes not only look at the projected separation of the systems but the morphology as well.
 
 \section{Nuclear Activity with Interaction Stage}\label{results:AGN_stage}
-\noindent We now cross match our sample with the two AGN catalogues and methods described in Section \ref{sec:agn-clsf}.
-This provides us a sample of 1,361 AGN and star forming galaxies (SFGs).
+\noindent We now use our AGN sample matched with the AGN catalogues described in Chapter \ref{sec:agn-clsf}.
+As stated previously, we find matches of 1,361 AGN and star forming galaxies (SFGs).
 The breakdown of number of classifications per stage is shown in Table \ref{tab:agn-sfg-breakdown}.
@@
 We find no major changes in AGN with stellar mass or SFR with stage in our sample.
-Galaxies containing AGN appearing throughout the SFMS and red sequence across each stage.
+Galaxies containing AGN appear throughout the starburst, the SFMS and red sequence across each stage.
 There is no obvious bias in stellar mass or SFR for hosting an AGN.
-We do, however, see a concentration of AGN in stage 1 on the red sequence at higher masses.
-This shifts as we increase interaction stage, with the bulk of the AGN beginning to appear at lower masses in stages 3 and 4.
-Finally, in stage 4 we see AGN and SFGs distributed almost evenly across the star forming main sequence with little bias in distribution with mass.
-This hints at evolution with stage.
-
-Applying KS- or AD- tests these, however, reveals p-values close to 1 and therefore it is very likely that these distributions have been drawn from the same parent sample.
-However, due to the low counts of AGN and SFGs in our sample, using KS- and AD-tests to verify this is not optimal.
+We do, however, see a concentration of AGN in the separated stage on the red sequence at higher masses.
+This changes as we increase interaction stage, with the bulk of the AGN beginning to appear at lower masses in the apocentre and merging stages.
+Finally, in the merging stage we see AGN and SFGs distributed almost evenly across the star forming main sequence with little bias in distribution with mass.
+
+Applying KS or AD tests to these, however, reveals $p$-values close to 1 and therefore these distributions are consistent with being drawn from the same parent sample.
+However, due to the low counts of AGN and SFGs in our sample, using KS and AD tests to verify this is not optimal.
 Therefore, we instead investigate the global AGN fractions in our sample across different stages.
@@
 \centering
-    \includegraphics[width=0.45\textwidth]{figures/agn-stage-dist.pdf}
-    \caption{The distribution of AGN through stage with SFR and stellar mass. We do not find any major changes and evolution with AGN and SFG position through interaction stage. }
+\includegraphics[width=\columnwidth]{figures/agn-stage-dist.pdf}
+\caption[The distribution of AGN through stage with SFR and stellar mass.]{The distribution of AGN through stage with SFR and stellar mass.
+We find that the AGN populate every part of the SFR-M$_{*}$ parameter space probed in the pair sample.}
 \label{fig:agn-stage}
@@
 \begin{tabular}{|c|c|c|c|c|}
-         & Stage 1 & Stage 2 & Stage 3 & Stage 4 \\
+\hline
+& Separated & Pericentre & Apocentre & Merging \\
 \hline
 SFG & 135 & 212 & 337 & 199 \\
-        AGN & 103 & 117 & 163 & 95
+AGN & 103 & 117 & 163 & 95 \\
+\hline
 \end{tabular}
-    \caption{Breakdown in number of classified AGN and SFGs per stage.
-With our counts so low in this sample, it is difficult to make concrete conclusions about the evolution of AGN during interaction.}
+\caption{Breakdown in number of classified AGN and SFGs per stage. With our counts so low in this sample, it is difficult to make concrete conclusions about the evolution of AGN during interaction.}
 \label{tab:agn-sfg-breakdown}
@@
 \centering
-    \includegraphics[width=0.45\textwidth]{figures/agn-frac-time.pdf}
-    \caption{The change in AGN fraction with stage.
+\includegraphics[width=\columnwidth]{figures/agn-frac-time.pdf}
+\caption[The change in AGN fraction with stage.]{The change in AGN fraction with stage.
+The dotted line is the expected AGN fraction in the field (from \citet{2008AJ....135.1877E}).
 We define the AGN fraction as the ratio of number of confirmed AGN divided by the number confirmed AGN and SFGs in the sample.
 This is then weighted by the relevant sizes of each subsample and the number of unclassified sources in each.
-Errors on each point are found by bootstrapping.
-We do not include any sources of which we have no information.
-We find a sudden drop in AGN fraction from stage 1 to stage 2, followed by a rapid increase from stage 3 to 4.}
+Errors on each fraction are found as the confidence intervals defined via the beta distribution.
+We find a sudden drop in AGN fraction from the separated to pericentre stage, followed by a rapid increase from the apocentre to merging stage.}
 \label{fig:agn-frac-time}
@@
 Figure \ref{fig:agn-frac-time} shows the changing AGN fraction with interaction stage.
-We find that the AGN fraction generally remains static with stage.
-There is a small decrease increase from stage 1 to 2, followed by the fraction mostly remaining unchanged until stage 3.
-Then, in stage 4 we measure a large jump in the AGN fraction.
+The dotted line shows the expected fraction of AGN in the field from \citet{2008AJ....135.1877E}.
+We find that the AGN fraction generally remains at the fraction of the field through the separated to apocentre stages.
+There is a small decrease from the separated to pericentre stage, followed by the fraction mostly remaining unchanged until the apocentre stage.
+Then, in the merging stage we measure a large increase in the AGN fraction from $\approx0.12$ to $\approx0.15$, far above the expected field fraction.
 However, before we discuss this result further, we must point out that the large error bars on our measurements and the low number counts of confirmed AGN and SFG make this difficult to interpret.
-We measure the errors as the standard deviation about the mean in each stage.
-Thus, while our initial values show relatively little change, because of the large error bars, there could be increase with stage to even a further decline.
 
@@
 It is also difficult to use interaction stage as a proxy for the projected separation in this context.
-As shown previously, stages 2 and 3 have some overlap in the range of projected separations we have classified them into.
+As shown previously, the pericentre and apocentre stages have some overlap in the range of projected separations we have classified them into.
 Therefore, we also investigate any overlap between our confirmed pairs and the AGN fractions we see here.
 We find 104 AGN and 180 SFGs overlap with our confirmed pairs.
-This sample is far too small to breakdown further into different stages.
-Therefore, Figure \ref{fig:sfg-agn-proj} shows the change in density of AGN classifications and SFGs with increasing projected separation.
+Figure \ref{fig:sfg-agn-proj} shows the change in density of AGN classifications and SFGs with increasing projected separation.
 As expected, we find that with increasing projected separation the number of confirmed AGN and SFGs decreases.
@@
 The first is a peak in the projected separation distribution is from 0kpc-25kpc.
-The only contribution here is from stage 2 galaxies, which are close to pericentre.
-The second peak, from a projected separation of 30kpc - 60kpc is dominated by stage 3 galaxies, although some stage 1 AGN are in this peak as well.
-Finally, the third peak from 85 - 125kpc is representative of a mixture of stage 1 and stage 3 galaxies.
-None of our stage 4 galaxies which had their secondaries identified overlapped with our AGN and SFG identified sample.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.45\textwidth]{figures/sfg-agn-dist.pdf}
-    \caption{The distribution of both AGN and SFGs which have been cross matched with our confirmed galaxy pairs.
-While we find, as expected, the number of AGN and SFGs decreases with projected separation we find interesting structure within the AGN sample.
-Here, there appears to be a double peak in the number of counts of AGN.
-The first peak, between a projected separation of 0 and 25kpc is primarily from stage 2 galaxies while the second peak of 40 to 65kpc is of stage 3 galaxies in our sample.
-As shown in Figure \ref{fig:agn-frac-time}, we expect the fraction of AGN to be similar in these two stages while they are at very different times in the dynamical timescale of the interaction.
-The third peak, from 75 to 125kpc is only from stage 1 and stage 3 galaxies.}
+The only contribution here is from pericentre stage galaxies.
+The second peak, from a projected separation of 30kpc - 60kpc is dominated by apocentre stage galaxies, although some separated stage AGN are in this peak as well.
+Finally, the third peak from 85 - 125kpc is representative of a mixture of the separated and apocentre stage galaxies.
+None of our merging stage galaxies which had their secondaries identified overlapped with our AGN and SFG identified sample.
+
+\begin{figure}
+\centering
+\includegraphics[width=\columnwidth]{figures/sfg-agn-dist.pdf}
+\caption[The distribution of both AGN and SFGs which have been matched our confirmed galaxy pairs.]{The distribution of both AGN and SFGs which have matched our confirmed galaxy pairs.
+While we find, as expected, the number of AGN and SFGs decreases with projected separation we find an interesting double peak in the AGN sample.
+The first peak, between a projected separation of 0 and 25kpc is primarily from pericentre stage galaxies (in red) while the second peak of 40 to 65kpc is of apocentre stage galaxies (in yellow) in our sample.
+As shown in Figure \ref{fig:agn-frac-time}, we expect the fraction of AGN to be similar in these two stages despite being at different parts of the dynamical timescale in interaction.
+The third peak, from 75 to 125kpc is only from separated and apocentre stage galaxies.}
 \label{fig:sfg-agn-proj}
@@
 
-We find the AGN fraction only increases at the point of coalescence in interaction: stage 4.
+We find the AGN fraction only increases at the point of coalescence in interaction: the merging stage.
 This indicates that the mechanism driving AGN ignition in interaction is primarily at the point of the closest approach between the two systems.
 When we investigate the AGN number counts with respect to the projected separation of systems, we find that it gradually declines over the projected separation.
-However, we find two peaks; first clearly in stage 2 of the interaction where the galaxies are overlapping and secondly in the early parts of stage 3.
+However, we find two peaks; first clearly in the pericentre of the interaction where the galaxies are overlapping and secondly in the early parts of the apocentre stage.
 This could be evidence of a delayed AGN ignition depending on the underlying parameters of the interaction.
-Thus, \textbf{we find that the AGN fraction is generally unchanged with stage, however, the mechanisms responsible for an increase in the fraction primarily occur when the two systems are actually merging.
-We find evidence of a delay of ignition, as there is an increase in fraction at a early projected separations in stage 3}.
+Thus, we find that the AGN fraction is generally unchanged with stage, although the mechanisms responsible for an increase in the fraction primarily occur when the two systems are actually merging.
+We find evidence of a delay of ignition, as there is a peak in AGN counts at a small projected separations in the apocentre stage.
 
@@
 However, what this fails to capture is the larger complexity of interaction.
-Without morphological consideration, we are unable to tell whether galaxies at close projected separation are actually about to coalesce or are simply at the closest point of flying by each other.
+Without morphological consideration, we are unable to tell whether galaxies at small projected separations are actually at the closest point of flying by each other or about to coalesce.
 
 We find that throughout the different stages of interaction the SFR within the systems is increasing.
-Observations of interacting galaxies at various stages have found increased gas inflows into the nuclear regions of the galaxies which lead to enhancement in SFR there over their outer reaches \citep{2015A&A...579A..45B}.
+Observations of interacting galaxies at various stages have found increased gas inflows into the nuclear regions of the galaxies which lead to enhancement in the SFR at the galactic core over their outer reaches \citep{2015A&A...579A..45B}.
 This is often confirmed with deep observations of individual systems, which capture snapshots of different parts of the dynamical timescale of the interaction \citep{2022MNRAS.514.2769K}.
 Our study utilises numerous snapshots of the dynamical time of interaction in attempt to build a full picture of the change in SFR.
-We have found here is that this process of increasing SFR and galaxies being driven to starburst begins from the pericentre of interaction.
+We have found that this process increases the SFR of galaxies and that being driven to starburst begins from the pericentre of interaction.
 Multiple simulation works, which have the ability to model the entire dynamical history, show that this is to be expected \citep{2007A&A...468...61D, 2013MNRAS.430.1901H, 2015MNRAS.452.2984K, 2021MNRAS.503.3113M}.
 Often, these works show an initial dramatic increase in the SFR of interacting systems followed by an exponential decline through the dynamical time before increasing dramatically again at either a second passage or coalescence.
-\citet{2015MNRAS.448.1107M} is a direct example of this SF history through the merger history.
-
-Our results differ here as we do not find an exponential decrease in the SFR as move from stage 2 systems to stage 3 systems.
-As stated previously, observational work does support a continued increase in SFE in galaxies to projected separations of out to 80kpc - well into our defined stage 3 systems \citep[for further examples, see][]{2008MNRAS.385.1903L, 2012MNRAS.426..549S}.
-However, it is important to note that our stage 3 defined classification is a `wide net' that captures many systems that may be very soon after the initial passage in the dynamical timescale.
-The criteria defining stage 2 and stage 3 are simply that the galaxies must be no longer connected or overlapping morphologically with tidal features.
+\citet{2015MNRAS.448.1107M} is a direct example of this SF history through the interaction.
+
+Our results differ here as we do not find an exponential decrease in the SFR as move from the pericentre systems to the apocentre systems.
+As stated previously, observational work does support a continued increase in SFE in galaxies to projected separations of out to 80kpc - well into our defined apocentre stage systems \citep[for further examples, see][]{2008MNRAS.385.1903L, 2012MNRAS.426..549S}.
+However, it is important to note that our apocentre stage defined classification is a `wide net' that captures many systems that may be very soon after the initial passage in the dynamical timescale (recall Figure \ref{fig:illustration}).
+The criteria defining pericentre and apocentre stages are simply that the galaxies must be no longer connected or overlapping morphologically with tidal features.
 They must only be distinct and separate galaxies.
-Therefore, our found large enhancement in stage 3 may be from interacting systems which are only just out of the pericentre passage and not enough time has passed for the rapid decline in SFR to begin.
-
-Nonetheless, we still find a disappearance of the red sequence in stage 3 systems which may come as unexpected to when compared to simulations.
-It is important to note, however, that this is not the same as saying that a large proportion of the stage 3 systems are classified as starbursting galaxies.
-While previously mentioned simulations approximate an initial large starburst before rapid decline, we find the interacting galaxy population is pushed being quiescent / sub the star forming main sequence to being on the star forming main sequence.
+Therefore, our found large enhancement in the apocentre stage may be from interacting systems which are only just out of the pericentre passage and not enough time has passed for the rapid decline in SFR to begin.
+
+Nonetheless, we still find a disappearance of the red sequence in the apocentre systems which may come as unexpected to when compared to simulations.
+It is important to note, however, that this is not the same as saying that a large proportion of the apocentre systems are classified as starbursting galaxies.
+While previously mentioned simulations approximate an initial large starburst before rapid decline, we find the interacting galaxy population is pushed from being quiescent / sub forming main sequence to being on the star forming main sequence.
 Therefore, it may be more likely that the impact of interaction on star formation is not to suddenly cause rapid star formation in the aforementioned starburst before declining, but rather to gradually increase a galaxy's SFR up and into the blue cloud of galaxies.
-This could be supported by the surprising lack of rapidly quenched post-interaction galaxies found in both observations \citep{2017ApJ...845..145W} and simulations \citep{2020MNRAS.493.3716H, 2021MNRAS.504.1888Q}.
-\textbf{Thus, the impact of interaction on star formation is may not be a catastrophic increase in star formation that leads to quenching but, rather, a small increase in galaxies to use whatever gas they have into star formation}.
+This could be supported by the lack of rapidly quenched post-interaction galaxies found in both observations \citep{2017ApJ...845..145W} and simulations \citep{2020MNRAS.493.3716H, 2021MNRAS.504.1888Q}.
+Thus, the impact of interaction on star formation may not be a catastrophic increase in star formation that leads to quenching but, rather, a small increase in galaxies to use whatever gas they have into star formation.
 % Expand?
 
-This idea can be brought further forward by considering the large increase in starbursting galaxies we find when going from stage 2 / stage 3 to stage 4 galaxies.
-Stage 4 represents, in our sample, galaxies that are undergoing the final coalescence of the two systems involved.
+This idea can be brought further forward by considering the large increase in starbursting galaxies we find when going from pericentre / apocentre stage to the merging galaxies.
+The merging stage represents, in our sample, galaxies that are undergoing the final coalescence of the two systems involved.
 We find that the point of final coalescence leads to a large increase in the fraction of starbursting galaxies as well as the almost complete disappearance of the quiescent and sub-main sequence fraction of galaxies.
@@
 
-Thus, we can conclude, that for merging galaxies if gas is present within them, star formation will increase and change our classification of the galaxy.
+Thus, we can conclude that, for merging galaxies if gas is present within them, star formation will increase and change our classification of the galaxy.
 We will observe a sudden increase in the star formation rates of these systems followed by a rapid quenching as the gas is used up entirely.
-This is completely at odds when compared to galaxies that move into stage 3 and do not merge.
-These stage 3 systems will then slowly lose their enhancement over a long period of time, and return to star forming at their expected rate, whereas only moving into a stage 4 galaxy will lead to a starburst which may incur rapid quenching.
+This differs from galaxies that move into the apocentre stage and do not merge.
+These apocentre stage systems will then slowly lose their enhancement over a long period of time, and return to star forming at their expected rate, whereas only moving into a merging stage galaxy will lead to a starburst which may incur rapid quenching.
 
 Such a conclusion would also, therefore, explain the often quite large divide in the literature between whether interaction actually leads to enhancement or not.
-The only part of the interaction which actually causes the enhancement, and is the forking point, is that of stage 2 - where the two galaxies overlap and are at pericentre.
-From this point, if the galaxies then move off to stage 3 and escape, we will see a gradual decline in the SFE with the stage 3 galaxy only having a minor increase in its star formation classification.
-Whereas, if the galaxies move into a stage 4 interaction and merge, that is where we see the catastrophic results of a major starburst and the complete using and of all the gas in the systems.
+The only part of the interaction which causes the enhancement, and is the forking point, is the pericentre stage.
+From this point, if the galaxies then move off to the apocentre stage and escape, we will see a gradual decline in the SFE with the apocentre stage galaxy only having a minor increase in its star formation classification.
+Whereas if the galaxies move into the merging stage of the interaction and coalesce we see the results of a major starburst and the complete using and of all the gas in the systems.
 Thus, leading to a large fraction of quenched post-merger galaxies, but only after the initial coalescence.
@@
 There are multiple observational works that show this \citep{2007MNRAS.375.1017A, 2013MNRAS.435.3627E, 2020ApJ...904..107S} as well as works on cosmological simulations which support these conclusions \citep{2023MNRAS.519.4966B}.
-In simulations, the increased likelihood of nuclear ignition comes from the sudden increase in gas density in the galactic core which naturally leads to increased black hole accretion and ignition.
+In simulations, the increased likelihood of AGN activation comes from the sudden increase in gas density in the galactic core which naturally leads to increased black hole feeding, growth and nuclear activity.
 To satisfy these conditions, actual coalescence of the two systems are required.
-Observations of interacting galaxies are often interesting, as they contain examples of duel AGN and individual examples \citep[e.g.][]{2017MNRAS.470L..49E, 2021ApJ...923...36S} or investigate the increase in the AGN fraction in only the merger / post-merger stage \citep{2020A&A...637A..94G}.
+Observations of interacting galaxies are often interesting, as they contain examples of dual AGN and individual examples \citep[e.g.][]{2017MNRAS.470L..49E, 2021ApJ...923...36S} or investigate the increase in the AGN fraction in only the merger / post-merger stage \citep{2020A&A...637A..94G}.
 
@@
 This is supported with other works which specifically look at AGN fraction with projected separation \citep{2011MNRAS.418.2043E, 2023ApJ...942..107S}.
-However, we specifically find that the AGN fraction increases rapidly in stage 4 and holds quite constant between stages 1 to 3.
-This shows, again, shows two distinct effects of interaction which can colour our interpretation of the link between AGN and interaction.
-It appears, from our results, that the AGN fraction is driven up during the points in the dynamical time when the inner parts of the galaxy are majorly disturbed, and not by the simple movement of gas and dust into the core during the two galaxies passing each other.
+However, we specifically find that the AGN fraction increases rapidly in the merging stage and holds quite constant between the separated to apocentre stages.
+This shows two distinct effects of interaction which can colour our interpretation of the link between AGN and interaction.
+It appears from our results that the AGN fraction is driven up during the points in the dynamical time when the inner parts of the galaxy are majorly disturbed, and not by the simple movement of gas and dust into the core during the two galaxies passing each other.
 There is evidence that the onset of nuclear ignition from interaction may be delayed \citep{2011MNRAS.418.2043E}, or even flicker \citep{2015MNRAS.451.2517S} after ignition.
-Both of these possibilities are reflected distributions of AGN fraction with projected separation.
+Both of these possibilities are reflected in the double peaked distributions of AGN fraction with projected separation and the different times in the dynamical time these represent.
 
 Again, it is important to note the rather `wide net' that our stage classification takes.
-There is overlap between our stage 2 and stage 3 classifications at high stage 2 projected separation and low stage 3 projected separations.
+There is overlap between our pericentre and apocentre stage classifications at high pericentre projected separation and low apocentre projected separations.
 However, these stages naturally lead onto one another.
 Therefore, what see in the bi-modal distribution of AGN fraction with projected separation in Figure \ref{fig:sfg-agn-proj} are two peaks.
-The second of these peaks is at the cross over point of stage 2 to stage 3; the point at which (if the two galaxies have just flown by each other) a delayed AGN ignition could take place.
-This is also reflected in Figure \ref{fig:agn-stage} where we see a slight increase in AGN fraction in stage 3.
+The second of these peaks is at the cross over point of pericentre to apocentre; the point at which (if the two galaxies have just flown by each other) a delayed AGN ignition could take place.
+This is also reflected in Figure \ref{fig:agn-stage} where we see a slight increase in AGN fraction in the apocentre stage.
 This is likely from the ignition of nuclear activity taking place over a large period of time with a delay being involved from the initial flyby.
 
-We also see a dramatic increase in AGN fraction in stage 4 systems, where coalescence is just beginning or has occurred.
-Multiple works show that this is as expected.
+We see an increase in AGN fraction in the merging stage systems, where coalescence is just beginning or has occurred.
 \citet{2023MNRAS.519.4966B} has used cosmological simulations to show that we expect a large increase in AGN fraction at coalescence, and even for sometime into the post-merger phase.
 This is supported by measured AGN fractions in post-merger galaxies.
-Here, we see that the enhancement actually begins in stage 2, before the coalescence has even begun, but the actual coalescence is what sends it into overdrive.
-This is matches observations mentioned previously of increased gas densities in nuclear regions and cores, and that stage 4 is when this really occurs in earnest,
+This is matches both what we find and what observations mentioned previously of increased gas densities in nuclear regions and cores, and that the merging stage is when this really occurs in earnest,
 
 However, to more fully study this, we would need a larger sample of confirmed AGN and star forming galaxies from existing photometry or catalogues to make more decisive conclusions based on stage.
-In this work, we were limited to a small number of AGN and star forming galaxies across each stage.
+In this Chapter, we were limited to a small number of AGN and star forming galaxies across each stage.
 When compared to our paired sample, we do not have the numbers to also divide into stage again.
@@
 \noindent In this work, we investigate the evolution of multiple parameters and processes in galaxy interaction with interaction stage.
-We use the \citet{2023ApJ...948...40O} catalogue of interacting galaxies and cross match it with the COSMOS survey to gain ancillary data.
-This gives us a sample of 4,135 interacting galaxies of which 960 have a confirmed secondary from available photometric redshift data.
+We use the interacting galaxy catalogue created in Chapter \ref{chapter2} and match it with the COSMOS survey to gain ancillary data.
+This gives us a flux limited sample of 4,181 interacting galaxies of which 834 have a confirmed secondary from available photometric redshift data.
+We apply a mass limit to our sample, reducing it to 3,384 galaxies with 676 pairs.
 We use visual morphology as well as angular separation to split our sample into four distinct stages: (1) close pair, (2) morphologically disturbed and overlapping, (3) morphologically disturbed and distinct, (4) merging.
 Each stage is designed to capture a different part of the dynamical timescale of the interaction.
-We then cross match these samples with existing catalogues of environment and active galactic nuclei for further study.
+We then match these samples with existing catalogues of environment and active galactic nuclei for further study.
 
@@
 We conduct Kolmogorov-Smirnov and Anderson-Darling tests to show the mass distribution of our sample does not change with stage, while the star formation rate changes dramatically.
-This change in star formation rate from stage 1 to 4 is found in the red sequence of galaxies reducing to the point of disappearance.
+This change in star formation rate from the separated to merging stages is found in the red sequence of galaxies reducing to the point of disappearance.
 This is further confirmed by sub-classifying each sampled stage into starbursting, main sequence and quiescent galaxies.
-We find that as the galaxies move from stage 1 to stage 2 the fraction of starbursting galaxies increases while the quiescent galaxy fraction reduces.
-In stage 4, the starbursting fraction increases dramatically while almost no quiescent galaxies exist in the sample.
-This implies that the mechanisms responsible for enhancement in star formation in interacting galaxies is dominant from stage 1 to stage 2 and in the final coalescence of the system.
+We find that as the galaxies move from the separated to pericentre stages the fraction of starbursting galaxies increases while the quiescent galaxy fraction reduces.
+In the merging stage, the starbursting fraction increases dramatically while almost no quiescent galaxies exist in the sample.
+This implies that the mechanisms responsible for enhancement in star formation in interacting galaxies is dominant from separated to pericentre stages and in the final coalescence of the system.
 We find that, for all of our galaxies, some enhancement in star formation is observed.
@@
 We find, across the whole subsample, a general increase in star formation efficiency as we move to smaller projected separation.
-The highest found enhancement is below 10kpc.
-However, when broken down into their constituent stages, we find dramatically different behaviour in the star formation efficiency.
-This is best seen in stage 2 enhancement, which does not seem to change with projected separation, while there is a dramatic decrease in stage 3 enhancement from 2.5 at 10kpc down to 1.2 at 100kpc.
+The highest found enhancement is below $10~\mathrm{kpc}$.
+However, when broken down into their constituent stages, we find different behaviour in the star formation efficiency.
+This is best seen in the pericentre stage enhancement, which does not seem to change with projected separation while remaining enhanced.
+There is a dramatic decrease in the pericentre stage enhancement from 2.2 at $10~\mathrm{kpc}$ down to 1.0 at $100~\mathrm{kpc}$.
 This shows that just using projected separation as a proxy for stage will leave out crucial information to the underlying causes and mechanisms fueling star formation enhancement.
@@
 While the results with projected separation are not unexpected, those with the different stages are.
-We have shown that one cannot simply use the projected separation of interacting galaxies as a proxy for the stage of the interaction.
+We have shown the use of projected separation of interacting galaxies as a proxy for the stage of the interaction may miss crucial information.
 We find very different behaviour in the star forming behavior of interacting galaxies based on stage which are at in the dynamical timescale of the interaction.
-We find the beginning of an enhancement in star formation occurs in stage 2, where the two galaxies are moving past each other at pericentre.
-Then, through to stage 3, the enhancement remains although with no further increase.
-There is then another dramatic starburst in stage 4, where the two galaxies actually begin to undergo the merging processes.
+We find the beginning of an enhancement in star formation occurs in the pericentre stage.
+Then, through to the apocentre stage, the enhancement remains although with no further increase.
+There is then another dramatic starburst in the merging stage, where the two galaxies actually begin to undergo the coalescence processes.
 
@@
 This is also particularly true of the relation between active galactic nuclei and the interaction stage, where we are unable to have the sample size to definitively draw conclusions from our results.
+We also require numerical models to better identify the point in the dynamical timescale an interacting system is.
+This would lead to reliable constraints on the relations we have explore in this Chapter.
+We present our work on building such an algorithm in the following Chapter.
+This algorithm is focused on constraining both the dynamical timescale of the interaction and the full set of underlying parameters needed to describe a galaxy interaction.
 

### 2024-06-14 paper-source/main.tex
Major updates to code. Need to update paper as well. Thesis subitted with everything looking good.

@@
 % Keep the title short and informative.
-\title[Interactions in COSMOS]{When do the effects of interaction happen? Interacting and disturbed galaxies in the COSMOS field}
+\title[Timescales of Interaction]{Timescales for the Effects of Interactions on Galaxy Properties and SMBH Growth}
 
@@
 % If you need two or more lines of authors, add an extra line using \newauthor
-\author[D. O'Ryan et al.]{
-David O'Ryan$^{1}$\thanks{E-mail: d.oryan@lancaster.ac.uk}
+\author[D. O'Ryan et al.]{David O'Ryan$^{1}$\thanks{E-mail: \href{mailto:d.oryan@lancaster.ac.uk}{d.oryan@lancaster.ac.uk}},
+    Brooke Simmons$^{1}$,
+    COSMOS Team,
+    GZ Team, 
+    \newauthor
+    Others from OR+23,
 \\
@@
 \begin{abstract}
-   Galaxy interaction and merging have fundamental impacts on galactic evolution.
-From increases in star formation, to morphology, to activation of nuclear activity, galaxy interaction is thought to play a role.
-However, at what point in the interaction do these effects occur?
-In this work, we divide a large sample of interacting galaxies in the COSMOS field into four distinct stages based on their interaction morphology.
+   Galaxy interactions and mergers fundamentally impact galaxy evolution in multiple ways.
+At what point in the interaction do these effects occur?
+In this work, we divide a large sample of interacting galaxies observed by the Hubble Space Telescope into four distinct stages based on their interaction morphology.
 Each stage captures a different part of the dynamical timescale of interaction.
-We then probe the relation between stage, mass, star formation, and nuclear activity.
+We select a sample of 4,181 interacting and merging systems in the COSMOS field, using the rich ancillary data available in this field to probe the relation between merger stage, stellar mass, star formation rate, and AGN activity.
 We find that the distribution of star formation rates rapidly changes with stage for an equivalent mass distribution.
-We find a shrinking red sequence with stage, and an increase in the fraction of starburst galaxies from 0.1 as close pairs to 0.38 at the point of coalescence.
+We find a shrinking red sequence with stage, and an increase in the fraction of starburst galaxies from 10\% as close pairs to 32\% at the point of coalescence.
 We also find that the fraction of active galactic nuclei is static through most of the interaction, until it increases at coalescence.
-We discuss these results, and compare them with the more prevalent stage diagnostic of projected separation between galaxy pairs.
+We compare these results with the more prevalent stage diagnostic of projected separation between galaxy pairs.
 We find morphology and stage dependence in the rate of star formation which is not captured by using the projected separation.
 We show that the point in time of the underlying dynamical timescale an interaction occupies is as important to consider as its projected separation.
-
 \end{abstract}
@@
 \section{Introduction}\label{introduction}
-\noindent To fully map out the effect of galaxy interaction, we must understand its impact through various merger histories and across the full dynamical timescale of the interaction.
+\noindent Galaxy interaction and merging is of fundamental importance to our current theories of galaxy formation and evolution.
+Our current cosmological theory, $\Lambda$CDM, dictates that structure is expected to form and assemble hierarchically \citep{1978MNRAS.183..341W, 2001MNRAS.328..726S, 2013MNRAS.436.1765M}.
+Thus, understanding the underlying processes that occur in galaxy interaction and merging is paramount to understanding cosmological theories.
+It is well known that many underlying processes are triggered or enhanced due to galaxy interaction.
+The clearest result of interaction is the disruption of galactic morphology, the acceleration of disks to spheroidal systems and the formation of tidal features \citep{1972ApJ...178..623T, 1977ApJ...212..616T, 2005MNRAS.357..753G, 2009MNRAS.397..802H}, increases in star formation rates when compared to the general galaxy population \citep{1991ApJ...370L..65B, 2006ApJ...652...56B, 2014MNRAS.437.2137S, 2015ApJ...807L..16K} and, potentially, their rapid quenching \citep{2013MNRAS.430.1901H, 2023RAA....23i5026D}.
+There is also evidence to suggest that interaction plays a role in the ignition of active galactic nuclei (AGN) \citep{2011MNRAS.418.2043E, 2015ApJ...806..219C, 2023MNRAS.523.4164H}.
+Therefore, with interaction having such an affect on the galaxies we see - over a long time period - understanding galaxy interaction is fundamental to understanding galaxy evolution.
+
+To fully map out the effect of galaxy interaction, we must understand its impact through various merger histories and across the full dynamical timescale of the interaction.
 The dynamical timescale is the full time of the interaction, from the two galaxies approaching each other to flying by and escaping or merging.
@@
 
-While cannot directly measure the full dynamical timescale for individual systems, we can create large samples of interacting galaxies contain systems spanning the full dynamical history.
+While we cannot yet directly measure the full dynamical timescale for individual systems, we can create large samples of interacting galaxies contain systems spanning the full dynamical history.
 Attempts to create such a sample have been either by machine learning classification \citep{2019A&A...626A..49P, 2023A&A...669A.141S}, visual classification by citizen scientists \citep{2010MNRAS.401.1043D} or by photometric parameterisation \citep{2004AJ....128..163L, 2023MNRAS.522....1N}.
@@
 
-In this Chapter, we split our large sample of interacting galaxies found in Chapter \ref{chapter2} into four specific stages based on their morphology.
+In this work, we split our large sample of interacting galaxies found in \citet[][hereafter OR23]{2023ApJ...948...40O} into four specific stages based on their morphology.
 Each stage is designed to capture different parts of the dynamical time of an interaction.
@@
 
-This Chapter is laid out as follows in Chapter \ref{data} we briefly summarise the COSMOS catalogue, and describe the process of catalogue matching especially focused on accurate de-duplication and cross-matching.
-Chapter \ref{method} describes the methods by which we split the interacting systems into stages, and how we identify the secondary galaxies in each pair.
+This paper is laid out as follows in Section \ref{data} we briefly summarise the COSMOS catalogue, and describe the process of catalogue matching especially focused on accurate de-duplication and cross-matching.
+Section \ref{method} describes the methods by which we split the interacting systems into stages, and how we identify the secondary galaxies in each pair.
 In Sections \ref{results:SF_stage} and \ref{results:AGN_stage} we show our results of star formation and active galactic nuclei evolution with interaction stage and present an initial discussion.
-These are followed in Chapter \ref{discussion} where we compare to previous works and put our results in the context of the field.
-Finally, in Chapter \ref{conclusion} we make concluding remarks and discuss future work to better our constraints.
+These are followed in Section \ref{discussion} where we compare to previous works and put our results in the context of the field.
+Finally, in Section \ref{conclusion} we make concluding remarks and discuss future work to better our constraints.
 
@@
 For the stellar mass we use the best fit \texttt{LePhare} measurement and for the star formation rates we use the best fit \texttt{EAzY}/\texttt{FAST} measurements.
-We compare the output masses and SFRs for our sources in Figure \ref{fig:difference-measures}.
-As shown, there can be wide scatter and disagreement between the two algorithms.
-We tested different combinations of \texttt{EAzY} and \texttt{LePhare} stellar masses and SFRs to find which would be best to use in this work.
 We found that using the same algorithm in both parameters revealed the degeneracies of using discrete templates to fit the broad band photometry in the underlying parameter space.
 Therefore, we elect to inter-mix the algorithms and use the best fit \texttt{LePhare} stellar mass and best fit \texttt{EAzY} SFR measurement.
-
-\begin{figure}
-\centering
-\includegraphics[width=\columnwidth]{figures/mass-sfr-scatter.pdf}
-\caption[Comparison of the measures of stellar mass and SFR using either \texttt{LePhare} or \texttt{EAzY}/\texttt{FAST} photometric codes to calculate them.]{Comparison of the measures of stellar mass and SFR using either \texttt{LePhare} or \texttt{EAzY}/\texttt{FAST} photometric codes to calculate them.
-If the algorithms agreed perfectly, the sources would lie on the blue 1:1 line.
-\textit{Left}: The scatter in the stellar masses between softwares.
-As shown, \texttt{EAzY} often seems to find larger stellar masses when compared to \texttt{LePhare}.
-\textit{Right}: Scatter in SFRs when measured with \texttt{LePhare} or \texttt{EAzY}.}
-\label{fig:difference-measures}
-\end{figure}
 
@@
 Beyond this redshift, we find that identification of tidal features becomes difficult due to surface brightness dimming and we risk mis-identifying the stages of the interacting galaxies.
-This also matches the redshift cut applied to the environment catalogue we cross match with in Chapter \ref{data:environ}.
+This also matches the redshift cut applied to the environment catalogue we cross match with in Section \ref{data:environ}.
 Applying these cuts reduces our sample size to 3,689 interacting galaxies.
@@
 \subsection{Secondary Identification}\label{sec:sec-ident}
-\noindent As the catalogue described in Chapter \ref{chapter2} only contains source coordinates and IDs, we must also manually identify the secondaries of many of our interacting systems.
+\noindent As the catalogue described in OR23 only contains source coordinates and IDs, we must also manually identify the secondaries of many of our interacting systems.
 To find the secondaries, we apply three steps.
@@
 Each cutout had a 30" radius (corresponding to 1001 $\times$ 1001 pixels).
-The original cutout from Chapter \ref{chapter2} was also displayed next to the enlarged cutout.
+The original OR23 cutout was also displayed next to the enlarged cutout.
 We annotate each cutout with each sources COSMOS2020 ID and measured photometric redshift and error.
@@
 The tidal features connecting the systems or coalescing systems would only be identified under one ID in the catalogue.
-Figure \ref{fig:secondary_selection} panel C) shows an example of two systems being close enough together that they have been identified under a single COSMOS2020 entry.
-Figure \ref{fig:secondaries_found} shows this disparity with the different types of interaction we observe.
-
-\begin{figure}
-\centering
-\includegraphics[width=\columnwidth]{figures/visualisation_classification.pdf}
-\caption[Where a secondary could be identified at different stages in the interaction.]{Where a secondary could be identified at different stages in the interaction.
+Figure \ref{fig:secondary_selection}c shows an example of two systems being close enough together that they have been identified under a single COSMOS2020 entry.
+
+% \begin{figure}
+    % \centering
+    % \includegraphics[width=\columnwidth]{figures/visualisation_classification.pdf}
+    % \caption[Where a secondary could be identified at different stages in the interaction.]{Where a secondary could be identified at different stages in the interaction.
 The reasoning for such disparity in secondaries identified is due to the relative distance each the secondary would be from the primary at each stage.
@@
 When the secondary was near apocentre, often it would be outside the cutout we were using for visual classification.}
-\label{fig:secondaries_found}
-\end{figure}
+    % \label{fig:secondaries_found}
+% \end{figure}
 
@@
 We also confirm that it does not already exist in the catalogue, and ensure there is no duplication in the control sample.
-Figure \ref{fig:matched-distributions} shows the mass distribution of our paired sub-sample of galaxies and their control, showing a mass distribution which is approximately the same as the interacting sample.
 With the previously defined cuts, we find a control galaxy for all but one of our interacting galaxies.
 
-\begin{figure}
-\centering
-\includegraphics[width=\columnwidth]{figures/mass-matching-pairs.pdf}
-\caption[The mass distribution of the paired interacting galaxy sample and the control sample.]{The mass distribution of the paired interacting galaxy sample and the control sample.
+% \begin{figure}
+    % \centering
+    % \includegraphics[width=\columnwidth]{figures/mass-matching-pairs.pdf}
+    % \caption[The mass distribution of the paired interacting galaxy sample and the control sample.]{The mass distribution of the paired interacting galaxy sample and the control sample.
 Both primary and secondary galaxies are within this distribution.}
-\label{fig:matched-distributions}
-\end{figure}
+    % \label{fig:matched-distributions}
+% \end{figure}
 
@@
 Our selection process was built to only find a primary and secondary galaxy and, therefore, we add these extra systems into our sample manually.
-Other interacting galaxies that were added were low redshift systems which would have appeared to completely fill the cutout of the classification process in Chapter \ref{chapter2}.
+Other interacting galaxies that were added were low redshift systems which would have appeared to completely fill the cutout of the classification process in OR23.
 By looking at the larger COSMOS2020 cutouts, we are able to recover these galaxies and add them to this sample.
@@
 First, this is the lowest mass system which is still observed in our the coalescing sample at $z = 1.2$.
-The second reason is that such a mass cut is approximately the one made in the environment catalogue we will describe later in Chapter \ref{data:environ}.
+The second reason is that such a mass cut is approximately the one made in the environment catalogue we will describe later in Section \ref{data:environ}.
 There we make a cut of $\log(\frac{M}{M_\odot}) \geq 9.6$, we find that decreasing the mass cut to $\log(\frac{M}{M_\odot}) \geq 9.25$ does not make major differences to our results.
@@
 
-Throughout this Chapter, we will use our mass-limited sample in our analysis.
+Throughout this paper, we will use our mass-limited sample in our analysis.
 This gives us uniform sensitivity across our volume.
-However, we also conducted the same analysis described below with the flux-limited sample and the qualitative conclusions of this Chapter did not change.
+However, we also conducted the same analysis described below with the flux-limited sample and the qualitative conclusions of this paper did not change.
 
 \subsection{Sample Count Summary}\label{sec:sample-summary}
-\noindent Thus, to briefly sumarise this chapter, we have applied multiple cuts and additions to our initial sample of interacting galaxies.
+\noindent Thus, to briefly summarise this Section, we have applied multiple cuts and additions to our initial sample of interacting galaxies.
 We have gone from an initial sample of 3,689 matched galaxies with COSMOS to a mass-limited sample of 3,384 galaxies.
@@
 Each stage covers a different part of the dynamical history in an interaction and, in this case, we define it based on the morphology and projected separation between systems.
-We have already encountered the four stages we will investigate in Figures \ref{fig:matched-distributions} and \ref{fig:redshift_selection} and now define a short hand name to refer to them as well as fully describe the part of the dynamical history they represent.
+We have already encountered the four stages we will investigate in Figure \ref{fig:redshift_selection} and now define a short hand name to refer to them as well as fully describe the part of the dynamical history they represent.
 These are:
@@
 
-Figure \ref{fig:stages} shows the original source cutouts used in Chapter \ref{chapter2} to give an example of each stage.
+Figure \ref{fig:stages} shows the original source cutouts used in OR23 to give an example of each stage.
 There are degeneracy's associated with this staging system, however.
@@
 Figure \ref{fig:illustration} shows the branching paths that the galaxies can take through each stage.
-These images are created using the Advanced Python Stellar Animation Module restricted numerical simulation, described in Chapter \ref{chapter4}, and are for illustrative purposes only here.
+These images are created using the Advanced Python Stellar Animation Module restricted numerical simulation, described in O'Ryan et al., in prep, and are for illustrative purposes only here.
 
@@
 If they do not have enough energy, the system will return to the pericentre stage of the encounter and then begin to coalesce in the merging stage.
-Images are from the Advanced Python Stellar Particle Animation Module interacting galaxy algorithm described in Chapter \ref{chapter4} and based on the stellar particle animation module algorithm described in \citet{2016A&C....16...26W}.}
+Images are from the Advanced Python Stellar Particle Animation Module interacting galaxy algorithm described in O'Ryan et al., in prep and based on the stellar particle animation module algorithm described in \citet{2016A&C....16...26W}.}
 \label{fig:illustration}
@@
 % Need to integrate this figure.
-\begin{figure*}
-\centering
-\includegraphics[width=\textwidth]{figures/redshift-proj-sep-diagnostic.pdf}
+\begin{figure}
+\centering
+\includegraphics[width=\columnwidth]{figures/redshift-proj-sep-diagnostic.pdf}
 \caption[The measured distribution of projected separation with redshift.]{The measured distribution of projected separation with redshift.
@@
 \label{fig:proj-seps-limits}
-\end{figure*}
+\end{figure}
 
@@
 Such a measure is often calculated in numerous ways, such as the N-nearest neighbour \citep{2006MNRAS.373..469B}, different Bayesian metrics \citep{2008ApJ...674L..13C} or estimating it from Voronoi Tesselation \citep{2021inas.book...57V}.
-However, in this Chapter, we use the existing environmental density catalogue produced by \citet{2017ApJ...837...16D}.
+However, in this Section, we use the existing environmental density catalogue produced by \citet{2017ApJ...837...16D}.
 This catalogue was created specifically for the COSMOS survey, and has a measured density for all sources with mass $\log(\frac{M}{M_\odot}) \geq 9.6$ and $z \leq 1.2$.
@@
 The result of this process, and the cuts defined previously, is a catalogue of $\approx$45,000 galaxies with their densities accurately measured.
-We remove any sources which are flagged as uncertain from the catalogue (a flag in it) providing us with $\approx$39,000 sources with which to cross match the sample from Chapter \ref{chapter2}.
+We remove any sources which are flagged as uncertain from the catalogue (a flag in it) providing us with $\approx$39,000 sources with which to cross match the sample from OR23.
 We apply the same cuts to our sample as applied in \citet{2017ApJ...837...16D}, and only consider those systems with a mass $\log(\frac{M}{M_\odot}) \geq 9.6$.
@@
 
-\begin{figure}
-\centering
-\includegraphics[width=\columnwidth]{figures/redshift_scatter.pdf}
-\caption[The scatter in photometric redshifts of our paired sample.]{The scatter in photometric redshifts of our paired sample.
+% \begin{figure}
+% \centering
+% \includegraphics[width=\columnwidth]{figures/redshift_scatter.pdf}
+% \caption[The scatter in photometric redshifts of our paired sample.]{The scatter in photometric redshifts of our paired sample.
 Left shows the scatter in the primary and secondary photometric redshift measurements.
@@
 As shown, the bulk of the sample lies within this region.}
-\label{fig:redshift-scatter}
-\end{figure}
+% \label{fig:redshift-scatter}
+% \end{figure}
 
 To investigate the affected systems, we therefore look at the redshift distribution of our paired sample.
-Figure \ref{fig:redshift-scatter} shows the scatter in our found pairs as well as the difference between them from our visual classification.
 During the visual classification, we instituted a cut that each interacting pair must be within a photometric redshift difference of $\pm0.1$.
@@
 Therefore, we are unlikely to have removed a large percentage of interacting galaxies due to the photometric redshift error and the cuts we have applied.
-
-The resultant scatter in photometric redshifts between the primary and secondary in our paired sample is shown on the left panel of Figure \ref{fig:redshift-scatter}.
-The right hand panel shows the distribution of the difference measured between the primary and secondary photo-$z$s, with the red dashed lines showing the maximum expected error on the photometric redshift measurement at the highest redshift of our sample.
-As shown, the bulk of our paired sample lies at very low redshift difference, meaning we are unlikely to have removed too many systems.
-This leads us to conclude that our pair selection process has been robust.
 
@@
 To check this, we measure the distributions of our galaxies in each environment with stellar mass.
-We use the sample matched to \citet{2017ApJ...837...16D} as described in Chapter \ref{data:environ}.
-
-Figure \ref{fig:dens-stage} shows the distribution of our matched samples with their density values with Figure \ref{fig:environ-fract} showing the change in environment fraction with stage.
+We use the sample matched to \citet{2017ApJ...837...16D} as described in Section \ref{data:environ}.
+
+Figure \ref{fig:environ-fract} shows the change in environment fraction with stage.
 It is important to note that \citet{2017ApJ...837...16D} has a higher mass cutoff than we have implemented in our underlying sample.
@@
 
-\begin{figure}
-\centering
-\includegraphics[width=\columnwidth]{figures/density-stage.pdf}
-\caption[The density about each of our sources matched with the \citet{2017ApJ...837...16D} catalogue.]{The density about each of our sources matched with the \citet{2017ApJ...837...16D} catalogue.
+% \begin{figure}
+    % \centering
+    % \includegraphics[width=\columnwidth]{figures/density-stage.pdf}
+    % \caption[The density about each of our sources matched with the \citet{2017ApJ...837...16D} catalogue.]{The density about each of our sources matched with the \citet{2017ApJ...837...16D} catalogue.
 As shown, there is no existing bias in the distribution of galactic environments throughout our stages.
 Therefore, that we have identified primarily tidal affects and not environmental ones.}
-\label{fig:dens-stage}
-\end{figure}
+    % \label{fig:dens-stage}
+% \end{figure}
 
@@
 These are separated into our previously defined interaction stages and the interaction type (based on mass ratio).
-We find that, overwhelmingly, our sample is dominated by micro and minor interactions.
-These are where the two systems have very different stellar masses.}
+We find that, overwhelmingly, our sample is dominated by micro and minor interactions (where the mass ratio is $<$1:10).}
 \label{fig:mass-ratio}
@@
 Another effect that could cause this relation to appear would be our selection was highly dependent on galactic environment.
-However, we have already explored this possibility in Chapter \ref{data:environ} and found no bias in environment between the stages.
+However, we have already explored this possibility in Section \ref{data:environ} and found no bias in environment between the stages.
 Therefore, this is likely not the cause of this decrease in the red sequence population.
@@
 
-\begin{figure}
-\centering
-\includegraphics[width = \columnwidth]{figures/stellar-mass-dist.pdf}
-\caption[The stellar mass distribution across the four stages.]{The stellar mass distribution across the four stages.
-Each bin is weighted based on the counts in the smallest sub-sample in stage: the merging stage of the interaction.}
-\label{fig:weighted-mass}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=\columnwidth]{figures/sfr_dist.pdf}
-\caption[SFR distribution weighted by mass across each stage.]{SFR distribution weighted by mass across each stage. This weighting is based on our sample of merging stage.}
-\label{fig:weighted-sfr}
-\end{figure}
-
-Figure \ref{fig:weighted-mass} shows the weighted mass distributions through the four different stages.
+\begin{figure*}
+    \centering
+    \includegraphics[width = \textwidth]{figures/mass_sfr_dist_comb.pdf}
+    \caption[The stellar mass distribution across the four stages.]{The distributions of mass and star formation with stage.
+\textit{Left}: The stellar mass distribution across the four stages.
+Each bin is weighted based on the counts in the smallest sub-sample in stage: the merging stage of the interaction.
+The weighting is designed to control for mass across the samples, for cleaner comparison of other properties.
+\textit{Right}: SFR distribution weighted by mass across each stage.
+This weighting is based on our sample of merging stage.}
+    \label{fig:weighted-mass-sfr}
+\end{figure*}
+
+The left panel of Figure \ref{fig:weighted-mass-sfr} shows the weighted mass distributions through the four different stages.
 These appear similar, however, to statistically measure the similarity we apply our KS- and AD-tests to them.
@@
 
-Figure \ref{fig:weighted-sfr} shows the SFR distributions while being weighted by stellar mass.
+The right panel of Figure \ref{fig:weighted-mass-sfr} shows the SFR distributions while being weighted by stellar mass.
 When comparing the separated and pericentre, separated and apocentre, separated and merging, pericentre and merging and apocentre and merging stages, the $p$-values are $\ll$0.05.
@@
 We expect that, due to an interaction, the population of starbursting and quiescent galaxies will change.
-Therefore, we define a star forming main sequence (SFMS) across redshift.
-This allows us to classify each source based on its SFR independently of redshift.
-To define the star forming main sequence, we follow the example of \citet{2019MNRAS.484.4360A}.
-There, they define the star forming main sequence as a function of galactic stellar mass and redshift as
-
-\begin{equation}
-\log \text{SFR}_{\text{MS}}(z)[M_\odot yr^{-1}] = -7.6 + 0.76\log\frac{M_*}{M_\odot} + 2.95\log(1+z).
-\end{equation}
-
-\noindent This finds the expected main sequence SFR of a galaxy at a given stellar mass, $M_*$, and redshift, z.
-
-The ratio of the measured galaxy SFR and the expected main sequence SFR is then taken. We then use this fraction to classify each galaxy into distinct bins. These bins are:
-
-\begin{enumerate}[(i)]
-    \item Starburst galaxies. Here, the galaxy SFR is highly elevated compared to the SFMS. We follow \citet{2019MNRAS.484.4360A} and define a cutoff of $\log$ SFR/SFR$_{\text{MS}} >$ 0.4.
-    \item Main sequence galaxy. The galaxy is within 0.4 dex of the SFMS and approximately has the expected SFR. Defined as $-0.4 < \log$ SFR/SFR$_{\text{MS}} < 0.4$.
-    \item Sub-main sequence galaxy. A galaxy whose SFR is below the majority of the SFMS, but likely not quiescent. Defined as $-1.3 < \log$ SFR/SFR $_{\text{MS}} < $ -0.4.
-    \item Quiescent (High) galaxy. A galaxy with an SFR in the top $\approx$50\% of the quiscent galaxy population. Defined as $-2.3 < \log$ SFR/SFR $_{\text{MS}} <$ -1.3.
-    \item Quiescent (Low) galaxy. A galaxy with low SFR and very likely completely quenched. Defined as $\log$ SFR/SFR$_{\text{MS}} <$ -2.3.
-\end{enumerate}
-
-\noindent We split our sample into its different stages and apply these criteria.
+We adopt the mass- and redshift-dependent star-forming classifications of \citet{2019MNRAS.484.4360A} for all galaxies in our system.
+In total, we have 620 Starburst (SB) galaxies, 2,005 Main Sequence (MS) galaxies, 540 Sub-MS galaxies, 239 Quiescent galaxies (of which 149 are "High" Quiescent galaxies and 90 are "Low" Quiescent galaxies according to the criteria described in \citet{2019MNRAS.484.4360A}).
+
 Figure \ref{fig:sfr-clsf} shows the ratio between the expected SFMS SFR and the measured SFR in COSMOS2020.
@@
 
-To measure the SFE of our galaxy pairs, we directly compare to the mass- and redshift-matched control sample that was also created with this sub-sample and defined in Chapter \ref{sec:sec-ident}.
+To measure the SFE of our galaxy pairs, we directly compare to the mass- and redshift-matched control sample that was also created with this sub-sample and defined in Section \ref{sec:sec-ident}.
 We separate our galaxy pairs into different bins based on the projected separation between them.
@@
 On the left of the plot, we have the distribution for the full galaxy pair sample, without taking account of stage.
-The errors on our measurements are following the methodology of \citet{2011PASA...28..128C} and briefly described in Chapter \ref{results:int_stage}.
+The errors on our measurements are following the methodology of \citet{2011PASA...28..128C} and briefly described in Section \ref{results:int_stage}.
 The dashed black line represents no enhancement in SFR, as the average SFR in the interacting galaxy sample would be equal to the average SFR in the control sample.
@@
 \section{Nuclear Activity with Interaction Stage}\label{results:AGN_stage}
-\noindent We now use our AGN sample matched with the AGN catalogues described in Chapter \ref{sec:agn-clsf}.
+\noindent We now use our AGN sample matched with the AGN catalogues described in Section \ref{sec:agn-clsf}.
 As stated previously, we find matches of 1,361 AGN and star forming galaxies (SFGs).
 The breakdown of number of classifications per stage is shown in Table \ref{tab:agn-sfg-breakdown}.
-Figure \ref{fig:agn-stage} shows distribution of stellar mass to SFR with stage, with the confirmed AGN and SFGs marked.
 We find no major changes in AGN with stellar mass or SFR with stage in our sample.
@@
 
-\begin{figure}
-\centering
-\includegraphics[width=\columnwidth]{figures/agn-stage-dist.pdf}
-\caption[The distribution of AGN through stage with SFR and stellar mass.]{The distribution of AGN through stage with SFR and stellar mass.
+% \begin{figure}
+%     \centering
+%     \includegraphics[width=\columnwidth]{figures/agn-stage-dist.pdf}
+%     \caption[The distribution of AGN through stage with SFR and stellar mass.]{The distribution of AGN through stage with SFR and stellar mass.
 We find that the AGN populate every part of the SFR-M$_{*}$ parameter space probed in the pair sample.}
-\label{fig:agn-stage}
-\end{figure}
+%     \label{fig:agn-stage}
+% \end{figure}
 
@@
     \end{tabular}
-\caption{Breakdown in number of classified AGN and SFGs per stage. With our counts so low in this sample, it is difficult to make concrete conclusions about the evolution of AGN during interaction.}
+    \caption{Breakdown in number of classified AGN and SFGs per stage.
+With our counts so low in this sample, it is difficult to make concrete conclusions about the evolution of AGN during interaction.}
     \label{tab:agn-sfg-breakdown}
@@
     \caption[The change in AGN fraction with stage.]{The change in AGN fraction with stage.
-The dotted line is the expected AGN fraction in the field (from \citet{2008AJ....135.1877E}).
+The dotted line is the expected AGN fraction in the field (from \citealt{2008AJ....135.1877E}).
 We define the AGN fraction as the ratio of number of confirmed AGN divided by the number confirmed AGN and SFGs in the sample.
@@
 Errors on each fraction are found as the confidence intervals defined via the beta distribution.
-We find a sudden drop in AGN fraction from the separated to pericentre stage, followed by a rapid increase from the apocentre to merging stage.}
+We find an increase in AGN fraction from the apocentre to merging stage.}
     \label{fig:agn-frac-time}
@@
 
-\begin{figure}
-\centering
-\includegraphics[width=\columnwidth]{figures/sfg-agn-dist.pdf}
-\caption[The distribution of both AGN and SFGs which have been matched our confirmed galaxy pairs.]{The distribution of both AGN and SFGs which have matched our confirmed galaxy pairs.
+% \begin{figure}
+    % \centering
+    % \includegraphics[width=\columnwidth]{figures/sfg-agn-dist.pdf}
+    % \caption[The distribution of both AGN and SFGs which have been matched our confirmed galaxy pairs.]{The distribution of both AGN and SFGs which have matched our confirmed galaxy pairs.
 While we find, as expected, the number of AGN and SFGs decreases with projected separation we find an interesting double peak in the AGN sample.
@@
 The third peak, from 75 to 125kpc is only from separated and apocentre stage galaxies.}
-\label{fig:sfg-agn-proj}
-\end{figure}
+    % \label{fig:sfg-agn-proj}
+% \end{figure}
 
@@
 
+\begin{figure*}
+    \centering
+    \includegraphics[width=\textwidth]{figures/sfg-agn-dist.pdf}
+    \caption[The distribution of both AGN and SFGs which have been cross matched with our confirmed galaxy pairs.]{The distribution of both AGN and SFGs which have been cross matched with our confirmed galaxy pairs.
+While we find, as expected, the number of AGN and SFGs decreases with projected separation we find an interesting double peak in the AGN sample.
+The first peak, between a projected separation of 0 and 25kpc is primarily from pericentre stage galaxies while the second peak of 40 to 65kpc is of apocentre stage galaxies in our sample.
+As shown in Figure \ref{fig:agn-frac-time}, we expect the fraction of AGN to be similar in these two stages despite being at different parts of the dynamical timescale in interaction.
+The third peak, from 75 to 125kpc is only from separated and apocentre stage galaxies.}
+    \label{fig:sfg-agn-proj}
+\end{figure*}
+
 Again, it is important to note the rather `wide net' that our stage classification takes.
@@
 The second of these peaks is at the cross over point of pericentre to apocentre; the point at which (if the two galaxies have just flown by each other) a delayed AGN ignition could take place.
-This is also reflected in Figure \ref{fig:agn-stage} where we see a slight increase in AGN fraction in the apocentre stage.
-This is likely from the ignition of nuclear activity taking place over a large period of time with a delay being involved from the initial flyby.
 
@@
 However, to more fully study this, we would need a larger sample of confirmed AGN and star forming galaxies from existing photometry or catalogues to make more decisive conclusions based on stage.
-In this Chapter, we were limited to a small number of AGN and star forming galaxies across each stage.
+In this work, we were limited to a small number of AGN and star forming galaxies across each stage.
 When compared to our paired sample, we do not have the numbers to also divide into stage again.
@@
 \noindent In this work, we investigate the evolution of multiple parameters and processes in galaxy interaction with interaction stage.
-We use the interacting galaxy catalogue created in Chapter \ref{chapter2} and match it with the COSMOS survey to gain ancillary data.
+We use the interacting galaxy catalogue created in OR23 and match it with the COSMOS survey to gain ancillary data.
 This gives us a flux limited sample of 4,181 interacting galaxies of which 834 have a confirmed secondary from available photometric redshift data.
@@
 We also require numerical models to better identify the point in the dynamical timescale an interacting system is.
-This would lead to reliable constraints on the relations we have explore in this Chapter.
-We present our work on building such an algorithm in the following Chapter.
-This algorithm is focused on constraining both the dynamical timescale of the interaction and the full set of underlying parameters needed to describe a galaxy interaction.
+This would lead to reliable constraints on the relations we have explore in this work.
 
 \section*{Acknowledgements}
-The Acknowledgements section is not numbered. Here you can thank helpful
-colleagues, acknowledge funding agencies, telescopes and facilities used etc.
-Try to keep it short.
-
+To be added: 
+\begin{itemize}
+    \item Students who conducted initial classifications (if not co-authors).
+    \item Funding Body.
+    \item Software used.
+    \item ESA DL.
+    \item COSMOS
+\end{itemize}
 This work utilised data from the Cosmic Evolution Survey (COSMOS) which has a digital object identifier of 10.26131/IRSA178.
@@
 %%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%
-
-\appendix
-
-\section{Needed?}
 
